### 2025-04-15 Paper/manuscript.tex
Init manuscript.tex

\documentclass[fleqn,10pt,lineno]{manuscript}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul}

\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }

\title{A Structural and Functional Bioinformatics Study of QTY-designed Retinylidene Proteins}

\author[1]{Siqi Pan}
\author[2]{Shuguang Zhang}
\affil[1]{Shanghai World Foreign Language Academy, No. 400, Baihua Road, Shanghai 200233, China}
\affil[2]{Lab of Molecular Architecture, Media Lab, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\corrauthor[2]{Shuguang Zhang}{Shuguang@MIT.EDU}

\keywords{Keyword1; Keyword2; Keyword3}
\begin{abstract}
This is the abstract!
\end{abstract}

\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}

\section*{Introduction}

Intro

* Families of opsins - vertebrate vs. bacterial

* General features of vertebrate opsin; structure and function

* Activation mechanism of rhodopsin

* Expression, function of each opsin

* General features of bacterial opsin; structure, function, applications

* Why solubilize

* History of solubilizing studies of rhodopsin and bacteriorhodopsin

* Intro to AlphaFold

* Existing QTY studies

* Intro to GROMACS

* Existing rhodopsin bioinformatics studies

\section*{Results and Discussion}

Results

* discuss the QTY code

* describe and explain Table1

* describe and explain Fig1

* describe and explain Fig2
	> I need more discussion here

* describe and explain Fig3

* discuss AlphaFold3 predictions

* describe, explain, discuss MD results (Fig3 and Fig4)
	> I need more discussion here

* future scopes and potential applications

* conclusion

\section*{Methods}

Methods

* protein sequences UniProt

* AlphaFold3 server

* superimposition (PDB, AlphaFold, PyMOL)

* Structure visualization (PyMOL, ChimeraX)

* MD simulation (GROMACS, etc.; detailed params; analysis techniques)

\section*{Supplementary Material}

Can be found at...

\section*{Data Availability Statement}

Can be found at...

\section*{Author contributions}

A.O., A.T. and A.F. conceived the presented idea; A.O. wrote the main manuscript; All authors have read and agreed to the published version of the manuscript.

\section*{Financial Support}

This work was supported ... For the purpose of open access, the author has applied a CC BY public copyright licence to any Author Accepted Manuscript version arising from this submission.

\section*{Acknowledgments}

Thank...

\section*{Competing Interests}

The authors declare no conflict of interest.

\section*{Ethics Statement}

No ethics issues...

\bibliography{references}

\end{document}

### 2025-04-17 Paper/manuscript.tex
clean up raw structures, keeping only number 0; hydrophobicity graphs; reorganize structures directory; save loops-cut structures
update address
add sequence figs
looking for background

@@
 \usepackage{soul}
+\usepackage[utf8]{inputenc}
 
@@
 \author[2]{Shuguang Zhang}
-\affil[1]{Shanghai World Foreign Language Academy, No. 400, Baihua Road, Shanghai 200233, China}
+\affil[1]{Shanghai World Foreign Language Academy, 400 Baihua Street, Shanghai 200233, China}
 \affil[2]{Lab of Molecular Architecture, Media Lab, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
@@
 \begin{abstract}
-This is the abstract!
+
+Abstract of paper -- leave until everything is written.
+
 \end{abstract}
@@
 
+* Existing QTY studies
+
 * Intro to AlphaFold
-
-* Existing QTY studies
 
@@
 * describe and explain Fig2
-	> I need more discussion here
+	- I need more discussion here
 
@@
 * describe, explain, discuss MD results (Fig3 and Fig4)
-	> I need more discussion here
+	- I need more discussion here
 
@@
 
-Can be found at...
+The supplementary material can be found at...
 
@@
 
-Can be found at...
+The data for ... can be found at...
 
@@
 
-A.O., A.T. and A.F. conceived the presented idea; A.O. wrote the main manuscript; All authors have read and agreed to the published version of the manuscript.
+Detailed author contributions
 
@@
 
-This work was supported ... For the purpose of open access, the author has applied a CC BY public copyright licence to any Author Accepted Manuscript version arising from this submission.
+No funding was received for this project.
 
@@
 
-Thank...
+Thanks to ... for ...
 
@@
 
-No ethics issues...
+There are no ethics issues related to the research in this paper. No animal or human data...
 
@@
 
+\begin{table}[h]
+	\centering
+	\caption{TWO}
+	\label{tb:2}
+	\begin{tabular}{cccccc}
+		\toprule
+		Name     & RMSD (\AA) & pI   & Mw (kDa) & TM variation (\%) & Overall variation (\%) \\
+		\toprule
+		OPSG     &                 & 8.90 & 40.58    &                   &                        \\
+		OPSG QTY & 0.468           & 8.82 & 40.85    & 41.86             & 19.78                  \\
+		\midrule
+		OPSR     &                 & 8.89 & 40.57    &                   &                        \\
+		OPSR QTY & 0.611           & 8.83 & 40.76    & 40.12             & 18.96                  \\
+		\midrule
+		OPSB     &                 & 8.75 & 38.72    &                   &                        \\
+		OPSB QTY & 0.486           & 8.66 & 39.30    & 46.51             & 23.19                  \\
+		\midrule
+		OPSD     &                 & 6.20 & 38.89    &                   &                        \\
+		OPSD QTY & 0.559           & 6.20 & 39.29    & 46.58             & 21.55                  \\
+		\midrule
+		OPN3     &                 & 9.29 & 44.87    &                   &                        \\
+		OPN3 QTY & 0.454           & 9.18 & 45.47    & 49.12             & 20.90                  \\
+		\midrule
+		OPN4     &                 & 9.35 & 52.64    &                   &                        \\
+		OPN4 QTY & 0.307           & 9.19 & 53.08    & 50.34             & 15.48                  \\
+		\midrule
+		OPN5     &                 & 9.11 & 39.73    &                   &                        \\
+		OPN5 QTY & 0.555           & 9.02 & 40.04    & 45.58             & 18.93                  \\
+		\midrule
+		RGR      &                 & 8.34 & 31.87    &                   &                        \\
+		RGR QTY  & 0.537           & 8.29 & 32.39    & 42.86             & 21.65                  \\
+		\midrule
+		OPSX     &                 & 8.77 & 37.42    &                   &                        \\
+		OPSX QTY & 0.548           & 8.72 & 37.46    & 40.96             & 20.18                  \\
+		\midrule
+		BACR     &                 & 4.75 & 26.92    &                   &                        \\
+		BACR QTY & 0.448           & 4.75 & 27.40    & 46.67             & 25.30                  \\
+		\midrule
+		BACH     &                 & 5.34 & 26.96    &                   &                        \\
+		BACH QTY & 0.296           & 5.34 & 27.50    & 44.19             & 30.04                  \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
 \end{document}

### 2025-04-20 MD/QTY/set_dihedral.py
run qty cis md

@@ -1,0 +1,61 @@
+from math import *
+
+def rotate(point, axis, ref_point, angle):
+    rel_point = [point[i] - ref_point[i] for i in range(3)]
+    rel_new_point = [0, 0, 0]
+    angle_rad = angle *pi / 180
+    axis_normalized = [axis[i] / sqrt(sum([axis[j]**2 for j in range(3)])) for i in range(3)]
+    dot = sum([rel_point[i] * axis_normalized[i] for i in range(3)])
+    cross = [rel_point[(i+1)%3]*axis_normalized[(i+2)%3] - rel_point[(i+2)%3]*axis_normalized[(i+1)%3] for i in range(3)]
+    parallel = [axis_normalized[i] * dot for i in range(3)]
+    perpendicular = [rel_point[i] - parallel[i] for i in range(3)]
+    rotated_perpendicular = [perpendicular[i] * cos(angle_rad) + cross[i] * sin(angle_rad) for i in range(3)]
+    rel_new_point = [parallel[i] + rotated_perpendicular[i] for i in range(3)]
+    new_point = [rel_new_point[i] + ref_point[i] for i in range(3)]
+    return new_point
+
+def measure_dihedral(a, b, c, d):
+    ab = [a[i] - b[i] for i in range(3)]
+    bc = [b[i] - c[i] for i in range(3)]
+    cd = [c[i] - d[i] for i in range(3)]
+    ab_cross_bc = [ab[1]*bc[2] - ab[2]*bc[1], ab[2]*bc[0] - ab[0]*bc[2], ab[0]*bc[1] - ab[1]*bc[0]]
+    bc_cross_cd = [bc[1]*cd[2] - bc[2]*cd[1], bc[2]*cd[0] - bc[0]*cd[2], bc[0]*cd[1] - bc[1]*cd[0]]
+    ab_cross_bc_length = sqrt(sum([x**2 for x in ab_cross_bc]))
+    bc_cross_cd_length = sqrt(sum([x**2 for x in bc_cross_cd]))
+    cos_angle = sum([ab_cross_bc[i]*bc_cross_cd[i] for i in range(3)]) / (ab_cross_bc_length * bc_cross_cd_length)
+    dihedral = acos(cos_angle) * 180 / pi
+    return dihedral
+
+with open("coordinates_to_rotate.txt", "r") as file:
+    lines = file.readlines()
+
+# axis is b-c
+# pivot is c
+# dihedral is a-b-c-d
+# delete the first column of resi/resn in .gro file
[…]

### 2025-04-21 Paper/manuscript.tex
Make sequence, protein characteristics, superimposition of human opsins figures
pairwise comparison and hydrophobicity graph
build background structure

@@
 
-\keywords{Keyword1; Keyword2; Keyword3}
+\keywords{Keyword 1; Keyword 2; Keyword 3}
 \begin{abstract}
@@
 
-Intro
+\textbf{* Families of opsins - vertebrate vs. bacterial}
 
-* Families of opsins - vertebrate vs. bacterial
+Retinylidene proteins are light-sensing proteins that bind to retinal as a chromophore. 
+Prevalence of these proteins - occur in many organisms, from archaea to vertebrates. 
+Evolutionarily distinct, convergence; GPCR vs ion pumps or channels.
 
-* General features of vertebrate opsin; structure and function
+\textbf{* General features of vertebrate opsin; structure and function; activation mechanism of rhodopsin; may include existing rhodopsin bioinformatics studies?}
 
-* Activation mechanism of rhodopsin
+GPCR, 7TM. 
+RHO: rhodopsin is exemplary; earliest GPCR studied, bovine rhodopsin. 
+Lysine-retinal schiff base linkage, conserved evolutionarily. 
+Delocalized electrons in retinal, receive photon, high activation rate. 
+11-cis to all-trans isomerization.
+RHO: dark >> batho >> lumi >> meta I <<>> meta II; proton-transfer pathway. 
+TM6 outward. 
+Activates G-protein, initiate secondary messenger cascade.
 
-* Expression, function of each opsin
+\textbf{* Expression, function of each vertebrate opsin}
 
-* General features of bacterial opsin; structure, function, applications
+The OPN family preferentially binds 11-cis-retinal and catalyzes its isomerization to all-trans-retinal via a retinochrome mechanism.
 
-* Why solubilize
+OPN1MW (Medium-Wave-sensitive Opsin 1), OPN1LW (Long-Wave-sensitive Opsin 1) and OPN1SW (Short-Wave-sensitive Opsin 1) are proteins expressed in cone photoreceptors in the retina and are responsible for color vision.
+OPN1MW has maximum absorption at wavelength 530nm (green), OPN1LW at wavelength 560nm (red), and OPN1SW at wavelength 420nm (blue).
+They are responsible for various color vision defects.
+Deutanopia, a partial colorblindness characterized by a dichromasy in which red and green are confused, is caused by variants affecting OPN1MW.
+Protanopia, a partial colorblindness similar to deutanopia, is caused by variants affecting OPN1LW.
+Tritanopia, a color blindness characterized by selective deficiency of blue spectral sensitivity, is owed to variants of OPN1SW.
+Blue cone monochromacy, an X-linked congenital cone dysfunction syndrome, is caused by the absence of functional OPN1MW and OPN1LW.
+Finally, cone dystrophy 5 is an X-linked cone dystrophy characterized by loss of visual acuity, macular lesions, and color vision.
 
-* History of solubilizing studies of rhodopsin and bacteriorhodopsin
+OPN2 (Opsin 2), also known as rhodopsin, is expressed in retinal rod photoreceptors and essential for light transduction and vision at low light intensity.
+It is correlated with retinitis pigmentosa 4, characterized by retinal pigments deposits, loss of night vision, loss of peripheral visual field, and eventual loss of central visual field.
+Autosomal dominant night blindness, a non-progressive impairment of night vision, is also attributed to mutation of OPN2.
 
-* Existing QTY studies
+OPN3 (Opsin 3), also known as encephalopsin or panopsin, is a GPCR activated via ultraviolet A light. 
+Regulates melanogenesis in melanocytes. 
+Plays a role in melanocyte survival through regulation of intracellular Ca levels. 
+Regulates apoptosis via Cyt c release and activation of caspase cascade. 
+Keratinocyte differentiation in response to blue light. 
+Plays a role in light'mediated glucose uptake, mitochondrial respiration and fatty acid metabolism in brown adipocyte tissues. 
+May be involved in photorelaxation of airway smooth muscle cells via blue light.
 
-* Intro to AlphaFold
+OPN4 (Opsin 4), also known as melanopsin, is expressed in ipRGC (intrinsically photosensitive Retinal Ganglion Cells) in the ganglion cell layer in the retina.
+Absorption wavelength???
+It is responsible for pupillary reflex, photoentrainment, optokinetic visual tracking response, and other non-image-forming responses to light.
 
-* Intro to GROMACS
+OPN5 (Opsin 5), also known as neuropsin, is a GPCR activated via ultraviolet A light. 
+Emission peaks at 380nm (UVA) and 470nm (blue). 
+Required for the light-response in the inner plexiform layer, and contributes to the regulation of the light-response in the nerve fiber layer. 
+Involved in local corneal and retinal circadian rhythm photoentrainment via modulation of UVA light-induced phase-shift of the retina clock. 
+Circadian photoreceptor in the outer ear.
 
-* Existing rhodopsin bioinformatics studies
+RGR (RPE-retinal GPCR) is expressed in the RPE (retinal pigmented epithelium) and Muller cells in the retina.
+Unlike the aforementioned OPN family, RGR preferentially binds all-trans-retinal and may catalyze its isomerization via a retinochrome-like mechanism.
+FUNCTION?
+
+RRH (visual pigment-like receptor), also known as peropsin, is localized in the microvilli of RPE that surround photoreceptor outer segments.
+It may play a role in RPE physiology either by detecting light directly or by monitoring the concentration of retinal.
+FUNCTION?
+
+\textbf{* General features of bacterial opsin; structure, function, applications}
+
+7TM? 
+Ion channels or pumps? 
+Optogenetics. 
+Other applications??
+
+\textbf{* Expression, function of each bacterial opsin}
+
+BACR, or bacteriorhodopsin, is a 7TM protein that forms a trimer light-driven proton pump. It binds to 13-cis-retinal and catalyzes the isomerization to all-trans-retinal? Studied... Applications...
+
+BACH, or halorhodopsin, is a 7TM protein that forms a trimer light-driven chloride pump.
+It binds to 13-cis-retinal and catalyzes the isomerization to all-trans-retinal?
+Studied...
+It is activated by yellow light and is used as a tool of inhibition in optogenetics.
+More applications...
+
+ChR2, or channelrhodopsin 2, is a 7TM protein that forms a dimer light-activated sodium channel.
+It binds to 13-cis-retinal and catalyzes the isomerization to all-trans-retinal?
+Studied...
+It is activated by blue light and is used as a tool of excitation in optogenetics.
+More applications...
+
+\textbf{* Why solubilize}
+
+“Recently, we have asked if the QTY code is applicable to other retinylidene proteins.
+The retinylidene proteins are all integral membrane proteins with seven transmembrane alpha-helices embedded in a lipid bilayer.
+Therefore, because of the hydrophobic properties of transmembrane domains, they are not water-soluble without the aid of detergents.
+We wanted to see if the QTY code could be utilized to design water-soluble variants of these retinylidene proteins.”
+
+\textbf{* History of solubilizing studies of rhodopsin and bacteriorhodopsin}
+
+RESEARCH.
+
+\textbf{* Existing QTY studies}
+
+\textbf{* Intro to AlphaFold}
+
+\textbf{* Intro to GROMACS}
+
+\textbf{* Overview of this paper}
 
@@
 	\centering
-	\caption{TWO}
-	\label{tb:2}
-	\begin{tabular}{cccccc}
-		\toprule
-		Name     & RMSD (\AA) & pI   & Mw (kDa) & TM variation (\%) & Overall variation (\%) \\
-		\toprule
-		OPSG     &                 & 8.90 & 40.58    &                   &                        \\
-		OPSG QTY & 0.468           & 8.82 & 40.85    & 41.86             & 19.78                  \\
-		\midrule
-		OPSR     &                 & 8.89 & 40.57    &                   &                        \\
-		OPSR QTY & 0.611           & 8.83 & 40.76    & 40.12             & 18.96                  \\
-		\midrule
-		OPSB     &                 & 8.75 & 38.72    &                   &                        \\
-		OPSB QTY & 0.486           & 8.66 & 39.30    & 46.51             & 23.19                  \\
-		\midrule
-		OPSD     &                 & 6.20 & 38.89    &                   &                        \\
-		OPSD QTY & 0.559           & 6.20 & 39.29    & 46.58             & 21.55                  \\
-		\midrule
-		OPN3     &                 & 9.29 & 44.87    &                   &                        \\
-		OPN3 QTY & 0.454           & 9.18 & 45.47    & 49.12             & 20.90                  \\
-		\midrule
-		OPN4     &                 & 9.35 & 52.64    &                   &                        \\
-		OPN4 QTY & 0.307           & 9.19 & 53.08    & 50.34             & 15.48                  \\
-		\midrule
-		OPN5     &                 & 9.11 & 39.73    &                   &                        \\
-		OPN5 QTY & 0.555           & 9.02 & 40.04    & 45.58             & 18.93                  \\
-		\midrule
-		RGR      &                 & 8.34 & 31.87    &                   &                        \\
-		RGR QTY  & 0.537           & 8.29 & 32.39    & 42.86             & 21.65                  \\
-		\midrule
-		OPSX     &                 & 8.77 & 37.42    &                   &                        \\
-		OPSX QTY & 0.548           & 8.72 & 37.46    & 40.96             & 20.18                  \\
-		\midrule
-		BACR     &                 & 4.75 & 26.92    &                   &                        \\
-		BACR QTY & 0.448           & 4.75 & 27.40    & 46.67             & 25.30                  \\
-		\midrule
-		BACH     &                 & 5.34 & 26.96    &                   &                        \\
-		BACH QTY & 0.296           & 5.34 & 27.50    & 44.19             & 30.04                  \\
-		\bottomrule
-	\end{tabular}
+	\caption{Protein characteristics}
+	\label{tb:characteristics}
+	\includegraphics[width=\linewidth]{Figures/characteristics.jpg}
 \end{table}
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
+	\caption{Protein sequence alignments}
+	\label{fig:sequences}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/superimposition-human.jpg}
+	\caption{Superimposition of human retinylidene proteins}
+	\label{fig:humansup}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/superimposition-bacterial.jpg}
+	\caption{Superimposition of bacterial retinylidene proteins}
+	\label{fig:bacterialsup}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/pairwise.jpg}
+	\caption{Pairwise comparison of human opsins}
+	\label{fig:pairwise}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/hydrophobicity.jpg}
+	\caption{Surface hydrophobicity}
+	\label{fig:hydrophobicity}
+\end{figure}
+
 \end{document}

### 2025-04-22 Paper/Source/manuscript.tex
Switch to Overleaf TeX. Add RGR and RRH to all OPN superimposition

--- 2025-04-21 Paper/manuscript.tex
@@
 %%\doublespacing
-\usepackage{soul}
+\usepackage{soul, hyperref}
 \usepackage[utf8]{inputenc}
@@
 
-\title{A Structural and Functional Bioinformatics Study of QTY-designed Retinylidene Proteins}
+\title{A Structural and Functional Bioinformatics Study of QTY-designed Opsins}
 
@@
 
-Abstract of paper -- leave until everything is written.
+This study investigates the QTY design of 9 human opsins and 3 microbial opsins, all of which bind retinal as the ligand.
 
@@
 
-\textbf{* Families of opsins - vertebrate vs. bacterial}
+\textbf{* Families of opsins - animal vs. microbial}
+
+\citep{Spudich_2000}
 
@@
 
-\textbf{* General features of vertebrate opsin; structure and function; activation mechanism of rhodopsin; may include existing rhodopsin bioinformatics studies?}
+\textbf{* General features of animal opsin; structure and function; activation mechanism of rhodopsin; may include existing rhodopsin bioinformatics studies?}
 
-GPCR, 7TM. 
-RHO: rhodopsin is exemplary; earliest GPCR studied, bovine rhodopsin. 
+Class A GPCR, 7TM, NPxxY motif, outward movement of TM6. \citep{Sakmar_2002, Zhou_2019}
+296 Lys in TM7 \citep{Guhmann_2022}.
 Lysine-retinal schiff base linkage, conserved evolutionarily. 
@@
 
-\textbf{* Expression, function of each vertebrate opsin}
+\textbf{* Expression, function of each animal opsin}
 
 The OPN family preferentially binds 11-cis-retinal and catalyzes its isomerization to all-trans-retinal via a retinochrome mechanism. 
+Evolutionarily distinct animal opsins \citep{Terakita_2005, Shichida_2009}
 
@@
 It is correlated with retinitis pigmentosa 4, characterized by retinal pigments deposits, loss of night vision, loss of peripheral visual field, and eventual loss of central visual field.
-Autosomal dominant night blindness, a non-progressive impairment of night vision, is also attributed to mutation of OPN2.
+Congenital stationary night blindness, a non-progressive autosomal dominant impairment of night vision, is also attributed to mutation of OPN2.
+RHO: rhodopsin is exemplary; earliest opsin studied, earliest crystal structure of GPCR \citep{Palczeski_2000} bovine rhodopsin.
 
@@
 
-RRH (visual pigment-like receptor), also known as peropsin, is localized in the microvilli of RPE that surround photoreceptor outer segments.
+RRH (RPE-derived Rhodopsin Homolog), also known as peropsin, is localized in the microvilli of RPE that surround photoreceptor outer segments.
 It may play a role in RPE physiology either by detecting light directly or by monitoring the concentration of retinal.
@@
 
-\textbf{* General features of bacterial opsin; structure, function, applications}
+\textbf{* General features of microbial opsin; structure, function, applications}
 
@@
 
-\textbf{* Expression, function of each bacterial opsin}
+\textbf{* Expression, function of each microbial opsin}
 
-BACR, or bacteriorhodopsin, is a 7TM protein that forms a trimer light-driven proton pump. It binds to 13-cis-retinal and catalyzes the isomerization to all-trans-retinal? Studied... Applications...
-
+\citep{Findlay_1986, Zhang_2011}
+BACR, or bacteriorhodopsin, is a 7TM protein that forms a trimer light-driven proton pump.Studied... Applications...
 BACH, or halorhodopsin, is a 7TM protein that forms a trimer light-driven chloride pump.
-It binds to 13-cis-retinal and catalyzes the isomerization to all-trans-retinal?
 Studied...
@@
 More applications...
-
 ChR2, or channelrhodopsin 2, is a 7TM protein that forms a dimer light-activated sodium channel.
-It binds to 13-cis-retinal and catalyzes the isomerization to all-trans-retinal?
 Studied...
@@
 More applications...
+All-trans to 13-cis? 
+BACH \citep{Baselt_1989, Kouyama_2018}. BACR \citep{Taguchi_2023}. ChR2 \citep{Nagel_2005, Ardevol_2018, Xin_2023}.
+
+\textbf{* History of solubilizing studies of rhodopsin and bacteriorhodopsin}
+
+RESEARCH.
+
+"Recently, researchers built on top of ProteinMPNN to devise SolubleMPNN trained on only soluble proteins, which was applied to engineer soluble variants of bacteriorhodopsin, successfully converting a membrane protein into a soluble one, while maintaining its core function and ligand-binding ability (Nikolaev et al., 2024)."
 
@@
 
-\textbf{* History of solubilizing studies of rhodopsin and bacteriorhodopsin}
+\textbf{* Existing QTY studies}
+
+"Instead of taking a computational approach, we applied the QTY code to systematically engineer watersoluble analogs with reduced hydrophobicity in membrane proteins.
+The QTY concept was inspired by high-resolution (1.5\AA) electron density maps, which revealed structural similarities between hydrophobic and polar amino acids leucine (L) vs glutamine (Q); isoleucine (I)/valine (V) vs threonine (T); and phenylalanine (F) vs tyrosine (Y) (Zhang et al., 2018; Zhang \& Egli 2022; Tegler et al., 2020).
+In our previous experiments, using the simple and straightforward QTY code, we successfully bioengineered detergent-free chemokine (Zhang et al., 2018; Qing et al., 2019; Tegler et al., 2020), cytokine receptors (Hao et al., 2020) and bacterial histidine kinase (Li et al 2024).
+After these detergent-free membrane proteins were expressed and purified, these QTY analogs demonstrated structural stability, retained their ligand-binding capabilities and intact four enzymatic activities, making them ideal candidates for further studies and use them as antigens to generate therapeutic monoclonal antibodies."
+
+\textbf{* Intro to AlphaFold}
+
+"In May 2024, AlphaFold was upgraded to version 3 as AlphaFold 3, featuring an enhanced diffusion-based architecture that enables accurate prediction of multiple structures of protein complexes.
+Additionally, AlphaFold 3 extends its capabilities beyond protein structure prediction to include DNA, RNA, and small molecules including ligands and other proteins (Abramson et al., 2024)"
+
+\textbf{* Intro to GROMACS}
 
@@
 
-\textbf{* Existing QTY studies}
+\textbf{* Overview of this paper}
 
-\textbf{* Intro to AlphaFold}
-
-\textbf{* Intro to GROMACS}
-
-\textbf{* Overview of this paper}
+SUMMARY.
 
@@
 * describe, explain, discuss MD results (Fig3 and Fig4)
+        - no changes to the NPxxY motif or retinal-binding Lys
 	- I need more discussion here
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 
@@
 
-\begin{table}[h]
+\begin{table}[htbp]
 	\centering
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
 	\centering
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
 	\centering
-	\includegraphics[width=\linewidth]{Figures/superimposition-bacterial.jpg}
-	\caption{Superimposition of bacterial retinylidene proteins}
-	\label{fig:bacterialsup}
+	\includegraphics[width=\linewidth]{Figures/superimposition-microbial.jpg}
+	\caption{Superimposition of microbial retinylidene proteins}
+	\label{fig:microbialsup}
 \end{figure}
 
-\begin{figure}[h]
+\begin{figure}[htbp]
 	\centering

### 2025-04-26 Paper/Source/manuscript.tex
rename superimposition to superposition; edit manuscript to nearly complete intro and methods

--- 2025-04-17 Paper/manuscript.tex
@@
 
-\keywords{Keyword1; Keyword2; Keyword3}
+\keywords{Keyword 1; Keyword 2; Keyword 3}
 \begin{abstract}
 
-Abstract of paper -- leave until everything is written.
+This study investigates the QTY design of 9 human and 3 microbial retinylidene proteins ... [TO BE WRITTEN]
 
@@
 
-Intro
+Retinylidene proteins are photochemically reactive proteins that is bound to or can bind to retinal (vitamin-A aldehyde) as their chromophore \citep{Spudich_2000}.
+We will use the term ``opsin'' interchangeably with ``retinylidene proteins'', despite that is sometimes refers specifically to the chromophore-free apoprotein.
+Retinylidene proteins are divided into two groups, animal opsins and microbial opsins, which are evolutionarily distinct but share common features such as haveing 7 transmembrane (TM) domains and a retinal-binding lysine residue \citep{Yee_2013, Spudich_2000}.
+In this study, we will consider 9 animal opsins and 3 microbial opsins.
 
-* Families of opsins - vertebrate vs. bacterial
+\textbf{Animal opsins} are a type of class A GPCR (G-protein coupled receptor), which are characterized by 7 transmembrane domains, the NPxxY motif, and activation of G-proteins through the outward movement of TM6.
+\citep{Sakmar_2002, Nordstrom_2011, Zhou_2019}.
+Almost all animal opsins include a lysine residue that forms a Schiff base linkage with retinal \citep{Bownds_1967, Guhmann_2022}.
+When retinal absorbs a photon, it isomerizes, usually changing from 11-cis to all-trans.
+The subsequent conformational changes of the protein are well studied using bovine rhodopsin, which changes from dark state to BATHO state, then LUMI, META I, and META II \citep{Okada_2001, Smith_2010}.
+Proton transfer plays a major role in this process \citep{Mahalingam_2008}.
+During this process, TM6 characteristically moves outward, activating the G-protein.
 
-* General features of vertebrate opsin; structure and function
+In this study, we selected 9 opsins expressed in the human nervous system: OPN1MW (\href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (\href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04000}), OPN1SW (\href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (\href{https://www.uniprot.org/uniprotkb/P08100/entry}{P08100}), OPN3 (\href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (\href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (\href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (\href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (\href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}).
+They belong to several evolutionarily distinct families of animal opsins \citep{Terakita_2005, Shichida_2009}.
 
-* Activation mechanism of rhodopsin
+\textbf{OPN1MW} (Medium-Wave-sensitive Opsin 1), \textbf{OPN1LW} (Long-Wave-sensitive Opsin 1) and \textbf{OPN1SW} (Short-Wave-sensitive Opsin 1) are expressed in retinal cone photoreceptors and are responsible for color vision \citep{Bowmaker_1980}.
+Certain variants of OPN1MW, OPN1LW and OPN1SW respectively cause deutanopia, protanopia, and tritanopia, which are different types of color blindness \citep{Ueyama_2002, Baraas_2012}.
+The absence of both functional OPN1MW and OPN1LW causes blue cone monochromacy, an X-linked congenital cone dysfunction syndrome \citep{Wissinger_2022}, and cone dystrophy 5, an X-linked cone dystrophy \citep{Gardner_2010}.
 
-* Expression, function of each opsin
+\textbf{OPN2} (Opsin 2), also known as rhodopsin, is expressed in retinal rod photoreceptors and is responsible for vision at low light intensity \citep{Hubbard_1958}.
+Certain variants lead to autosomal recessive or autosomal dominant retinitis pigmentosa \citep{Fanelli_2021}.
+Other variants also lead to congenital stationary night blindness \citep{Fanelli_2021}.
+OPN2 is a representative animal opsin, one of the earliest studied \citep{Hubbard_1958}.
+In fact, bovine OPN2 is the first opsin to be sequenced \citep{Nathans_1984} as well as the first GPCR whose crystal structure was resolved experimentally \citep{Palczeski_2000}.
+Many studies on the functional mechanisms of animal opsins also focus on OPN2 \citep{Park_2008, Scheerer_2008, Kimata_2016}.
+Consequently, we also choose OPN2 to conduct a functional analysis in this study, in order to further explore the effectiveness of the QTY design of retinylidene proteins.
 
-* General features of bacterial opsin; structure, function, applications
+\textbf{OPN3} (Opsin 3), also known as encephalopsin or panopsin, is activated by blue and ultraviolet A light.
+It is expressed in the brain \citep{Blackshaw_1999}.
+It is also expressed in melanocytes and keratinocytes in the skin and regulates functions such as melanogenesis, cell differentiation, and glucose uptake \citep{Koyanagi_2013, Olinski_2020}.
 
-* Why solubilize
+\textbf{OPN4} (Opsin 4), also known as melanopsin, is expressed in ipRGC (intrinsically photosensitive Retinal Ganglion Cells) in the ganglion cell layer in the retina \citep{Provencio_1998}.
+It is responsible for pupillary reflex, photoentrainment, optokinetic visual tracking response, and other non-image-forming responses to light \citep{Berson_2002, Gooley_2003}.
 
-* History of solubilizing studies of rhodopsin and bacteriorhodopsin
+\textbf{OPN5} (Opsin 5), also known as neuropsin, is activated by blue and ultraviolet A light \citep{Tarttelin_2003, Yamashita_2010}.
+It is expressed in the retina and contributes to the regulation of light-dependent vascular development \citep{Nguyen_2019} and the photoentrainment in the cornea and retina \citep{Buhr_2015}.
 
-* Existing QTY studies
+\textbf{RGR} (RPE-retinal GPCR) is expressed in the RPE (Retinal Pigmented Epithelium) and M\"uller cells in the retina \citep{Shen_1994}.
+Unlike the aforementioned human opsins, RGR preferentially binds all-trans-retinal and may catalyze its isomerization into 11-cis-retinal via a retinochrome-like mechanism \citep{Radu_2008}.
+It plays a role in light-dependent synthesis of visual chromophore \citep{Radu_2008}.
 
-* Intro to AlphaFold
+\textbf{RRH} (RPE-derived Rhodopsin Homolog), also known as peropsin, is localized in the microvilli of RPE cells that surround photoreceptor outer segments \citep{Sun_1997}.
+It is another protein that preferentially binds to all-trans-retinal \citep{Cook_2017}.
 
-* Intro to GROMACS
+\textbf{Bacterial opsins} are transmembrane ion pumps or channels \citep{Findlay_1986, Zhang_2011}.
+They are also 7TM, though this is due to convergent evolution rather than homology \citep{Yee_2013}.
+The isomerization of retinal is usually from all-trans to 13-cis, different from that in animal opsins \citep{Findlay_1986, Spudich_2000}.
+Additionally, bacterial opsins often form oligomers to carry out their functions \citep{Taguchi_2023, Gmelin_2007, Shan_2024}.
 
-* Existing rhodopsin bioinformatics studies
+In this study, we selected 3 bacterial opsins: BACR (\href{https://www.uniprot.org/uniprotkb/P02945/entry}{P02945}), BACH (\href{https://www.uniprot.org/uniprotkb/B0R2U4/entry}{B0R2U4}), ChR2 (\href{https://www.uniprot.org/uniprotkb/Q8RUT8/entry}{Q8RUT8}).
+
+\textbf{BACR} (Bacteriorhodopsin) is a light-driven proton pump \citep{Oesterhelt_1971}.
+\textbf{BACH} (Halorhodopsin) is a light-driven chloride pump activated by yellow light \citep{Schobert_1982}.
+\textbf{ChR2} (Channelrhodopsin 2) is a light-activated sodium channel activated by blue light \citep{Nagel_2003}.
+BACH and ChR2 are among the first optogenetic tools \citep{Zhang_2007, Han_2007}.
+BACH is used for inhibition while ChR2 is used for excitation.
+
+We have asked if retinylidene proteins could be redesigned to be more soluble.
+Retinylidene proteins are all integral membrane proteins with seven transmembrane alpha-helices embedded in a lipid bilayer.
+Due the hydrophobic properties of transmembrane domains, they are not water-soluble without the aid of detergents.
+
+Bacteriorhodopsin has been the subject of several protein-solubilizing studies, though to limited success \citep{Sirokman_1993, Gibas_1997, Mitra_2002}.
+Recently, researchers leveraged a neural network, SolubleMPNN, which was built upon ProteinMPNN, to engineer soluble variants of bacteriorhodopsin while maintaining its ligand-binding ability and light-sensing function \citep{Nikolaev_2024}.
+
+Instead of taking a computational approach, we applied the QTY code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins.
+There are structural similarities between hydrophobic and polar amino acids: leucine (L) vs glutamine (Q); isoleucine (I)/valine (V) vs threonine (T); and phenylalanine (F) vs tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}.
+This justifies residue replacement of hydrophobic aminoacids with polar ones.
+We initially applied the QTY (Glutamine, Threonine, Tyrosine) code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding activities and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}.
+We have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.
+
+AlphaFold2 was released by Google DeepMind in July 2021 \citep{Jumper_2021}.
+It greatly facilitated the study of QTY-designed protein variants.
+Subsequently, AlphaFold3 was released in May 2024, featuring an enhanced architecture and improved efficiency \citep{Abramson_2024}.
+Furthermore, AlphaFold3 enabled accurate prediction of complexes of multiple proteins as well as complexes with nucleic acids and certain small molecules.
+QTY studies have made use of these new features \citep{Chen_2025, Johnsson_2025}.
+
+GROMACS is a molecular dynamics (MD) simulation program released in 1995 \citep{Berendsen_1995}.
+Its 5.0 version was released in 2015 \citep{Abraham_2015}.
+GROMACS enables efficient and realistic simulation of biomolecular systems, and it has been used to investigate structural and functional properties of QTY-designed protein variants in various studies \citep{Karagol_2024, Li_Tang_2024, Smorodina_2024, Li_Wang_2024, Johnsson_2025}.
+
+In this paper, we apply the QTY code to redesign 9 human opsins and 3 microbial opsins. We provide superposition
 
@@
 * describe and explain Table1
+
+* entrance of retinal is posteriori folding, so it is safe that we predict chromophore-free form
 
@@
 * describe, explain, discuss MD results (Fig3 and Fig4)
+        - no changes to the NPxxY motif or retinal-binding Lys
+        - "The ionic environment of the RSB, defined by the residues of the binding pocket, dictates the spectral and kinetic characteristics of each individual protein." - \citep{Fenno_2011}
 	- I need more discussion here
@@
 
-Methods
+\subsection*{QTY design, protein sequence alignment and other characteristics}
 
-* protein sequences UniProt
+The native protein sequences for OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, RRH, BACR, BACH, and ChR2 were attained from UniProt (\url{https://www.uniprot.org}).
+The sequence for ChR2 was truncated according to the experimental structure in RCSB PDB (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
+The QTY designs were realized through the Protein Solubilizing Server (\url{https://pss.sjtu.edu.cn/}) \citep{Tao_2022}.
+For ChR2, secondary structure was provided to the server in SS3 format according to the RCSB PDB structure.
 
-* AlphaFold3 server
+\subsection*{AlphaFold3 predictions}
 
-* superimposition (PDB, AlphaFold, PyMOL)
+We predicted the structures of the native proteins and their QTY variants using the AlphaFold3 website (\url{https://alphafoldserver.com}) \citep{Abramson_2024}.
+For microbial opsins, the dimers and trimers had identical subunits, i.e., were homodimers and homotrimers.
+In AlphaFold3, this is achieved by altering the number of protein copies.
 
-* Structure visualization (PyMOL, ChimeraX)
+\subsection*{Structure superpositions}
 
-* MD simulation (GROMACS, etc.; detailed params; analysis techniques)
+PDB files for native protein structures determined experimentally using X-ray diffraction or electron microscopy were taken from RCSB PDB: OPN2 (\href{https://www.rcsb.org/structure/5W0P}{5W0P}), BACR (\href{https://www.rcsb.org/structure/7XJC}{7XJC}), BACH (\href{https://www.rcsb.org/structure/2JAF}{2JAF}), ChR2 (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
+The AlphaFold3-predicted native and QTY variants were taken directly from the most probable predicted structure.
+Superpositions were performs via the command ``super'' in PyMOL (\url{https://pymol.org}).
+We removed unstructured loops at N and C terminals for clarity.
+
+\subsection*{Structure visualization}
+
+We used PyMOL (\url{https://pymol.org}) to superpose the native predicted protein structures, their QTY variants, and the experimental structures for those proteins where these existed.
+We then used UCSF ChimeraX (\url{https://www.cgl.ucsf.edu/chimerax/}) to render each protein model with hydrophobicity patches.
+
+\subsection*{Molecular dynamics simulations}
+
+All MD simulations and analyses were executed on a desktop computer with Intel Xeon Platinum 8352V Processor, 256GB RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 24GB VRAM each.
+All MD simulations were conducted using GROMACS 2024.5 \citep{Abraham_2015} with the CHARMM36m all-atom force field \citep{Huang_2017}.
+The parameters for retinal were obtained from NAMD Wiki (\url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalTop} and \url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalPar}), and integrated manually into the files for the protein.
+Initial structures, configuration files and command-line codes for the simulations are publicly available at ...
+[ONLINE DATABASE TO BE PREPARED].
+
+Regarding the native OPN2, the membrane-protein system was constructed using CHARMM-GUI’s web-based membrane builder and downloaded in GROMACS format \citep{Jo_2008, Wu_2014, Lee_2016}.
+The protein was centered in a rectangular box.
+The membrane models generated consisted 40\% POPC, 40\% POPE, 10\% POPS, and 10\% cholesterol, which simulate a rod photoreceptor disk membrane \citep{Albert_2005}.
+The system was solvated in TIP3P water with 150 mM NaCl.
+11-cis-retinal was manually added to the protein files.
+Electrostatics were handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm.
+System energy was minimized using the steepest descent until maximum forces converged below 1000 kJ/mol/nm.
+The standard six-step CHARMM-GUI NP$\gamma$T equilibration protocol \citep{Jo_2008} was used, with 2 125-ps NVT equilibration simulations, and 1 125-ps and 3 500-ps NP$\gamma$T equilibration simulations.
+Temperature and pressure were maintained at 303.15 K and 1.0 bar, respectively, using the V-rescale thermostat and C-rescale barostat with surface-tension coupling.
+The LINCS algorithm was used for constraints.
+Verlet integrator was used.
+Following equilibration, a 10-ns production MD simulation was run.
+Then, the retinal molecule was manually switched to all-trans state by rotating C13 to C15 and bonded hydrogens and methyl groups by 180 degrees around the C11-C12 bond.
+Energy minimization and equilibration were repeated exactly as before, and then a 200-ns production MD simulation was run.
+
+Regarding the QTY-designed OPN2, the system was constructed directly using GROMACS.
+The protein was centered in a rectangular box of identical size with that of native OPN2.
+The system was solvated in TIP3P water with 150mM NaCl.
+11-cis-retinal was manually added to the protein files.
+System energy was minimized using the steepest descent until maximum forces converged below 1000 kJ/mol/nm.
+Electrostatics were handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm.
+The equilibration process is designed to align with that of the native protein, with 1 250-ps NVT equilibration simulation, and 1 125-ps and 1 1500-ps NPT equilibration simulations.
+Temperature and pressure were maintained at 303.15 K and 1.0 bar, respectively, using the V-rescale thermostat and C-rescale barostat with isotropic coupling.
+The LINCS algorithm was used for constraints.
+Verlet integrator was used.
+Following equilibration, a 10-ns production MD simulation was run.
+Then, the retinal molecule was manually switched to all-trans state by rotating C13 to C15 and bonded hydrogens and methyl groups by 180 degrees around the C11-C12 bond.
+Energy minimization and equilibration were repeated exactly as before, and then a 200-ns production MD simulation was run.
+
+ANALYSIS METHODS TO BE ADDED.
 
@@
 
-The supplementary material can be found at...
+The supplementary material can be found at... [TO BE ADDED]
 
@@
 
-The data for ... can be found at...
+The data for ... can be found at... [ONLINE DATABASE TO BE PREPARED]
 
@@
 
-Detailed author contributions
+Conceptualization: S.P., S.Z.; Formal analysis: S.P.; Investigation: Methodology: S.P.; Validation: S.P.; Data curation: S.P.; Writing—original draft preparation: S.P., S.Z.; Review and editing: S.P., S.Z.
 
@@
 
-No funding was received for this project.
+There is no financial support for this digital bioinformatics study. We only used free tools that are publicly available.
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 
-Thanks to ... for ...
+Thanks to ... for ... [TO BE ADDED]
 
@@
 
-The authors declare no conflict of interest.
+Massachusetts Institute of Technology (MIT) filed several patent applications for the QTY code for GPCRs excluding the human opsins.
+OH2Laboratories licensed the technology from MIT to work on water-soluble GPCR variants.
+S.Z.
+is an inventor of the QTY code and has a minor equity in OH2Laboratories.
+S.Z.
+is a Scientific Advisor and has minor shares for a startup RealNose to develop a sensing device based on olfactory receptors.
+S.Z.
+founded a startup 511 Therapeutics to generate therapeutic monoclonal antibodies against solute carrier transporters to treat pancreatic cancer.
+S.Z.
+has majority equity in 511 Therapeutics.
+All other authors have no competing interests.
 
@@
 
-There are no ethics issues related to the research in this paper. No animal or human data...
+All methods were carried out in accordance with relevant guidelines and regulations.
+All experimental protocols were approved by a named institutional and licensing committee.
+Neither human biological samples nor human subjects were used in the study.
+This is a completely digital structural bioinformatic study using the publicly available AlphaFold3 machine learning program and GROMACS molecular dynamics simulation program.
 
@@
 
-\begin{table}[h]
+\begin{table}[htbp]
 	\centering
-	\caption{TWO}
-	\label{tb:2}
-	\begin{tabular}{cccccc}
-		\toprule
-		Name     & RMSD (\AA) & pI   & Mw (kDa) & TM variation (\%) & Overall variation (\%) \\
-		\toprule
-		OPSG     &                 & 8.90 & 40.58    &                   &                        \\
-		OPSG QTY & 0.468           & 8.82 & 40.85    & 41.86             & 19.78                  \\
-		\midrule
-		OPSR     &                 & 8.89 & 40.57    &                   &                        \\
-		OPSR QTY & 0.611           & 8.83 & 40.76    & 40.12             & 18.96                  \\
-		\midrule
-		OPSB     &                 & 8.75 & 38.72    &                   &                        \\
-		OPSB QTY & 0.486           & 8.66 & 39.30    & 46.51             & 23.19                  \\
-		\midrule
-		OPSD     &                 & 6.20 & 38.89    &                   &                        \\
-		OPSD QTY & 0.559           & 6.20 & 39.29    & 46.58             & 21.55                  \\
-		\midrule
-		OPN3     &                 & 9.29 & 44.87    &                   &                        \\
-		OPN3 QTY & 0.454           & 9.18 & 45.47    & 49.12             & 20.90                  \\
-		\midrule
-		OPN4     &                 & 9.35 & 52.64    &                   &                        \\
-		OPN4 QTY & 0.307           & 9.19 & 53.08    & 50.34             & 15.48                  \\
-		\midrule
-		OPN5     &                 & 9.11 & 39.73    &                   &                        \\
-		OPN5 QTY & 0.555           & 9.02 & 40.04    & 45.58             & 18.93                  \\
-		\midrule
-		RGR      &                 & 8.34 & 31.87    &                   &                        \\
-		RGR QTY  & 0.537           & 8.29 & 32.39    & 42.86             & 21.65                  \\
-		\midrule
-		OPSX     &                 & 8.77 & 37.42    &                   &                        \\
-		OPSX QTY & 0.548           & 8.72 & 37.46    & 40.96             & 20.18                  \\
-		\midrule
-		BACR     &                 & 4.75 & 26.92    &                   &                        \\
-		BACR QTY & 0.448           & 4.75 & 27.40    & 46.67             & 25.30                  \\
-		\midrule
-		BACH     &                 & 5.34 & 26.96    &                   &                        \\
-		BACH QTY & 0.296           & 5.34 & 27.50    & 44.19             & 30.04                  \\
-		\bottomrule
-	\end{tabular}
+	\caption{Protein characteristics}
+	\label{tb:characteristics}
+	\includegraphics[width=\linewidth]{Figures/characteristics.jpg}
 \end{table}
 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
+	\caption{Protein sequence alignments}
+	\label{fig:sequences}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/superposition-human.jpg}
+	\caption{Superposition of human retinylidene proteins}
+	\label{fig:humansup}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/superposition-microbial.jpg}
+	\caption{Superposition of microbial retinylidene proteins}
+	\label{fig:microbialsup}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/pairwise.jpg}
+	\caption{Pairwise comparison of human opsins. Green: OPN1MW; red: OPN1LW; blue: OPN1SW; purple: OPN2; cyan: OPN3; gray: OPN4; olive: OPN5; orange: RGR; pink: RRH. }
+	\label{fig:pairwise}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/hydrophobicity.jpg}
+	\caption{Surface hydrophobicity}
+	\label{fig:hydrophobicity}
+\end{figure}
+
 \end{document}

### 2025-04-27 MD/plot_xvg_change_to_use.py
Run QTY trans

@@ -17,7 +17,7 @@ def plot_running_avg(data):
     x_avg = x[len(x) - len(running_avg) : ]
     plt.plot(x_avg, running_avg, label="10-ps Running Avg", color="red")
 
-filename = "WT/rmsd_transprot"
+filename = "QTY/rmsd_transprot"
 data = load_xvg(f"{filename}.xvg")
 plt.figure(figsize=(8, 5))
 plt.plot(data[:, 0], data[:, 1], label="", color="black")

### 2025-04-27 Paper/Source/manuscript.tex

@@
 
-In this paper, we apply the QTY code to redesign 9 human opsins and 3 microbial opsins. We provide superposition
+In this paper, we apply the QTY code to redesign 9 human opsins and 3 microbial opsins.
+We provide the superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY variants, and experimentally-determined structures when available.
+We also provide the comparative surface hydrophobicity of the variants.
+Furthermore, we run MD simulations of native and QTY-designed OPN2 and analyze their response to the 11-cis to all-trans isomerization of the retinal chromophore.
 
@@
 All MD simulations were conducted using GROMACS 2024.5 \citep{Abraham_2015} with the CHARMM36m all-atom force field \citep{Huang_2017}.
-The parameters for retinal were obtained from NAMD Wiki (\url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalTop} and \url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalPar}), and integrated manually into the files for the protein.
-Initial structures, configuration files and command-line codes for the simulations are publicly available at ...
+Data for retinal were obtained from NAMD Wiki (\url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalTop} for topology and \url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalPar} for parameters) and manually integrated into the protein file.
+Initial structures, configuration files, and command-line codes for the simulations are publicly available at...
 [ONLINE DATABASE TO BE PREPARED].
 
-Regarding the native OPN2, the membrane-protein system was constructed using CHARMM-GUI’s web-based membrane builder and downloaded in GROMACS format \citep{Jo_2008, Wu_2014, Lee_2016}.
+Regarding native OPN2, the membrane protein system was constructed using the web-based membrane builder CHARMM-GUI and was downloaded in GROMACS format \citep{Jo_2008, Wu_2014, Lee_2016}.
 The protein was centered in a rectangular box.
-The membrane models generated consisted 40\% POPC, 40\% POPE, 10\% POPS, and 10\% cholesterol, which simulate a rod photoreceptor disk membrane \citep{Albert_2005}.
+The generated membrane models consisted of 40\% POPC, 40\% POPE, 10\% POPS, and 10\% cholesterol, which simulate a rod photoreceptor disk membrane \citep{Albert_2005}.
 The system was solvated in TIP3P water with 150 mM NaCl.
 11-cis-retinal was manually added to the protein files.
-Electrostatics were handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm.
-System energy was minimized using the steepest descent until maximum forces converged below 1000 kJ/mol/nm.
-The standard six-step CHARMM-GUI NP$\gamma$T equilibration protocol \citep{Jo_2008} was used, with 2 125-ps NVT equilibration simulations, and 1 125-ps and 3 500-ps NP$\gamma$T equilibration simulations.
+LINCS constraints was used for constraints and Verlet integrator was used.
+Electrostatics was handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm.
+The energy of the system was minimized using the steepest descent until the maximum forces converged below 1000 kJ/mol/nm.
+The standard six-step CHARMM-GUI NP$\gamma$T equilibration protocol \citep{Jo_2008} was used, with two 125-ps NVT equilibration simulations, and one 125-ps and three 500-ps NP$\gamma$T equilibration simulations.
 Temperature and pressure were maintained at 303.15 K and 1.0 bar, respectively, using the V-rescale thermostat and C-rescale barostat with surface-tension coupling.
-The LINCS algorithm was used for constraints.
-Verlet integrator was used.
 Following equilibration, a 10-ns production MD simulation was run.
-Then, the retinal molecule was manually switched to all-trans state by rotating C13 to C15 and bonded hydrogens and methyl groups by 180 degrees around the C11-C12 bond.
+The retinal molecule was then manually switched to the all-trans state by rotating C13 to C15 and bonded hydrogen and methyl groups by 180 degrees around the C11-C12 bond.
 Energy minimization and equilibration were repeated exactly as before, and then a 200-ns production MD simulation was run.
 
-Regarding the QTY-designed OPN2, the system was constructed directly using GROMACS.
-The protein was centered in a rectangular box of identical size with that of native OPN2.
-The system was solvated in TIP3P water with 150mM NaCl.
-11-cis-retinal was manually added to the protein files.
-System energy was minimized using the steepest descent until maximum forces converged below 1000 kJ/mol/nm.
-Electrostatics were handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm.
-The equilibration process is designed to align with that of the native protein, with 1 250-ps NVT equilibration simulation, and 1 125-ps and 1 1500-ps NPT equilibration simulations.
-Temperature and pressure were maintained at 303.15 K and 1.0 bar, respectively, using the V-rescale thermostat and C-rescale barostat with isotropic coupling.
-The LINCS algorithm was used for constraints.
-Verlet integrator was used.
-Following equilibration, a 10-ns production MD simulation was run.
-Then, the retinal molecule was manually switched to all-trans state by rotating C13 to C15 and bonded hydrogens and methyl groups by 180 degrees around the C11-C12 bond.
-Energy minimization and equilibration were repeated exactly as before, and then a 200-ns production MD simulation was run.
+Regarding QTY-designed OPN2, the system was constructed directly using GROMACS.
+The protein was centered in a rectangular box with dimensions equivalent to those of the native OPN2.
+The equilibration involved a sequence of simulations: a 250-ps NVT equilibration, followed by 125-ps and 1500-ps NPT equilibrations, totaling an equilibration duration that matches that of the natural OPN2.
+All other configurations and parameters are identical to those of the original OPN2.
 

### 2025-04-27 Paper/Source/manuscript.tex
Complete intro and methodology draft. Structure the results and discussion sections.

@@
 
-\keywords{Keyword 1; Keyword 2; Keyword 3}
+\keywords{hydrophobic to hydrophilic conversion; membrane proteins; protein design; QTY code; water-soluble retinylidene proteins; water-soluble opsins; activation of QTY variants of rhodopsin}
 \begin{abstract}
@@
 
-Retinylidene proteins are photochemically reactive proteins that is bound to or can bind to retinal (vitamin-A aldehyde) as their chromophore \citep{Spudich_2000}.
-We will use the term ``opsin'' interchangeably with ``retinylidene proteins'', despite that is sometimes refers specifically to the chromophore-free apoprotein.
-Retinylidene proteins are divided into two groups, animal opsins and microbial opsins, which are evolutionarily distinct but share common features such as haveing 7 transmembrane (TM) domains and a retinal-binding lysine residue \citep{Yee_2013, Spudich_2000}.
+Retinylidene proteins are photochemically reactive proteins that are bound to or can bind to retinal (vitamin A aldehyde) as their chromophore \citep{Spudich_2000}.
+We will use the term ``opsin'' interchangeably with ``retinylidene protein'', despite the fact that ``opsin'' sometimes refers specifically to the chromophore-free apoprotein.
+Retinylidene proteins are divided into two groups, animal opsins and microbial opsins, which are evolutionarily distinct but share common characteristics such as having 7 transmembrane (TM) domains and a retinal binding lysine residue \citep{Yee_2013, Spudich_2000}.
 In this study, we will consider 9 animal opsins and 3 microbial opsins.
@@
 \citep{Sakmar_2002, Nordstrom_2011, Zhou_2019}.
-Almost all animal opsins include a lysine residue that forms a Schiff base linkage with retinal \citep{Bownds_1967, Guhmann_2022}.
+Almost all animal opsins include a lysine residue that forms a Schiff base link with the retinal \citep{Bownds_1967, Guhmann_2022}.
 When retinal absorbs a photon, it isomerizes, usually changing from 11-cis to all-trans.
@@
 Proton transfer plays a major role in this process \citep{Mahalingam_2008}.
-During this process, TM6 characteristically moves outward, activating the G-protein.
+During this process, TM6 is characteristically moved outward, activating the G-protein.
 
-In this study, we selected 9 opsins expressed in the human nervous system: OPN1MW (\href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (\href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04000}), OPN1SW (\href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (\href{https://www.uniprot.org/uniprotkb/P08100/entry}{P08100}), OPN3 (\href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (\href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (\href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (\href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (\href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}).
+In this study, we selected 9 opsins expressed in the human nervous system: OPN1MW (\href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (\href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04001}), OPN1SW (\href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (\href{https://www.uniprot.org/uniprotkb/P08100/entry}{P04001}), OPN3 (\href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (\href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (\href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (\href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (\href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}).
 They belong to several evolutionarily distinct families of animal opsins \citep{Terakita_2005, Shichida_2009}.
@@
 \textbf{OPN5} (Opsin 5), also known as neuropsin, is activated by blue and ultraviolet A light \citep{Tarttelin_2003, Yamashita_2010}.
-It is expressed in the retina and contributes to the regulation of light-dependent vascular development \citep{Nguyen_2019} and the photoentrainment in the cornea and retina \citep{Buhr_2015}.
+It is expressed in the retina and contributes to the regulation of light-dependent vascular development \citep{Nguyen_2019} and photoentrainment in the cornea and retina \citep{Buhr_2015}.
 
-\textbf{RGR} (RPE-retinal GPCR) is expressed in the RPE (Retinal Pigmented Epithelium) and M\"uller cells in the retina \citep{Shen_1994}.
+\textbf{RGR} (RPE-retinal GPCR) is expressed in RPE (Retinal Pigmented Epithelium) and M\"uller cells in the retina \citep{Shen_1994}.
 Unlike the aforementioned human opsins, RGR preferentially binds all-trans-retinal and may catalyze its isomerization into 11-cis-retinal via a retinochrome-like mechanism \citep{Radu_2008}.
-It plays a role in light-dependent synthesis of visual chromophore \citep{Radu_2008}.
+It plays a role in the light-dependent synthesis of visual chromophore \citep{Radu_2008}.
 
@@
 The isomerization of retinal is usually from all-trans to 13-cis, different from that in animal opsins \citep{Findlay_1986, Spudich_2000}.
-Additionally, bacterial opsins often form oligomers to carry out their functions \citep{Taguchi_2023, Gmelin_2007, Shan_2024}.
+In addition, bacterial opsins often form oligomers to carry out their functions \citep{Taguchi_2023, Gmelin_2007, Shan_2024}.
 
@@
 BACH and ChR2 are among the first optogenetic tools \citep{Zhang_2007, Han_2007}.
-BACH is used for inhibition while ChR2 is used for excitation.
+BACH is used for inhibition, while ChR2 is used for excitation.
 
 We have asked if retinylidene proteins could be redesigned to be more soluble.
-Retinylidene proteins are all integral membrane proteins with seven transmembrane alpha-helices embedded in a lipid bilayer.
-Due the hydrophobic properties of transmembrane domains, they are not water-soluble without the aid of detergents.
+Retinylidene proteins are all integral membrane proteins with seven transmembrane alpha helices embedded in a lipid bilayer.
+Because of the hydrophobic properties of the transmembrane domains, they are not water-soluble without the aid of detergents.
 
-Bacteriorhodopsin has been the subject of several protein-solubilizing studies, though to limited success \citep{Sirokman_1993, Gibas_1997, Mitra_2002}.
+Bacteriorhodopsin has been the subject of several protein-solubilizing studies, though with limited success \citep{Sirokman_1993, Gibas_1997, Mitra_2002}.
 Recently, researchers leveraged a neural network, SolubleMPNN, which was built upon ProteinMPNN, to engineer soluble variants of bacteriorhodopsin while maintaining its ligand-binding ability and light-sensing function \citep{Nikolaev_2024}.
 
-Instead of taking a computational approach, we applied the QTY code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins.
-There are structural similarities between hydrophobic and polar amino acids: leucine (L) vs glutamine (Q); isoleucine (I)/valine (V) vs threonine (T); and phenylalanine (F) vs tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}.
-This justifies residue replacement of hydrophobic aminoacids with polar ones.
-We initially applied the QTY (Glutamine, Threonine, Tyrosine) code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding activities and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}.
+Instead of taking a computational approach, we applied the QTY (Glutamine, Threonine, Tyrosine) code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins.
+There are structural similarities between hydrophobic and polar amino acids: leucine (L) vs.
+glutamine (Q); isoleucine (I) / valine (V) vs.
+threonine (T); and phenylalanine (F) vs.
+tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}.
+This justifies the replacement of hydrophobic amino acids with polar ones.
+We initially applied the QTY code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding activities and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}.
 We have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.
@@
 It greatly facilitated the study of QTY-designed protein variants.
-Subsequently, AlphaFold3 was released in May 2024, featuring an enhanced architecture and improved efficiency \citep{Abramson_2024}.
-Furthermore, AlphaFold3 enabled accurate prediction of complexes of multiple proteins as well as complexes with nucleic acids and certain small molecules.
+Subsequently, AlphaFold3 was released in May 2024, featuring improved architecture and improved efficiency \citep{Abramson_2024}.
+Furthermore, AlphaFold3 enabled the accurate prediction of complexes of multiple proteins, as well as complexes with nucleic acids and certain small molecules.
 QTY studies have made use of these new features \citep{Chen_2025, Johnsson_2025}.
@@
 Its 5.0 version was released in 2015 \citep{Abraham_2015}.
-GROMACS enables efficient and realistic simulation of biomolecular systems, and it has been used to investigate structural and functional properties of QTY-designed protein variants in various studies \citep{Karagol_2024, Li_Tang_2024, Smorodina_2024, Li_Wang_2024, Johnsson_2025}.
+GROMACS enables an efficient and realistic simulation of biomolecular systems, and has been used to investigate the structural and functional properties of QTY-designed protein variants in various studies \citep{Karagol_2024, Li_Tang_2024, Smorodina_2024, Li_Wang_2024, Johnsson_2025}.
 
@@
 We provide the superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY variants, and experimentally-determined structures when available.
-We also provide the comparative surface hydrophobicity of the variants.
+We also provide a comparison of the surface hydrophobicity of the variants.
 Furthermore, we run MD simulations of native and QTY-designed OPN2 and analyze their response to the 11-cis to all-trans isomerization of the retinal chromophore.
@@
 
-Results
+\subsection*{The QTY code}
 
-* discuss the QTY code
+Discuss the QTY code.
 
-* describe and explain Table1
+\subsection*{Retinylidene proteins sequence alignments and other characteristics}
 
-* entrance of retinal is posteriori folding, so it is safe that we predict chromophore-free form
+Describe and discuss Table~\ref{tb:characteristics} (native and QTY protein characteristics) // NOTE: the binding of retinal is posterior to folding, so it is safe to say that we predicted chromophore-free form (i.e.
+folding does not rely on retinal).
 
-* describe and explain Fig1
+\subsection*{Superpositions of AlphaFold3-predicted native human opsins, their water-soluble QTY variants, and experimentally determined structures}
 
-* describe and explain Fig2
-	- I need more discussion here
+Describe and discuss Fig.~\ref{fig:humansup} (AF3 native - AF3 QTY - experimental superpositions of human opsins).
 
-* describe and explain Fig3
+\subsection*{Pairwise superpositions among AlphaFold3-predicted native human opsins and among their water-soluble QTY variants}
 
-* discuss AlphaFold3 predictions
+Describe and discuss Fig.~\ref{fig:pairwise} (pairwise superpositions of human opsins) // NOTE: the QTY pairwise superpositions roughly maintains the trends in the native superpositions.
 
-* describe, explain, discuss MD results (Fig3 and Fig4)
-        - no changes to the NPxxY motif or retinal-binding Lys
-        - "The ionic environment of the RSB, defined by the residues of the binding pocket, dictates the spectral and kinetic characteristics of each individual protein." - \citep{Fenno_2011}
-	- I need more discussion here
+\subsection*{Superpositions of AlphaFold3-predicted native microbial opsins, their water-soluble QTY variants, and experimentally determined structures}
 
-* future scopes and potential applications
+Describe and discuss Fig.~\ref{fig:microbialsup} (AF3 native - AF3 QTY - experimental superimpositions of microbial opsins) // NOTE: comment specifically on the formation of dimers and trimers.
 
-* conclusion
+\subsection*{Analysis of the hydrophobic surface of native retinylidene proteins and their water-soluble QTY variants}
+
+Describe and discuss Fig.~\ref{fig:hydrophobicity} (surface hydrophobicity).
+
+\subsection*{AlphaFold3 predictions}
+
+Discuss the role of AlphaFold3 predictions.
+
+\subsection*{Simulation of 11-cis to all-trans isomerization of retinal in native OPN2 and its QTY variant}
+
+Describe, explain, discuss MD simulation results.
+// NOTE: there were no changes to the NPxxY motif or retinal-binding Lys; "The ionic environment of the RSB, defined by the residues of the binding pocket, dictates the spectral and kinetic characteristics of each individual protein." \citep{Fenno_2011}, so QTY variant may have different absorption peak.
+
+\subsection*{Future scopes and potential applications}
+
+* Future scopes and potential applications.
+
+\subsection*{Conclusion}
+
+* Conclusion
 
@@
 
-The native protein sequences for OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, RRH, BACR, BACH, and ChR2 were attained from UniProt (\url{https://www.uniprot.org}).
+The native protein sequences for OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, RRH, BACR, BACH, and ChR2 were obtained from UniProt (\url{https://www.uniprot.org}).
 The sequence for ChR2 was truncated according to the experimental structure in RCSB PDB (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
-The QTY designs were realized through the Protein Solubilizing Server (\url{https://pss.sjtu.edu.cn/}) \citep{Tao_2022}.
-For ChR2, secondary structure was provided to the server in SS3 format according to the RCSB PDB structure.
+The QTY designs were performed through the Protein Solubilizing Server (\url{https://pss.sjtu.edu.cn/}) \citep{Tao_2022}.
+For ChR2, the secondary structure was provided to the server in SS3 format according to the RCSB PDB structure.
 
@@
 
-We predicted the structures of the native proteins and their QTY variants using the AlphaFold3 website (\url{https://alphafoldserver.com}) \citep{Abramson_2024}.
-For microbial opsins, the dimers and trimers had identical subunits, i.e., were homodimers and homotrimers.
-In AlphaFold3, this is achieved by altering the number of protein copies.
+We predicted the structures of native proteins and their QTY variants using the AlphaFold3 website (\url{https://alphafoldserver.com}) \citep{Abramson_2024}.
+For microbial opsins, the dimers and trimers had identical subunits, i.e., they were homodimers and homotrimers.
+In AlphaFold3, this was achieved by altering the number of protein copies.
 
@@
 
-PDB files for native protein structures determined experimentally using X-ray diffraction or electron microscopy were taken from RCSB PDB: OPN2 (\href{https://www.rcsb.org/structure/5W0P}{5W0P}), BACR (\href{https://www.rcsb.org/structure/7XJC}{7XJC}), BACH (\href{https://www.rcsb.org/structure/2JAF}{2JAF}), ChR2 (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
+PDB files for native protein structures determined experimentally by X-ray diffraction or electron microscopy were taken from RCSB PDB: OPN2 (\href{https://www.rcsb.org/structure/5W0P}{5W0P}), BACR (\href{https://www.rcsb.org/structure/7XJC}{7XJC}), BACH (\href{https://www.rcsb.org/structure/2JAF}{2JAF}), ChR2 (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
 The AlphaFold3-predicted native and QTY variants were taken directly from the most probable predicted structure.
-Superpositions were performs via the command ``super'' in PyMOL (\url{https://pymol.org}).
-We removed unstructured loops at N and C terminals for clarity.
+Superpositions were performed via the command ``super'' in PyMOL (\url{https://pymol.org}).
+We remove unstructured loops at the N and C terminals for the sake of clarity.
 
@@
 
-We used PyMOL (\url{https://pymol.org}) to superpose the native predicted protein structures, their QTY variants, and the experimental structures for those proteins where these existed.
+We used PyMOL (\url{https://pymol.org}) to superpose the native predicted protein structures, their QTY variants, and the experimental structures for the proteins where these existed.
 We then used UCSF ChimeraX (\url{https://www.cgl.ucsf.edu/chimerax/}) to render each protein model with hydrophobicity patches.
@@
 
-All MD simulations and analyses were executed on a desktop computer with Intel Xeon Platinum 8352V Processor, 256GB RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 24GB VRAM each.
+All MD simulations and analyses were executed on a desktop computer with Intel Xeon Platinum 8352V Processor, 256 GB RAM, and 2 NVIDIA GPU (GeForce RTX 4090) with 24 GB VRAM each.
 All MD simulations were conducted using GROMACS 2024.5 \citep{Abraham_2015} with the CHARMM36m all-atom force field \citep{Huang_2017}.
@@
 11-cis-retinal was manually added to the protein files.
-LINCS constraints was used for constraints and Verlet integrator was used.
+LINCS constraints were used for constraints, and Verlet integrator was used.
 Electrostatics was handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm.
@@
 Regarding QTY-designed OPN2, the system was constructed directly using GROMACS.
-The protein was centered in a rectangular box with dimensions equivalent to those of the native OPN2.
+The protein was centered in a rectangular box with dimensions equivalent to those of native OPN2.
 The equilibration involved a sequence of simulations: a 250-ps NVT equilibration, followed by 125-ps and 1500-ps NPT equilibrations, totaling an equilibration duration that matches that of the natural OPN2.
@@
 
-ANALYSIS METHODS TO BE ADDED.
+[ANALYSIS METHODS OF MD SIMULATION RESULTS, TO BE ADDED.]
 
@@
 
-The data for ... can be found at... [ONLINE DATABASE TO BE PREPARED]
+The data for... can be found at... [ONLINE DATABASE TO BE PREPARED]
 
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 
-Thanks to ... for ... [TO BE ADDED]
+Thanks to... for... [TO BE ADDED]
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{Figures/superposition-microbial.jpg}
-	\caption{Superposition of microbial retinylidene proteins}
-	\label{fig:microbialsup}
+	\includegraphics[width=\linewidth]{Figures/pairwise.jpg}
+	\caption{Pairwise comparison of human opsins. Green: OPN1MW; red: OPN1LW; blue: OPN1SW; purple: OPN2; cyan: OPN3; gray: OPN4; olive: OPN5; orange: RGR; pink: RRH. }
+	\label{fig:pairwise}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\linewidth]{Figures/pairwise.jpg}
-	\caption{Pairwise comparison of human opsins. Green: OPN1MW; red: OPN1LW; blue: OPN1SW; purple: OPN2; cyan: OPN3; gray: OPN4; olive: OPN5; orange: RGR; pink: RRH. }
-	\label{fig:pairwise}
+	\includegraphics[width=\linewidth]{Figures/superposition-microbial.jpg}
+	\caption{Superposition of microbial retinylidene proteins}
+	\label{fig:microbialsup}
 \end{figure}

### 2025-04-27 MD/plot_xvg_change_to_use.py
Prepare MD simulation results demo

@@ -10,21 +10,22 @@ def load_xvg(filename):
     return np.array(data)
 
 def plot_running_avg(data):
-    window_size = 10
+    window_size = 1000
     x = data[:, 0]
     y = data[:, 1]
     running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
     x_avg = x[len(x) - len(running_avg) : ]
     plt.plot(x_avg, running_avg, label="10-ps Running Avg", color="red")
 
-filename = "QTY/rmsd_transprot"
+filename = "WT/rmsd_transprot"
 data = load_xvg(f"{filename}.xvg")
 plt.figure(figsize=(8, 5))
 plt.plot(data[:, 0], data[:, 1], label="", color="black")
-#plot_running_avg(data)
+plot_running_avg(data)
 plt.xlabel("time (ns)")
 plt.ylabel("RMSD (nm)")
 plt.title("")
+plt.ylim(0, 0.35)
 #plt.xlim(-180, 180)
 #plt.legend()
 plt.grid(False)

### 2025-04-29 Paper/Source/supp.tex
Write supplementary material

\documentclass[fleqn,12pt]{supp}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul, float, hyperref}
\hypersetup{hidelinks}
\usepackage[utf8]{inputenc}

\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }

\title{Supplementary Information}
\author{}

\begin{document}

\flushbottom
\maketitle

\vspace{-35pt}
\section*{A Structural and Functional Bioinformatics Study of QTY-designed Retinylidene Proteins}

\subsection*{Siqi Pan and Shuguang Zhang}

\begin{figure}[H]
    \label{tb:sequence}
    \caption{\textbf{The enlarge protein sequence alignments of 12 retinylidene proteins with their water-soluble QTY analogs from Figure 1.} The symbols $|$ and $*$ indicate that amino acids are identical and different respectively. Amino acids L, V, I and F in TM (transmembrane) alpha helices are replaced with Q, T, Y and Y respectively. The alpha helices (blue) are shown above the protein sequences. \\
    The alignments are: 
    \textbf{a)} OPN1MW vs. OPN1MW$^{\textrm{QTY}}$, 
    \textbf{b)} OPN1LW vs. OPN1LW$^{\textrm{QTY}}$, 
    \textbf{c)} OPN1SW vs. OPN1SW$^{\textrm{QTY}}$, 
    \textbf{d)} OPN2 vs. OPN2$^{\textrm{QTY}}$, 
    \textbf{e)} OPN3 vs. OPN3$^{\textrm{QTY}}$, 
    \textbf{f)} OPN4 vs. OPN4$^{\textrm{QTY}}$, 
    \textbf{g)} OPN5 vs. OPN5$^{\textrm{QTY}}$, 
    \textbf{h)} RGR vs. RGR$^{\textrm{QTY}}$, 
    \textbf{i)} RRH vs. RRH$^{\textrm{QTY}}$, 
    \textbf{j)} BACR vs. BACR$^{\textrm{QTY}}$, 
    \textbf{k)} BACH vs. BACH$^{\textrm{QTY}}$, 
    \textbf{l)} ChR2 vs. ChR2$^{\textrm{QTY}}$. }
    \textbf{a)} OPN1MW vs. OPN1MW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1mw.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{b)} OPN1LW vs. OPN1LW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1lw.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{c)} OPN1SW vs. OPN1SW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1sw.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{d)} OPN2 vs. OPN2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn2.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{e)} OPN3 vs. OPN3$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn3.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{f)} OPN4 vs. OPN4$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn4.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{g)} OPN5 vs. OPN5$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn5.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{h)} RGR vs. RGR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/rgr.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{i)} RRH vs. RRH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/rrh.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{j)} BACR vs. BACR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/bacr.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{k)} BACH vs. BACH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/bach.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{l)} ChR2 vs. ChR2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/chr2.jpg}
\end{figure}

\begin{figure}[H]
    \label{tb:af3}
    \caption{\textbf{AlphaFold3 prediction accuracy: plDDT, PAE, ipTM, and pTM scores.} \\
    The scores are displayed for the following proteins: 
    \textbf{a)} OPN1MW$^{\textrm{QTY}}$,
    \textbf{b)} OPN1LW$^{\textrm{QTY}}$,
    \textbf{c)} OPN1SW$^{\textrm{QTY}}$,
    \textbf{d)} OPN2$^{\textrm{QTY}}$,
    \textbf{e)} OPN3$^{\textrm{QTY}}$,
    \textbf{f)} OPN4$^{\textrm{QTY}}$,
    \textbf{g)} OPN5$^{\textrm{QTY}}$,
    \textbf{h)} RGR$^{\textrm{QTY}}$,
    \textbf{i)} RRH$^{\textrm{QTY}}$,
    \textbf{j)} BACR$^{\textrm{QTY}}$ monomer,
    \textbf{k)} BACH$^{\textrm{QTY}}$ monomer,
    \textbf{l)} ChR2$^{\textrm{QTY}}$ monomer,
    \textbf{m)} BACR$^{\textrm{QTY}}$ trimer,
    \textbf{n)} BACH$^{\textrm{QTY}}$ trimer,
    \textbf{o)} ChR2$^{\textrm{QTY}}$ dimer.}
    \textbf{a)} OPN1MW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 opn1mw qty.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{b)} OPN1LW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 opn1lw qty.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{c)} OPN1SW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 opn1sw qty.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{d)} OPN2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 opn2 qty.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{e)} OPN3$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 opn3 qty.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{f)} OPN4$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 opn4 qty.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{g)} OPN5$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 opn5 qty.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{h)} RGR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 rgr qty.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{i)} RRH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 rrh qty.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{j)} BACR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bacr qty mono.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{k)} BACH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bach qty mono.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{l)} ChR2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 chr2 qty mono.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{m)} BACR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bacr qty tri.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{n)} BACH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 bach qty tri.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{o)} ChR2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 chr2 qty di.jpg}
\end{figure}

\end{document}

### 2025-04-29 MD/plot_xvg_change_to_use.py
Concatenate cis and trans traj, draw RMSD graphs

@@ -9,23 +9,24 @@ def load_xvg(filename):
                 data.append([float(x) for x in line.split()])
     return np.array(data)
 
-def plot_running_avg(data):
+def plot_running_avg(x, y):
     window_size = 1000
-    x = data[:, 0]
-    y = data[:, 1]
     running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
     x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label="10-ps Running Avg", color="red")
+    plt.plot(x_avg, running_avg, label="X-ps Running Avg", color="red")
 
-filename = "WT/rmsd_transprot"
+filename = "WT/rmsd_wt_SOLU"
 data = load_xvg(f"{filename}.xvg")
+x = [time - 10 for time in data[:, 0]]
+y = data[:, 1]
 plt.figure(figsize=(8, 5))
-plt.plot(data[:, 0], data[:, 1], label="", color="black")
-plot_running_avg(data)
+plt.plot(x, y, label="", color="black")
+plot_running_avg(x, y)
 plt.xlabel("time (ns)")
 plt.ylabel("RMSD (nm)")
 plt.title("")
-plt.ylim(0, 0.35)
+plt.ylim(0, 0.4)
+plt.axvline(x=0, color='b', linestyle='--')
 #plt.xlim(-180, 180)
 #plt.legend()
 plt.grid(False)

### 2025-04-29 MD/plot_xvg_change_to_use.py
create QTY-cut folder, getting ready to run qty

@@ -15,19 +15,19 @@ def plot_running_avg(x, y):
     x_avg = x[len(x) - len(running_avg) : ]
     plt.plot(x_avg, running_avg, label="X-ps Running Avg", color="red")
 
-filename = "WT/rmsd_wt_SOLU"
+filename = "QTY/radius_cis_to_trans_ref_cismd"
 data = load_xvg(f"{filename}.xvg")
-x = [time - 10 for time in data[:, 0]]
+x = [time/1000 - 10 for time in data[:, 0]]
 y = data[:, 1]
 plt.figure(figsize=(8, 5))
 plt.plot(x, y, label="", color="black")
 plot_running_avg(x, y)
 plt.xlabel("time (ns)")
-plt.ylabel("RMSD (nm)")
+#plt.ylabel("RMSD (nm)")
 plt.title("")
-plt.ylim(0, 0.4)
+#plt.ylim(0, 1.2)
 plt.axvline(x=0, color='b', linestyle='--')
-#plt.xlim(-180, 180)
+#plt.xlim(-10, 0)
 #plt.legend()
 plt.grid(False)
 plt.savefig(f"{filename}.pdf", format="pdf", bbox_inches="tight")

### 2025-04-30 MD/QTY-cut/Delete_atom_gro.py
begin run QTY-cut

@@ -1,0 +1,30 @@
+import re
+
+def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms):
+    with open(file_path, "r") as file:
+        lines = file.readlines()
+    updated_lines = []
+    num_deleted = 0
+
+    for line in lines:
+        line_splitted = line.split()
+        if len(line_splitted) != 6:
+            updated_lines.append(line)
+            continue
+        atom_index = int(line_splitted[2])
+        if atom_index in target_delete_atoms:
+            num_deleted += 1
+            continue
+        new_line_splitted = line_splitted[:2] + [str(atom_index - num_deleted)] + line_splitted[3:]
+        formatted_line = "{:>8}{:>7}{:>5}{:>8}{:>8}{:>8}\n".format(*new_line_splitted)
+        updated_lines.append(formatted_line)
+
+    with open(write_path, "w") as file:
+        file.writelines(updated_lines)
+
+file_path = "complex.gro"
+write_path = "complex_new.gro"
+target_delete_atoms = [i for i in range(4966, 5303)]
+delete_atom_and_update_indices(file_path, write_path, target_delete_atoms)
+
+# Remember to manually edit the total atom count!

### 2025-04-30 MD/QTY-cut/Delete_atom_ndx.py

@@ -1,0 +1,41 @@
+import re
+
+def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms):
+    with open(file_path, "r") as file:
+        lines = file.readlines()
+    updated_lines = []
+
+    section = []
+    for line in lines:
+        if "[" in line:
+            updated_line = ""
+            count = 0
+            for index in section:
+                if count == 15:
+                    updated_lines.append(updated_line + "\n")
+                    count = 0
+                    updated_line = ""
+                updated_line += index + " "
+            updated_lines.append(line)
+            section = []
+            continue
+        line_splitted = line.split()
+        for index in line_splitted:
+            if int(index) not in target_delete_atoms:
+                section.append(index)
+    count = 0
+    for index in section:
+        if count == 15:
+            updated_lines.append(updated_line + "\n")
+            count = 0
+            updated_line = ""
+        updated_line += index + " "
+        updated_lines.append(line)
+    
+    with open(write_path, "w") as file:
+        file.writelines(updated_lines)
+
+file_path = "index.ndx"
+write_path = "index_new.ndx"
+target_delete_atoms = [i for i in range(4966, 5303)]
+delete_atom_and_update_indices(file_path, write_path, target_delete_atoms)

### 2025-05-02 MD/QTY-cut/Delete_atom_gro.py
run qty from em again; run qty-cut cis with water deleted.

@@ -1,10 +1,12 @@
 import re
 
-def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms):
+def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms, target_delete_residues):
     with open(file_path, "r") as file:
         lines = file.readlines()
     updated_lines = []
     num_deleted = 0
+    num_res_deleted = 0
+    res_deleted = []
 
     for line in lines:
         line_splitted = line.split()
@@ -12,19 +14,45 @@ def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms):
             updated_lines.append(line)
             continue
         atom_index = int(line_splitted[2])
+        line_0 = line_splitted[0]
+        res_index = int(line_0[:-3])
+        res_index -= num_res_deleted
+        res_name = line_0[-3:]
+        if atom_index > 62450:
+            pass
         if atom_index in target_delete_atoms:
             num_deleted += 1
+            if res_index in target_delete_residues and res_index not in res_deleted:
+                num_res_deleted += 1
+                res_deleted.append(res_index)
             continue
-        new_line_splitted = line_splitted[:2] + [str(atom_index - num_deleted)] + line_splitted[3:]
-        formatted_line = "{:>8}{:>7}{:>5}{:>8}{:>8}{:>8}\n".format(*new_line_splitted)
+        new_line_splitted = [str(res_index), res_name, line_splitted[1], str(atom_index - num_deleted)] + line_splitted[3:]
+        formatted_line = "{:>5}{:>3}{:>7}{:>5}{:>8}{:>8}{:>8}\n".format(*new_line_splitted)
         updated_lines.append(formatted_line)
 
     with open(write_path, "w") as file:
         file.writelines(updated_lines)
 
-file_path = "complex.gro"
-write_path = "complex_new.gro"
-target_delete_atoms = [i for i in range(4966, 5303)]
-delete_atom_and_update_indices(file_path, write_path, target_delete_atoms)
+file_path = "solv_ions_again.gro"
+write_path = "solv_ions_again_new.gro"
+target_delete_atoms = [
+    62459, 62460, 62461, 
+    62501, 62502, 62503, 
+    78107, 78108, 78109, 
+    78110, 78111, 78112, 
+    78116, 78117, 78118, 
+    78146, 78147, 78148, 
+    78167, 78168, 78169
+]
+target_delete_residues = [
+    19472,
+    19486,
+    24688,
+    24689,
[…]

### 2025-05-02 MD/QTY-cut/Delete_atom_gro_large.py

@@ -1,0 +1,66 @@
+import re
+
+def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms, target_delete_residues):
+    with open(file_path, "r") as file:
+        lines = file.readlines()
+    updated_lines = []
+    num_deleted = 0
+    num_res_deleted = 0
+    res_deleted = []
+
+    for line in lines:
+        line_splitted = line.split()
+        if len(line_splitted) == 5:
+            line_splitted = line_splitted[:1] + [line_splitted[1][:-5], line_splitted[1][-5:]] + line_splitted[2:]
+        elif len(line_splitted) != 6:
+            updated_lines.append(line)
+            continue
+        atom_index = int(line_splitted[2])
+        line_0 = line_splitted[0]
+        res_index = int(line_0[:-3])
+        res_index -= num_res_deleted
+        res_name = line_0[-3:]
+        if atom_index in target_delete_atoms and num_deleted < len(target_delete_atoms):
+            num_deleted += 1
+            if res_index in target_delete_residues and res_index not in res_deleted:
+                num_res_deleted += 1
+                res_deleted.append(res_index)
+            continue
+        new_line_splitted = [str(res_index), res_name, line_splitted[1], str(atom_index - num_deleted)] + line_splitted[3:]
+        formatted_line = ""
+        formatted_line = "{:>5}{:>3}{:>7}{:>5}{:>8}{:>8}{:>8}\n".format(*new_line_splitted)
+        updated_lines.append(formatted_line)
+
+    with open(write_path, "w") as file:
+        file.writelines(updated_lines)
+
+file_path = "solv_ions_again.gro"
+write_path = "solv_ions_again_new.gro"
+target_delete_atoms = [
+    62459, 62460, 62461, 
+    62501, 62502, 62503, 
+    78107, 78108, 78109, 
+    78110, 78111, 78112, 
+    78116, 78117, 78118, 
+    78146, 78147, 78148, 
+    78167, 78168, 78169
+]
+target_delete_residues = [
+    19472,
+    19486,
+    24688,
+    24689,
+    24691,
+    24701,
+    24708
+]
+delete_atom_and_update_indices(file_path, write_path, target_delete_atoms, target_delete_residues)
+
+# Remember to manually edit the total atom count!
+
+# when there are over 10000 atoms, edit things like:
[…]

### 2025-05-02 MD/plot_xvg_change_to_use.py

@@ -15,15 +15,15 @@ def plot_running_avg(x, y):
     x_avg = x[len(x) - len(running_avg) : ]
     plt.plot(x_avg, running_avg, label="X-ps Running Avg", color="red")
 
-filename = "QTY/radius_cis_to_trans_ref_cismd"
+filename = "QTY-cut/rmsd_cis_md_again"
 data = load_xvg(f"{filename}.xvg")
-x = [time/1000 - 10 for time in data[:, 0]]
+x = [time - 10 for time in data[:, 0]]
 y = data[:, 1]
 plt.figure(figsize=(8, 5))
 plt.plot(x, y, label="", color="black")
 plot_running_avg(x, y)
 plt.xlabel("time (ns)")
-#plt.ylabel("RMSD (nm)")
+plt.ylabel("RMSD (nm)")
 plt.title("")
 #plt.ylim(0, 1.2)
 plt.axvline(x=0, color='b', linestyle='--')

### 2025-05-02 MD/QTY-cut/Delete_atom_gro_large.py
run qty_cut_again (deleted water after solv_ions step) and qty_cut_again_delwater (deleted water after both solv_ions step and trans_em step)

@@ -7,6 +7,7 @@ def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms, t
     num_deleted = 0
     num_res_deleted = 0
     res_deleted = []
+    reached100000 = False
 
     for line in lines:
         line_splitted = line.split()
@@ -20,13 +21,17 @@ def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms, t
         res_index = int(line_0[:-3])
         res_index -= num_res_deleted
         res_name = line_0[-3:]
+        if reached100000:
+           atom_index += 100000 
+        if atom_index == 99999:
+            reached100000 = True
         if atom_index in target_delete_atoms and num_deleted < len(target_delete_atoms):
             num_deleted += 1
             if res_index in target_delete_residues and res_index not in res_deleted:
                 num_res_deleted += 1
                 res_deleted.append(res_index)
             continue
-        new_line_splitted = [str(res_index), res_name, line_splitted[1], str(atom_index - num_deleted)] + line_splitted[3:]
+        new_line_splitted = [str(res_index), res_name, line_splitted[1], str((atom_index - num_deleted) % 100000)] + line_splitted[3:]
         formatted_line = ""
         formatted_line = "{:>5}{:>3}{:>7}{:>5}{:>8}{:>8}{:>8}\n".format(*new_line_splitted)
         updated_lines.append(formatted_line)
@@ -34,25 +39,41 @@ def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms, t
     with open(write_path, "w") as file:
         file.writelines(updated_lines)
 
-file_path = "solv_ions_again.gro"
-write_path = "solv_ions_again_new.gro"
+file_path = "trans_em_again.gro"
+write_path = "trans_em_again_delwater.gro"
 target_delete_atoms = [
-    62459, 62460, 62461, 
-    62501, 62502, 62503, 
-    78107, 78108, 78109, 
-    78110, 78111, 78112, 
-    78116, 78117, 78118, 
-    78146, 78147, 78148, 
-    78167, 78168, 78169
+    5066,   5067,   5068, 
+    7994,   7995,   7996, 
+    8051,   8052,   8053, 
+    39665,  39666,  39667, 
+    62339,  62340,  62341, 
+    62549,  62550,  62551, 
+    67952,  67953,  67954, 
+    78410,  78411,  78412, 
[…]

### 2025-05-02 MD/QTY-cut/Delete_atom_ndx.py

@@ -1,41 +1,0 @@
-import re
-
-def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms):
-    with open(file_path, "r") as file:
-        lines = file.readlines()
-    updated_lines = []
-
-    section = []
-    for line in lines:
-        if "[" in line:
-            updated_line = ""
-            count = 0
-            for index in section:
-                if count == 15:
-                    updated_lines.append(updated_line + "\n")
-                    count = 0
-                    updated_line = ""
-                updated_line += index + " "
-            updated_lines.append(line)
-            section = []
-            continue
-        line_splitted = line.split()
-        for index in line_splitted:
-            if int(index) not in target_delete_atoms:
-                section.append(index)
-    count = 0
-    for index in section:
-        if count == 15:
-            updated_lines.append(updated_line + "\n")
-            count = 0
-            updated_line = ""
-        updated_line += index + " "
-        updated_lines.append(line)
-    
-    with open(write_path, "w") as file:
-        file.writelines(updated_lines)
-
-file_path = "index.ndx"
-write_path = "index_new.ndx"
-target_delete_atoms = [i for i in range(4966, 5303)]
-delete_atom_and_update_indices(file_path, write_path, target_delete_atoms)

### 2025-05-02 Paper/Source/manuscript.tex
Write supplementary material
cancel line numbering and prepare to convert to word

@@
-\documentclass[fleqn,10pt,lineno]{manuscript}
+\documentclass[fleqn,10pt]{manuscript}
 %%\usepackage{setspace}
@@
 
-\subsection*{The QTY code}
+\subsection*{The rationale of the QTY code}
 
@@
 
+MD Results
+
+* different states - binding pocket residues + ligand orientation
+
+* bond length, angle, dihedral, non-bonded interaction lengths graph
+
+* by-helix rmsd
+
+* by-residue IE
+
+* hbond
+
+* overall rmsd, gyrate, rmsf, IE
+
 \subsection*{Future scopes and potential applications}
 
-* Future scopes and potential applications.
+Future scopes and potential applications.
 
@@
 
-* Conclusion
+Conclusion
 
@@
 Regarding QTY-designed OPN2, the system was constructed directly using GROMACS.
-The protein was centered in a rectangular box with dimensions equivalent to those of native OPN2.
-The equilibration involved a sequence of simulations: a 250-ps NVT equilibration, followed by 125-ps and 1500-ps NPT equilibrations, totaling an equilibration duration that matches that of the natural OPN2.
+The protein was centered in a rectangular box with dimensions equal to those of native OPN2.
+The equilibration involved a sequence of simulations: one 250-ps NVT equilibration, followed by one 125-ps and one 1500-ps NPT equilibrations, totaling an equilibration duration that matches that of the natural OPN2.
 All other configurations and parameters are identical to those of the original OPN2.
@@
 	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
-	\caption{Protein sequence alignments}
+	\caption{Protein sequence alignments --- THIS FIGURE NEEDS REVISION!!!!!}
 	\label{fig:sequences}

### 2025-05-07 Paper/Source/manuscript.tex
Write results and discussion

@@
-\documentclass[fleqn,10pt]{manuscript}
+\documentclass[fleqn, 10pt, lineno]{manuscript}
 %%\usepackage{setspace}
@@
 We will use the term ``opsin'' interchangeably with ``retinylidene protein'', despite the fact that ``opsin'' sometimes refers specifically to the chromophore-free apoprotein.
-Retinylidene proteins are divided into two groups, animal opsins and microbial opsins, which are evolutionarily distinct but share common characteristics such as having 7 transmembrane (TM) domains and a retinal binding lysine residue \citep{Yee_2013, Spudich_2000}.
+Retinylidene proteins are divided into two groups, animal opsins and microbial opsins, which are evolutionarily distinct but share common characteristics such as having 7 transmembrane (TM) domains and a retinal-binding lysine residue \citep{Yee_2013, Spudich_2000}.
 In this study, we will consider 9 animal opsins and 3 microbial opsins.
@@
 \textbf{Animal opsins} are a type of class A GPCR (G-protein coupled receptor), which are characterized by 7 transmembrane domains, the NPxxY motif, and activation of G-proteins through the outward movement of TM6.
-\citep{Sakmar_2002, Nordstrom_2011, Zhou_2019}.
-Almost all animal opsins include a lysine residue that forms a Schiff base link with the retinal \citep{Bownds_1967, Guhmann_2022}.
+\citep{Zhou_2019}.
+Almost all animal opsins include a lysine residue that forms a Schiff base link with the retinal \citep{Guhmann_2022}.
 When retinal absorbs a photon, it isomerizes, usually changing from 11-cis to all-trans.
-The subsequent conformational changes of the protein are well studied using bovine rhodopsin, which changes from dark state to BATHO state, then LUMI, META I, and META II \citep{Okada_2001, Smith_2010}.
+The subsequent conformational changes of the protein are well studied using bovine rhodopsin, which changes from dark state to BATHO state, then LUMI, META I, and META II \citep{Okada_2001}.
 Proton transfer plays a major role in this process \citep{Mahalingam_2008}.
@@
 
-In this study, we selected 9 opsins expressed in the human nervous system: OPN1MW (\href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (\href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04001}), OPN1SW (\href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (\href{https://www.uniprot.org/uniprotkb/P08100/entry}{P04001}), OPN3 (\href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (\href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (\href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (\href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (\href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}).
-They belong to several evolutionarily distinct families of animal opsins \citep{Terakita_2005, Shichida_2009}.
+In this study, we selected 9 opsins expressed in the human nervous system: OPN1MW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04001}), OPN1SW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P08100/entry}{P04001}), OPN3 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}).
+They belong to several evolutionarily distinct families of animal opsins \citep{Terakita_2005}.
 
@@
 \textbf{OPN2} (Opsin 2), also known as rhodopsin, is expressed in retinal rod photoreceptors and is responsible for vision at low light intensity \citep{Hubbard_1958}.
-Certain variants lead to autosomal recessive or autosomal dominant retinitis pigmentosa \citep{Fanelli_2021}.
-Other variants also lead to congenital stationary night blindness \citep{Fanelli_2021}.
-OPN2 is a representative animal opsin, one of the earliest studied \citep{Hubbard_1958}.
+Certain variants lead to autosomal recessive or autosomal dominant retinitis pigmentosa and congenital stationary night blindness \citep{Fanelli_2021}.
+OPN2 is a representative animal opsin, one of the earliest studied.
 In fact, bovine OPN2 is the first opsin to be sequenced \citep{Nathans_1984} as well as the first GPCR whose crystal structure was resolved experimentally \citep{Palczeski_2000}.
-Many studies on the functional mechanisms of animal opsins also focus on OPN2 \citep{Park_2008, Scheerer_2008, Kimata_2016}.
-Consequently, we also choose OPN2 to conduct a functional analysis in this study, in order to further explore the effectiveness of the QTY design of retinylidene proteins.
+Many studies on the functional mechanisms of animal opsins also focus on OPN2.
+Consequently, we also chose OPN2 to conduct a functional analysis in this study, in order to further explore the effectiveness of the QTY design of retinylidene proteins.
 
@@
 It is expressed in the brain \citep{Blackshaw_1999}.
-It is also expressed in melanocytes and keratinocytes in the skin and regulates functions such as melanogenesis, cell differentiation, and glucose uptake \citep{Koyanagi_2013, Olinski_2020}.
+It is also expressed in melanocytes and keratinocytes in the skin and regulates functions such as melanogenesis, cell differentiation, and glucose uptake.
+It is also expressed in the liver, pancreas, kidney, lung, heart, and skeletal muscles.
+When it is expressed in neurons, neurotransmitter release is inhibit by light, which renders OPN3 a useful optogenetic tool \citep{Copits_2021}.
 
 \textbf{OPN4} (Opsin 4), also known as melanopsin, is expressed in ipRGC (intrinsically photosensitive Retinal Ganglion Cells) in the ganglion cell layer in the retina \citep{Provencio_1998}.
-It is responsible for pupillary reflex, photoentrainment, optokinetic visual tracking response, and other non-image-forming responses to light \citep{Berson_2002, Gooley_2003}.
+It is essential for non-image-forming responses to light, including for pupillary reflex, optokinetic visual tracking response, and photoentrainment and regulation of circadian rhythm.
+Certain variants of OPN4 lead to seasonal affective disorder and other circadian rhythm disorders.
+\citep{Berson_2002}.
+Image formation via OPN4-containing ipRGCs is also a potential pathway of treatment for various eye diseases such as retinitis pigmentosa and diabetic retinopathy.
 
-\textbf{OPN5} (Opsin 5), also known as neuropsin, is activated by blue and ultraviolet A light \citep{Tarttelin_2003, Yamashita_2010}.
-It is expressed in the retina and contributes to the regulation of light-dependent vascular development \citep{Nguyen_2019} and photoentrainment in the cornea and retina \citep{Buhr_2015}.
+\textbf{OPN5} (Opsin 5), also known as neuropsin, is activated by blue and ultraviolet A light \citep{Tarttelin_2003}.
+It is expressed in the retina and contributes to the regulation of light-dependent vascular development and photoentrainment in the cornea and retina \citep{Buhr_2015}.
+Certain variants of OPN5 may lead to cycloplegia, paralysis of the ciliary muscle in the eye.
 
 \textbf{RGR} (RPE-retinal GPCR) is expressed in RPE (Retinal Pigmented Epithelium) and M\"uller cells in the retina \citep{Shen_1994}.
-Unlike the aforementioned human opsins, RGR preferentially binds all-trans-retinal and may catalyze its isomerization into 11-cis-retinal via a retinochrome-like mechanism \citep{Radu_2008}.
-It plays a role in the light-dependent synthesis of visual chromophore \citep{Radu_2008}.
+Unlike the aforementioned human opsins, RGR preferentially binds all-trans-retinal and may catalyze its isomerization into 11-cis-retinal via a retinochrome-like mechanism.
+It is expressed only in tissue surrounding photoreceptors and plays a role in the light-dependent synthesis of visual chromophore \citep{Radu_2008}.
 
@@
 It is another protein that preferentially binds to all-trans-retinal \citep{Cook_2017}.
+Although not much information is known about RRH, it can reasonably be inferred that it photoisomerizes all-trans-retinal to 11-cis state, and may play a role in the upkeeping of photoreceptor functions.
 
@@
 They are also 7TM, though this is due to convergent evolution rather than homology \citep{Yee_2013}.
-The isomerization of retinal is usually from all-trans to 13-cis, different from that in animal opsins \citep{Findlay_1986, Spudich_2000}.
-In addition, bacterial opsins often form oligomers to carry out their functions \citep{Taguchi_2023, Gmelin_2007, Shan_2024}.
+The isomerization of retinal is usually from all-trans to 13-cis, different from that in animal opsins \citep{Findlay_1986}.
+In addition, bacterial opsins often form oligomers to carry out their functions \citep{Gmelin_2007}.
 
-In this study, we selected 3 bacterial opsins: BACR (\href{https://www.uniprot.org/uniprotkb/P02945/entry}{P02945}), BACH (\href{https://www.uniprot.org/uniprotkb/B0R2U4/entry}{B0R2U4}), ChR2 (\href{https://www.uniprot.org/uniprotkb/Q8RUT8/entry}{Q8RUT8}).
+In this study, we selected 3 bacterial opsins: BACR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P02945/entry}{P02945}), BACH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/B0R2U4/entry}{B0R2U4}), ChR2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q8RUT8/entry}{Q8RUT8}).
 
-\textbf{BACR} (Bacteriorhodopsin) is a light-driven proton pump \citep{Oesterhelt_1971}.
+\textbf{BACR} (Bacteriorhodopsin) is a light-driven proton pump and is one of the first bacterial opsins discovered \citep{Oesterhelt_1971}.
 \textbf{BACH} (Halorhodopsin) is a light-driven chloride pump activated by yellow light \citep{Schobert_1982}.
@@
 
-We have asked if retinylidene proteins could be redesigned to be more soluble.
+We have asked whether retinylidene proteins could be redesigned to be more soluble.
 Retinylidene proteins are all integral membrane proteins with seven transmembrane alpha helices embedded in a lipid bilayer.
@@
 
-Bacteriorhodopsin has been the subject of several protein-solubilizing studies, though with limited success \citep{Sirokman_1993, Gibas_1997, Mitra_2002}.
+Bacteriorhodopsin has been the subject of several protein-solubilizing studies, though with limited success \citep{Qing_2022}.
 Recently, researchers leveraged a neural network, SolubleMPNN, which was built upon ProteinMPNN, to engineer soluble variants of bacteriorhodopsin while maintaining its ligand-binding ability and light-sensing function \citep{Nikolaev_2024}.
@@
 Instead of taking a computational approach, we applied the QTY (Glutamine, Threonine, Tyrosine) code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins.
-There are structural similarities between hydrophobic and polar amino acids: leucine (L) vs.
-glutamine (Q); isoleucine (I) / valine (V) vs.
-threonine (T); and phenylalanine (F) vs.
-tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}.
+There are structural similarities between hydrophobic and polar amino acids: leucine (L) \textit{vs} glutamine (Q); isoleucine (I) / valine (V) \textit{vs} threonine (T); and phenylalanine (F) \textit{vs} tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}.
 This justifies the replacement of hydrophobic amino acids with polar ones.
@@
 We have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.
+Besides GPCRs, we have also used the QTY code to design water-soluble glucose transporters \citep{Smorodina_2022}, ABC transporters \citep{Pan_2024}, monoamine neurotransmitter transporters \citep{Karagol_Karagol_Alper_2024}, glutamate transporters \citep{Karagol_Karagol_Smorodina_2024, Karagol_2024}, mitochondrial megacomplex \citep{Chen_2025}, antibodies \citep{Li_Wang_2024}, potassium channels \citep{Smorodina_2024}, receptor kinases \citep{Li_Tang_2024}, transmembrane enzymes \citep{Chen_Pan_2025}, as well as bacterial enzymes with beta barrel structures \citep{Sajeev-Sheeja_2023, Sajeev-Sheeja_2024}.
+The QTY-designed water-soluble CXCR4 chemokine receptor has been successfully in biomimetic sensors \citep{Qing_2023}.
+We have also applied the rQTY (reverse QTY) code to design nanoparticles \citep{Meng_2023}.
 
@@
 
-\section*{Results and Discussion}
-
-\subsection*{The rationale of the QTY code}
-
-Discuss the QTY code.
-
-\subsection*{Retinylidene proteins sequence alignments and other characteristics}
-
-Describe and discuss Table~\ref{tb:characteristics} (native and QTY protein characteristics) // NOTE: the binding of retinal is posterior to folding, so it is safe to say that we predicted chromophore-free form (i.e.
-folding does not rely on retinal).
-
-\subsection*{Superpositions of AlphaFold3-predicted native human opsins, their water-soluble QTY variants, and experimentally determined structures}
-
-Describe and discuss Fig.~\ref{fig:humansup} (AF3 native - AF3 QTY - experimental superpositions of human opsins).
-
-\subsection*{Pairwise superpositions among AlphaFold3-predicted native human opsins and among their water-soluble QTY variants}
-
-Describe and discuss Fig.~\ref{fig:pairwise} (pairwise superpositions of human opsins) // NOTE: the QTY pairwise superpositions roughly maintains the trends in the native superpositions.
-
-\subsection*{Superpositions of AlphaFold3-predicted native microbial opsins, their water-soluble QTY variants, and experimentally determined structures}
-
-Describe and discuss Fig.~\ref{fig:microbialsup} (AF3 native - AF3 QTY - experimental superimpositions of microbial opsins) // NOTE: comment specifically on the formation of dimers and trimers.
-
-\subsection*{Analysis of the hydrophobic surface of native retinylidene proteins and their water-soluble QTY variants}
-
-Describe and discuss Fig.~\ref{fig:hydrophobicity} (surface hydrophobicity).
-
-\subsection*{AlphaFold3 predictions}
-
-Discuss the role of AlphaFold3 predictions.
-
-\subsection*{Simulation of 11-cis to all-trans isomerization of retinal in native OPN2 and its QTY variant}
-
-Describe, explain, discuss MD simulation results.
-// NOTE: there were no changes to the NPxxY motif or retinal-binding Lys; "The ionic environment of the RSB, defined by the residues of the binding pocket, dictates the spectral and kinetic characteristics of each individual protein." \citep{Fenno_2011}, so QTY variant may have different absorption peak.
-
-MD Results
-
-* different states - binding pocket residues + ligand orientation
-
-* bond length, angle, dihedral, non-bonded interaction lengths graph
-
-* by-helix rmsd
-
-* by-residue IE
-
-* hbond
-
-* overall rmsd, gyrate, rmsf, IE
-
-\subsection*{Future scopes and potential applications}
-
-Future scopes and potential applications.
-
-\subsection*{Conclusion}
-
-Conclusion
-
 \section*{Methods}
@@
 The native protein sequences for OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, RRH, BACR, BACH, and ChR2 were obtained from UniProt (\url{https://www.uniprot.org}).
-The sequence for ChR2 was truncated according to the experimental structure in RCSB PDB (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
+The sequence for ChR2 was truncated according to the experimentally determined structure in RCSB PDB (PDB ID: \href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
 The QTY designs were performed through the Protein Solubilizing Server (\url{https://pss.sjtu.edu.cn/}) \citep{Tao_2022}.
@@
 
-PDB files for native protein structures determined experimentally by X-ray diffraction or electron microscopy were taken from RCSB PDB: OPN2 (\href{https://www.rcsb.org/structure/5W0P}{5W0P}), BACR (\href{https://www.rcsb.org/structure/7XJC}{7XJC}), BACH (\href{https://www.rcsb.org/structure/2JAF}{2JAF}), ChR2 (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
+PDB files for native protein structures determined experimentally by X-ray diffraction or electron microscopy were taken from RCSB PDB: OPN2 (PDB ID: \href{https://www.rcsb.org/structure/5W0P}{5W0P}), BACR (PDB ID: \href{https://www.rcsb.org/structure/7XJC}{7XJC}), BACH (PDB ID: \href{https://www.rcsb.org/structure/2JAF}{2JAF}), ChR2 (PDB ID: \href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
 The AlphaFold3-predicted native and QTY variants were taken directly from the most probable predicted structure.
@@
 
-We used PyMOL (\url{https://pymol.org}) to superpose the native predicted protein structures, their QTY variants, and the experimental structures for the proteins where these existed.
+We used PyMOL (\url{https://pymol.org}) to superpose the native predicted protein structures, their QTY variants, and the experimentally determined structures for the proteins where these existed.
 We then used UCSF ChimeraX (\url{https://www.cgl.ucsf.edu/chimerax/}) to render each protein model with hydrophobicity patches.
@@
 [ANALYSIS METHODS OF MD SIMULATION RESULTS, TO BE ADDED.]
+
+\section*{Results and Discussion}
+
+\subsection*{The rationale of the QTY code}
+
+The transmembrane segments of membrane proteins are hydrophobic in nature.
+This leads to a challenge to study their structure and function.
+Traditionally, detergent must be used to purify them.
+We consider a different approach, i.e., via systematic soluble protein design.
+There exists structural similarities, as can be observed on high-resolution electron density maps, between certain hydrophobic and hydrophilic amino acids: leucine (L) and glutamine (Q), isoleucine (I) or valine (V) and threonine (T), and phenylalanine (F) with tyrosine (Y).
+This fact enables systematic replacement of L with Q, I/V with T, and F with Y in all transmembrane segments of the membrane protein, which we named the QTY code.
+QTY analogs are less hydrophobic than native membrane proteins.
+Although their amino acid sequences have been significantly changed, they still exhibit relatively preserved structure, isoelectric points (pI), and molecular weights (MW) compared to the native membrane proteins (Table~\ref{tb:characteristics}).
+
+\subsection*{Protein sequence alignments and other characteristics of retinylidene proteins}
+
+The protein sequences of 9 human opsins and 3 microbial opsins are aligned with their QTY analogs (Figure~\ref{fig:sequences}).
+The QTY substitution resulted in an overall variation of the sequence of 15.48\% to 30.04\% and a variation of transmembrane domain of 35.53\% to 50.24\%.
+Despite changes to the amino acid composition and sequence, the pI only experiences a slight change, between 0.00 and 0.16.
+This is because the amino acids Q, T, and Y have neutral charges and do not introduce additional charges to the system.
+The MW increases slightly by a value between 0.04kDa and 0.60kDa.
+This is because the hydrophilic amino acids usually have nitrogen or oxygen atoms in place of carbon atoms in hydrophobic acids and thus may have higher mass: L (131.17Da) \textit{vs} Q (146.14Da); I (131.17Da) and V (117.15Da) \textit{vs} T (119.12Da); F (165.19Da) \textit{vs} Y (181.19Da).
+
+\subsection*{Superpositions of AlphaFold3-predicted native human opsins, their water-soluble QTY variants, and experimentally determined structures}
+
+Although the chromophore, retinal, is bound to retinylidene proteins in an internal pocket, it is only incorporated into the protein after protein folding is complete.
+In other words, protein folding does not depend on the chromophore.
+Thus, it is justified to predict the ligand-free forms of the proteins.
+We used AlphaFold3 to predict the structure of the 9 native human opsins and their water-soluble QTY analogs.
+The structures superpose very well (Figure~\ref{fig:humansup} \textbf{a)} to \textbf{i)}).
+For OPN2, which has an available X-ray diffraction structure, we also superposed the experimentally determined structure with the AlphaFold3-predicted structures.
+Overall, the root mean square distances (RMSD) are small, from 0.307\AA to 0.611\AA, with only one exception of OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$ (RMSD = 0.999).
+This shows that the water-soluble QTY analogs are quite similar to native proteins in terms of structure.
+
+All 9 of these human opsins belong to the same large family, i.e.
+animal opsins.
+However, they belong to different subfamilies and have structural differences from each other.
+In order to investigate the extent to which the water-soluble QTY analogs preserve these differences, we also conducted pairwise superpositions within all 9 native human opsins and within all 9 QTY analogs of human opsins (Figure~\ref{fig:humansup} \textbf{j)} and \textbf{k)}).
+As observed in the tables, there is a large degree of similarity between the RMSD between a pair of native proteins and that between the corresponding pair of QTY analogs.
+Therefore, we conclude that the structural differences are relatively well-preserved before and after the QTY substitution.
+However, whether the functional differences are preserved remains a problem to study.
+
+\subsection*{Superpositions of AlphaFold3-predicted native microbial opsins, their water-soluble QTY variants, and experimentally determined structures}
+
+We used AlphaFold3 to predict the structure of monomers of the 3 native microbial opsins, their water-soluble QTY analogs.
+Since microbial opsins often have to form oligomers to be functional, we also predicted the structure of native and QTY variants of BACR trimers, BACH trimers, and ChR2 dimers.
+These predicted structures are also superposed with experimentally determined structures (X-ray diffraction or electron microscopy).
+The structures superpose very well (Figure~\ref{fig:microbialsup}).
+Overall, the root mean square differences (RMSD) are small, with the highest value being 0.685\AA.
+This shows that the water-soluble QTY analogs are likely capable of forming oligomers with structures similar to those of native proteins.
+
+\subsection*{Analysis of the hydrophobic surface of native retinylidene proteins and their water-soluble QTY variants}
+
+Describe and discuss Figure~\ref{fig:hydrophobicity} (surface hydrophobicity).
+
+As transmembrane proteins, retinylidene proteins require detergents to be separated from the lipid bilayer.
+The detergents act as an interface between the hydrophobic transmembrane domain of the protein and the surrounding water, thus solubilizing the protein.
+If these proteins are exposed in water without detergents, their hydrophobicity will induce them to aggregate and precipitate, with their structures and functions disrupted.
+
+The hydrophobic portions of the protein surface are represented in yellow (Figure 5).
+In the native proteins, there are large hydrophobic patches in the transmembrane domains, which are embedded within the lipid bilayer.
+The nonpolar and hydrophobic amino acids including leucine (L), isoleucine (I), valine (V), phenylalanine (F), alanine (A), methionine (M), and tryptophan (W) interact with the hydrophobic hydrocarbon chains and expel water.
+
+We investigate the surface hydrophobicity of water-soluble QTY-analogs in comparison with the native proteins.
+After applying the QTY code to respectively replace the hydrophobic amino acids L, I/V, and F with hydrophilic amino acids glutamine (Q), threonine (T), and tyrosine (Y), the hydrophobic surface areas are significantly reduced.
+More importantly, since the electron density maps of the corresponding amino acids are similar, the alpha helices in QTY analogs have a similar surface contour to the helices in the native proteins.
+The QTY analogs have successfully retained its structural integrity and stability.
+
+\subsection*{AlphaFold3 predictions}
+
+DeepMind released AlphaFold3 in May 2024, marking a significant leap in accuracy for modeling across biomolecular space.
+This latest iteration outperforms state-of-the-art docking tools and its predecessor, AlphaFold-Multimer v.2.3, in protein structure and protein-protein interaction predictions \citep{Abramson_2024}.
+AlphaFold3 reduces the reliance on multiple sequence alignment by integrating a diffusion-based model, enabling it to predict a broader spectrum of biomolecules, including ligands, ions, nucleic acids, modified residues, and large protein megacomplexes.
+On October 9, 2024, DeepMind’s founders, Demis Hassabis and John Jumper, received the Nobel Prize in Chemistry for revolutionizing protein structure prediction through leveraging machine learning.
+
+AlphaFold3 is easily accessible online (\url{https://alphafoldserver.com}), allowing users to make 30 predictions a day.
+The structures of the QTY analogs were predicted using the AlphaFold3 server, which was run free of charge and the results were produced within a few minutes.
+
+DeepMind also collaborates with the EBI to make over 214 million predicted protein structures available through the AlphaFold Protein Structure Database (\url{https://alphafold.ebi.ac.uk}).
+This number is continuously expanding, with the quality of predictions further improving with the advent of AlphaFold 3.
+
+However, AlphaFold3 still has limitations that have been encountered in this study.
+Although AlphaFold3 allows the structural prediction of complexes that include small-molecule ligands, it only supports a small range of ligands, which does not include retinal.
+We were therefore unable to predict the structure of chromophore-bound states of retinylidene proteins.
+Consequently, we chose another approach, namely molecular dynamics simulation, in order to investigate the behavior of QTY opsin analogs when they are bound to the chromophore.
+
+\subsection*{Simulation of 11-cis to all-trans isomerization of retinal in native OPN2 and its QTY variant}
+
+Describe, explain, discuss MD simulation results.
+// NOTE: there were no changes to the NPxxY motif or retinal-binding Lys; "The ionic environment of the RSB, defined by the residues of the binding pocket, dictates the spectral and kinetic characteristics of each individual protein." \citep{Fenno_2011}, so QTY variant may have different absorption peak.
+
+MD Results
+
+* different states - binding pocket residues + ligand orientation
+
+* bond length, angle, dihedral, non-bonded interaction lengths graph
+
+* by-helix rmsd
+
+* by-residue IE
+
+* hbond
+
+* overall rmsd, gyrate, rmsf, IE
+
+\subsection*{Future scopes and potential applications}
+
+Future scopes and potential applications.
+
+\subsection*{Conclusion}
+
+Conclusion
 
@@
 	\centering
-	\caption{Protein characteristics}
+	\caption{\textbf{Protein characteristics of 12 retinylidene proteins and their QTY analogs.
+} Blue: human opsins; purple: microbial opsins.
+RMSD: root mean square distance; pI: isoelectric focusing; MW: molecular weight; TM: transmembrane.
+}
 	\label{tb:characteristics}
@@
 	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
-	\caption{Protein sequence alignments --- THIS FIGURE NEEDS REVISION!!!!!}
+	\caption{\textbf{The protein sequence alignments of 12 retinylidene proteins and their QTY analogs.
+} Blue: human opsins; purple: microbial opsins.
+The symbols $|$ and $*$ indicate that amino acids are identical and different respectively.
+Amino acids L, V, I and F in TM (transmembrane) alpha helices are replaced with Q, T, Y and Y respectively.
+The alpha helices (blue) are shown above the protein sequences.
+The characteristics of the proteins are shown above the sequences.
+    The alignments are: 
+    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
+    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
+    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
+    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$, 
+    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$, 
+    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$, 
+    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$, 
+    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$, 
+    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$, 
+    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$, 
+    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$, 
+    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$. }
 	\label{fig:sequences}
@@
 	\centering
-	\includegraphics[width=\linewidth]{Figures/superposition-human.jpg}
-	\caption{Superposition of human retinylidene proteins}
+	\includegraphics[width=\linewidth]{Figures/superposition-human-pairwise.jpg}
+	\caption{Superposition of AlphaFold3-predicted native human retinylidene proteins, their QTY analogs, and experimentally determined structures. 
+    For \textbf{a)} to \textbf{i)}, green: AlphaFold3-predicted native structure; cyan: AlphaFold3-predicted QTY analog structure; magenta: experimentally determined structure. The superpositions are 
+    \textbf{a)} OPN1MW$^{\textrm{AF3}}$ \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
+    \textbf{b)} OPN1LW$^{\textrm{AF3}}$ \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
+    \textbf{c)} OPN1SW$^{\textrm{AF3}}$ \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
+    \textbf{d)} OPN2$^{\textrm{AF3}}$ \textit{vs} OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$, 
+    \textbf{e)} OPN3$^{\textrm{AF3}}$ \textit{vs} OPN3$^{\textrm{QTY}}$, 
+    \textbf{f)} OPN4$^{\textrm{AF3}}$ \textit{vs} OPN4$^{\textrm{QTY}}$, 
+    \textbf{g)} OPN5$^{\textrm{AF3}}$ \textit{vs} OPN5$^{\textrm{QTY}}$, 
+    \textbf{h)} RGR$^{\textrm{AF3}}$ \textit{vs} RGR$^{\textrm{QTY}}$, 
+    \textbf{i)} RRH$^{\textrm{AF3}}$ \textit{vs} RRH$^{\textrm{QTY}}$, 
+    \textbf{j)} BACR$^{\textrm{AF3}}$ \textit{vs} BACR$^{\textrm{QTY}}$, 
+    \textbf{k)} BACH$^{\textrm{AF3}}$ \textit{vs} BACH$^{\textrm{QTY}}$, 
+    \textbf{l)} ChR2$^{\textrm{AF3}}$ \textit{vs} ChR2$^{\textrm{QTY}}$. 
+    For \textbf{j)} and \textbf{k)}, green: OPN1MW; red: OPN1LW; blue: OPN1SW; purple: OPN2; cyan: OPN3; gray: OPN4; olive: OPN5; orange: RGR; pink: RRH. The superpositions are
+    \textbf{j)} OPN1MW$^{\textrm{AF3}}$ \textit{vs} OPN1LW$^{\textrm{AF3}}$ \textit{vs} OPN1SW$^{\textrm{AF3}}$ \textit{vs} OPN2$^{\textrm{AF3}}$ \textit{vs} OPN3$^{\textrm{AF3}}$ \textit{vs} OPN4$^{\textrm{AF3}}$ \textit{vs} OPN5$^{\textrm{AF3}}$ \textit{vs} RGR$^{\textrm{AF3}}$ \textit{vs} RRH$^{\textrm{AF3}}$,
+    \textbf{k)} OPN1MW$^{\textrm{QTY}}$ \textit{vs} OPN1LW$^{\textrm{QTY}}$ \textit{vs} OPN1SW$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{QTY}}$ \textit{vs} OPN3$^{\textrm{QTY}}$ \textit{vs} OPN4$^{\textrm{QTY}}$ \textit{vs} OPN5$^{\textrm{QTY}}$ \textit{vs} RGR$^{\textrm{QTY}}$ \textit{vs} RRH$^{\textrm{QTY}}$.
+    }
 	\label{fig:humansup}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\linewidth]{Figures/pairwise.jpg}
-	\caption{Pairwise comparison of human opsins. Green: OPN1MW; red: OPN1LW; blue: OPN1SW; purple: OPN2; cyan: OPN3; gray: OPN4; olive: OPN5; orange: RGR; pink: RRH. }
-	\label{fig:pairwise}
 \end{figure}

### 2025-05-08 MD/Delete_atom_gro_large.py
prepare for analysis

@@ -1,52 +1,0 @@
-import re
-
-def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms):
-    with open(file_path, "r") as file:
-        lines = file.readlines()
-    updated_lines = []
-    num_deleted = 0
-
-    in_protein = 0
-    for line in lines:
-        line_splitted = line.split()
-        if len(line_splitted) == 5:
-            line_splitted = line_splitted[:1] + [line_splitted[1][:-5], line_splitted[1][-5:]] + line_splitted[2:]
-        elif len(line_splitted) != 6:
-            updated_lines.append(line)
-            continue
-        atom_index = int(line_splitted[2])
-        if atom_index in target_delete_atoms and num_deleted < len(target_delete_atoms):
-            num_deleted += 1
-            continue
-        new_line_splitted = line_splitted[:2] + [str(atom_index - num_deleted)] + line_splitted[3:]
-        formatted_line = ""
-        
-        # below are specifically for the membrane system sice CHL1, POPC, POPE, POPS are all 4-letter residues
-        if "RET" in line_splitted[0]:
-            in_protein = 1
-        elif in_protein == 1:
-            in_protein = -1
-            
-        if in_protein == -1:
-            formatted_line = "{:>9}{:>6}{:>5}{:>8}{:>8}{:>8}\n".format(*new_line_splitted)
-        else:
-            formatted_line = "{:>8}{:>7}{:>5}{:>8}{:>8}{:>8}\n".format(*new_line_splitted)
-        
-        updated_lines.append(formatted_line)
-
-    with open(write_path, "w") as file:
-        file.writelines(updated_lines)
-
-file_path = "step5_input_formatted.gro"
-write_path = "step5_input.gro"
-target_delete_atoms = [4686, 4687, 5497, 5498]
-delete_atom_and_update_indices(file_path, write_path, target_delete_atoms)
-
-# Remember to manually edit the total atom count!
-
-# when there are over 10000 atoms, edit things like:
-# 19908TIP3  OH21   -4   9.829   5.121   0.182
-# 19908TIP3   H11   -3   9.893   5.189   0.208
-# 19908TIP3   H21   -2   9.879   5.079   0.109
-# 19909TIP3  OH21   -1   9.664   4.387   0.095
-# 19909TIP3   H11    0   9.662   4.483   0.111

### 2025-05-08 Paper/Source/manuscript.tex

@@
 	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
+        \vspace{-0.5cm}
 	\caption{\textbf{The protein sequence alignments of 12 retinylidene proteins and their QTY analogs.
@@
 	\includegraphics[width=\linewidth]{Figures/superposition-human-pairwise.jpg}
-	\caption{Superposition of AlphaFold3-predicted native human retinylidene proteins, their QTY analogs, and experimentally determined structures. 
+	\caption{\textbf{Superposition of AlphaFold3-predicted native human retinylidene proteins, their QTY analogs, and experimentally determined structures.
+} For clarity, unstructured N- and C- terminal ends are deleted.
     For \textbf{a)} to \textbf{i)}, green: AlphaFold3-predicted native structure; cyan: AlphaFold3-predicted QTY analog structure; magenta: experimentally determined structure. The superpositions are 
@@
     \textbf{h)} RGR$^{\textrm{AF3}}$ \textit{vs} RGR$^{\textrm{QTY}}$, 
-    \textbf{i)} RRH$^{\textrm{AF3}}$ \textit{vs} RRH$^{\textrm{QTY}}$, 
-    \textbf{j)} BACR$^{\textrm{AF3}}$ \textit{vs} BACR$^{\textrm{QTY}}$, 
-    \textbf{k)} BACH$^{\textrm{AF3}}$ \textit{vs} BACH$^{\textrm{QTY}}$, 
-    \textbf{l)} ChR2$^{\textrm{AF3}}$ \textit{vs} ChR2$^{\textrm{QTY}}$. 
+    \textbf{i)} RRH$^{\textrm{AF3}}$ \textit{vs} RRH$^{\textrm{QTY}}$. 
     For \textbf{j)} and \textbf{k)}, green: OPN1MW; red: OPN1LW; blue: OPN1SW; purple: OPN2; cyan: OPN3; gray: OPN4; olive: OPN5; orange: RGR; pink: RRH. The superpositions are
@@
 	\includegraphics[width=\linewidth]{Figures/superposition-microbial.jpg}
-	\caption{Superposition of microbial retinylidene proteins}
+	\caption{\textbf{Superposition of AlphaFold3-predicted native microbial retinylidene proteins, their QTY analogs, and experimentally determined structures.
+} For clarity, unstructured N- and C- terminal ends are deleted.
+    Green: AlphaFold3-predicted native structure; cyan: AlphaFold3-predicted QTY analog structure; magenta: experimentally determined structure. The superpositions are 
+    \textbf{a)} BACR$^{\textrm{AF3}}$ \textit{vs} BACR$^{\textrm{QTY}}$ \textit{vs} BACR$^{\textrm{EXP}}$ monomer, 
+    \textbf{b)} BACR$^{\textrm{AF3}}$ \textit{vs} BACR$^{\textrm{QTY}}$ \textit{vs} BACR$^{\textrm{EXP}}$ trimer, 
+    \textbf{c)} BACH$^{\textrm{AF3}}$ \textit{vs} BACH$^{\textrm{QTY}}$ \textit{vs} BACH$^{\textrm{EXP}}$ monomer, 
+    \textbf{d)} BACH$^{\textrm{AF3}}$ \textit{vs} BACH$^{\textrm{QTY}}$ \textit{vs} BACH$^{\textrm{EXP}}$ trimer, 
+    \textbf{e)} ChR2$^{\textrm{AF3}}$ \textit{vs} ChR2$^{\textrm{QTY}}$ \textit{vs} ChR2$^{\textrm{EXP}}$ monomer, 
+    \textbf{f)} ChR2$^{\textrm{AF3}}$ \textit{vs} ChR2$^{\textrm{QTY}}$ \textit{vs} ChR2$^{\textrm{EXP}}$ dimer. }
 	\label{fig:microbialsup}
@@
 	\includegraphics[width=\linewidth]{Figures/hydrophobicity.jpg}
-	\caption{Surface hydrophobicity}
+	\caption{\textbf{Hydrophobic surface of 12 retinylidene proteins and their water-soluble QTY analogs.
+} The native proteins have many hydrophobic (yellow) patches due to the presence of hydrophobic amino acids, including L, I, V, and F.
+After QTY substitution, hydrophilic Q, T, and Y have respectively replaced hydrophobic L, I/V, and F, and the hydrophobic patches in the surface of transmembrane helices have become more hydrophilic (cyan).
+For clarity, unstructured N- and C- terminal ends are deleted.
+    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
+    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
+    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
+    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$, 
+    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$, 
+    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$, 
+    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$, 
+    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$, 
+    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$, 
+    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$ monomer, 
+    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$ monomer, 
+    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$ monomer, 
+    \textbf{m)} BACR \textit{vs} BACR$^{\textrm{QTY}}$ trimer, 
+    \textbf{n)} BACH \textit{vs} BACH$^{\textrm{QTY}}$ trimer, 
+    \textbf{o)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$ dimer. 
+    }
 	\label{fig:hydrophobicity}

### 2025-05-09 MD/Analysis/plot_hbonds.py
Add plotting for hbonds, numwater, and rmsd

@@ -1,0 +1,40 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+
+def load_xvg(filename, start = 0):
+    data = []
+    with open(filename, "r") as f:
+        for line in f:
+            if not line.startswith(("#", "@")):
+                split = line.split()
+                data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(len(split))])
+    return np.array(data)
+
+def plot_running_avg(x, y):
+    window_size = 500
+    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
+    x_avg = x[len(x) - len(running_avg) : ]
+    plt.plot(x_avg, running_avg, label="1-ns Running Avg", color="red")
+
+matplotlib.rcParams['font.family'] = 'Calibri'
+targetname = "hbonds"
+for protein in ["qty", "wt"]:
+    cis_data = load_xvg(f"{protein}_cis_{targetname}.xvg", -10)
+    trans_data = load_xvg(f"{protein}_trans_{targetname}.xvg")
+    data = np.concatenate((cis_data, trans_data), axis=0)
+    x = data[:, 0]
+    y = data[:, 1]
+    plt.figure(figsize=(8, 5))
+    plt.plot(x, y, label="", color="black", linewidth=0.5)
+    plot_running_avg(x, y)
+    plt.xlabel("Time (ns)")
+    plt.ylabel("Number of hydrogen bonds within binding pocket")
+    plt.title("")
+    plt.xlim(-10, 120)
+    plt.xticks(np.arange(-10, 121, 10))
+    plt.axvline(x=0, color='b', linestyle='--')
+    #plt.legend()
+    plt.grid(False)
+    plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
+    plt.show()

### 2025-05-09 MD/Analysis/plot_ie.py

@@ -1,0 +1,66 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+
+def load_xvg(filename, start = 0):
+    data = []
+    with open(filename, "r") as f:
+        for line in f:
+            if not line.startswith(("#", "@")):
+                split = line.split()
+                data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(len(split))])
+    return np.array(data)
+
+def plot_running_avg(x, y, c="red", labelname="", window=1):
+    window_size = window * 500
+    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
+    x_avg = x[len(x) - len(running_avg) : ]
+    plt.plot(x_avg, running_avg, label=labelname, color=c)
+
+matplotlib.rcParams['font.family'] = 'Calibri'
+number = 17
+data = []
+targetname = "ie"
+subtargetids = ["prot", "pocket", "byres"]
+resnames = {
+    "qty": ["265W", "113E", "181E", "268Y", "207M", "186S", "191Y", "187C", "188G", "189I", "117A", "292A", "212Y", "295A", "208Y"], 
+    "wt" : ["265W", "113E", "181E", "268Y", "207M", "186S", "191Y", "187C", "188G", "189I", "117A", "292A", "212F", "295A", "208F"]
+}
+subtargetnames = [int(subtargetid) for subtargetid in subtargetids]
+cmap = plt.cm.get_cmap("tab20", 16)
+colors = [cmap(i) for i in range(16)]
+for protein in ["qty", "wt"]:
+    plt.figure(figsize=(8, 5))
+    plt.xlabel("Time (ns)")
+    plt.ylabel("RMSD (ns)")
+    plt.title("")
+    plt.xlim(-10, 120)
+    plt.xticks(np.arange(-10, 121, 10))
+    plt.axvline(x=0, color='b', linestyle='--')
+    plt.grid(False)
+    for i in range(len(subtargetnames)):
+        cis_data = load_xvg(f"{protein}_cis_{targetname}_{subtargetnames[i]}.xvg", -10)
+        trans_data = load_xvg(f"{protein}_trans_{targetname}_{subtargetnames[i]}.xvg")
+        data = np.concatenate((cis_data, trans_data), axis=0)
+        x = data[:, 0]
+        y = data[:, 1]
[…]

### 2025-05-09 MD/Analysis/plot_rmsd.py

@@ -1,0 +1,48 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+
+def load_xvg(filename, start = 0):
+    data = []
+    with open(filename, "r") as f:
+        for line in f:
+            if not line.startswith(("#", "@")):
+                split = line.split()
+                data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(len(split))])
+    return np.array(data)
+
+def plot_running_avg(x, y, c="red", labelname=""):
+    window_size = 500
+    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
+    x_avg = x[len(x) - len(running_avg) : ]
+    plt.plot(x_avg, running_avg, label=labelname, color=c)
+
+matplotlib.rcParams['font.family'] = 'Calibri'
+targetname = "rmsd"
+subtargetnames = ["solu", "tm6", "pocket", "ret"]
+colors = [
+    ["#000000", "#000000"],
+    ["#000077", "#0000FF"],
+    ["#007700", "#00FF00"],
+    ["#770000", "#FF0000"]
+]
+for protein in ["qty", "wt"]:
+    plt.figure(figsize=(8, 5))
+    plt.xlabel("Time (ns)")
+    plt.ylabel("RMSD (nm)")
+    plt.title("")
+    plt.xlim(-10, 120)
+    plt.xticks(np.arange(-10, 121, 10))
+    plt.axvline(x=0, color='b', linestyle='--')
+    plt.grid(False)
+    for i in range(len(subtargetnames)):
+        cis_data = load_xvg(f"{protein}_cis_{targetname}_{subtargetnames[i]}.xvg", -10)
+        trans_data = load_xvg(f"{protein}_trans_{targetname}_{subtargetnames[i]}.xvg")
+        data = np.concatenate((cis_data, trans_data), axis=0)
+        x = data[:, 0]
+        y = data[:, 1]
+        #plt.plot(x, y, label=subtargetnames[i], color=colors[i][0], linewidth=0.5)
+        plot_running_avg(x, y, c=colors[i][1], labelname=subtargetnames[i])
+    plt.legend()
+    plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
+    plt.show()

### 2025-05-09 MD/Analysis/plot_ie.py
Prepare programs for all graphs

@@ -2,65 +2,71 @@ import numpy as np
 import matplotlib
 import matplotlib.pyplot as plt
 
-def load_xvg(filename, start = 0):
-    data = []
+def load_xvg_ie(filename, byres = False):
+    data = [[] for _ in range(15)] if byres else [[]]
     with open(filename, "r") as f:
         for line in f:
-            if not line.startswith(("#", "@")):
+            if not line.startswith(("#", "@")) and len(line.split()) > 0:
                 split = line.split()
-                data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(len(split))])
+                if byres:
+                    for i in range(15):
+                        data[i].append(float(split[2 * i + 1]) + float(split[2 * i + 2]))
+                else:
+                    data[0].append(float(split[1]) + float(split[2]))
     return np.array(data)
 
-def plot_running_avg(x, y, c="red", labelname="", window=1):
-    window_size = window * 500
-    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
-    x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label=labelname, color=c)
-
 matplotlib.rcParams['font.family'] = 'Calibri'
-number = 17
 data = []
 targetname = "ie"
-subtargetids = ["prot", "pocket", "byres"]
-resnames = {
+reslabels = {
     "qty": ["265W", "113E", "181E", "268Y", "207M", "186S", "191Y", "187C", "188G", "189I", "117A", "292A", "212Y", "295A", "208Y"], 
     "wt" : ["265W", "113E", "181E", "268Y", "207M", "186S", "191Y", "187C", "188G", "189I", "117A", "292A", "212F", "295A", "208F"]
 }
-subtargetnames = [int(subtargetid) for subtargetid in subtargetids]
-cmap = plt.cm.get_cmap("tab20", 16)
-colors = [cmap(i) for i in range(16)]
+matplotlib.rcParams['font.family'] = 'Calibri'
+targetname = "ie"
+resids = [265, 113, 181, 268, 207, 186, 191, 187, 188, 189, 117, 292, 212, 295, 208]
+resnames = [int(resid) for resid in resids]
[…]

### 2025-05-09 MD/Analysis/plot_rmsf.py

@@ -1,0 +1,40 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+
+def load_xvg_rmsf(filename):
+    data = []
+    with open(filename, "r") as f:
+        for line in f:
+            if not line.startswith(("#", "@")) and len(line.split()) > 0 \
+                and int(line.split()[0]) < 323:
+                data.append([int(line.split()[i]) if i == 0 else float(line.split()[i]) for i in range(2)])
+    return np.array(data)
+
+matplotlib.rcParams["font.family"] = "Calibri"
+targetname = "rmsf"
+for protein in ["qty", "wt"]:
+    data_cis = load_xvg_rmsf(f"{protein}_cis_{targetname}.xvg")
+    data_trans = load_xvg_rmsf(f"{protein}_trans_{targetname}.xvg")
+    fig, ax = plt.subplots(figsize=(8, 5))
+    bar_width = 1.0
+    x = data_cis[:, 0]
+    y_cis=data_cis[:, 1]
+    y_trans=data_trans[:, 1]
+    for i in range(len(x)):
+        if y_cis[i] >= y_trans[i]:
+            ax.bar(x[i], y_cis[i], color="blue", width=bar_width, alpha=0.8, align="edge")
+            ax.bar(x[i], y_trans[i], color="yellow", width=bar_width, alpha=0.8, align="edge")
+            
+        else:
+            ax.bar(x[i], y_trans[i], color="yellow", width=bar_width, alpha=0.8, align="edge")
+            ax.bar(x[i], y_cis[i], color="blue", width=bar_width, alpha=0.8, align="edge")
+    ax.set_xticks([0.5] + [x[i] + 0.5 for i in range(14, 323, 15)])
+    ax.set_xticklabels([1] + [int(x[i]) for i in range(14, 323, 15)])
+    ax.set_xlim(0.5, 323.5)
+    ax.set_xlabel("Residue Number")
+    ax.set_ylabel("RMS Fluctuation (nm)")
+    ax.set_ylim(0, 0.75)
+    #ax.legend()
+    plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
+    plt.show()

### 2025-05-09 MD/Analysis/plot_ie.py
Plot final numwater. correct errors in plot_ie. prepare draft for graphs

@@ -32,11 +32,11 @@ for protein in ["qty", "wt"]:
     for group in groups:
         cis_data = load_xvg_ie(f"{protein}_cis_{targetname}_{group}.xvg", byres=False)
         data_temp.append(cis_data)
-        #trans_data = load_ie_not_byres(f"{protein}_trans_{targetname}_{group}.xvg")
+        #trans_data = load_xvg_ie(f"{protein}_trans_{targetname}_{group}.xvg"， byres=False)
         #data_temp.append(np.concatenate((cis_data, trans_data), axis=0))
     cis_data = load_xvg_ie(f"{protein}_cis_{targetname}_byres.xvg", byres=True)
     data_temp.append(cis_data)
-    #trans_data = load_ie_byres(f"{protein}_trans_{targetname}_{resname}.xvg")
+    #trans_data = load_xvg_ie(f"{protein}_trans_{targetname}_byres.xvg", byres=True)
     #data_temp.append(np.concatenate((cis_data, trans_data), axis=0))
     data = np.concatenate(data_temp, axis=0)
     

### 2025-05-09 MD/Analysis/plot_hbonds&numwater.py
draw hbonds and numwater together

@@ -1,0 +1,71 @@
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+
+def load_xvg_numwater(filename, start = 0):
+    data = []
+    with open(filename, "r") as f:
+        for line in f:
+            if not line.startswith(("#", "@")) and len(line.split()) > 0:
+                split = line.split()
+                data.append([float(split[i]) + start if i == 0 else int(float(split[i]) / 3) for i in range(len(split))])
+    return np.array(data)
+
+def load_xvg(filename, start = 0):
+    data = []
+    with open(filename, "r") as f:
+        for line in f:
+            if not line.startswith(("#", "@")):
+                split = line.split()
+                data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(len(split))])
+    return np.array(data)
+
+def compute_running_avg(x, y):
+    window_size = 500
+    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
+    x_avg = x[len(x) - len(running_avg) : ]
+    return x_avg, running_avg
+
+matplotlib.rcParams["font.family"] = "Calibri"
+
+for protein in ["qty", "wt"]:
+    target_water = "numwater"
+    cis_water = load_xvg_numwater(f"{protein}_cis_{target_water}.xvg", -10)
+    trans_water = load_xvg_numwater(f"{protein}_trans_{target_water}.xvg")
+    water_data = np.concatenate((cis_water, trans_water), axis=0)
+    x_water = water_data[:, 0]
+    y_water = water_data[:, 1]
+    x_water_avg, y_water_avg = compute_running_avg(x_water, y_water)
+
+    target_hbond = "hbonds"
+    cis_hbond = load_xvg(f"{protein}_cis_{target_hbond}.xvg", -10)
+    trans_hbond = load_xvg(f"{protein}_trans_{target_hbond}.xvg")
+    hbond_data = np.concatenate((cis_hbond, trans_hbond), axis=0)
+    x_hbond = hbond_data[:, 0]
+    y_hbond = hbond_data[:, 1]
+    x_hbond_avg, y_hbond_avg = compute_running_avg(x_hbond, y_hbond)
+
+    fig, ax1 = plt.subplots(figsize=(4, 2.5))
+    ax2 = ax1.twinx()
+
[…]

### 2025-05-09 MD/Analysis/plot_ie.py

@@ -40,12 +40,13 @@ for protein in ["qty", "wt"]:
     #data_temp.append(np.concatenate((cis_data, trans_data), axis=0))
     data = np.concatenate(data_temp, axis=0)
     
-    fig, ax = plt.subplots(figsize=(8, 5))
+    fig, ax = plt.subplots(figsize=(4, 5))
     vmax = np.max(np.abs(data))
     cax = ax.imshow(data, aspect="auto", cmap="RdBu_r", vmin=-vmax, vmax=vmax, origin="lower", interpolation="nearest")
-    fig.colorbar(cax)
     ax.set_xlabel("Time (ns)")
     ax.set_ylabel("")
+    ax.set_yticks(range(17))
+    ax.set_yticklabels(["Protein", "Pocket"] + reslabels[protein])
     ax.set_ylim(-0.5, 16.5)
     for y in np.arange(0.5, 17, 1):
         ax.axhline(y=y, color="black", linestyle="-", linewidth=1)
@@ -55,6 +56,8 @@ for protein in ["qty", "wt"]:
     ax.set_xticklabels(np.arange(-10, 120 + 1, 10))
     ax.axvline(x=10*500, color='b', linestyle='--')
     plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
+    fig.colorbar(cax)
+    plt.savefig(f"{protein}_{targetname}_colorbar.pdf", format="pdf", bbox_inches="tight")
     plt.show()
 
 

### 2025-05-09 MD/Analysis/plot_rmsd.py

@@ -15,11 +15,12 @@ def plot_running_avg(x, y, c="red", labelname=""):
     window_size = 500
     running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
     x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label=labelname, color=c)
+    plt.plot(x_avg, running_avg, label=labelname, color=c, linewidth=0.75)
 
 matplotlib.rcParams['font.family'] = 'Calibri'
 targetname = "rmsd"
 subtargetnames = ["solu", "tm6", "pocket", "ret"]
+labelnames = ["Protein and retinal", "TM6", "Binding pocket", "Retinal"]
 colors = [
     ["#000000", "#000000"],
     ["#000077", "#0000FF"],
@@ -27,13 +28,13 @@ colors = [
     ["#770000", "#FF0000"]
 ]
 for protein in ["qty", "wt"]:
-    plt.figure(figsize=(8, 5))
+    plt.figure(figsize=(4, 2.5))
     plt.xlabel("Time (ns)")
     plt.ylabel("RMSD (nm)")
     plt.title("")
     plt.xlim(-10, 120)
     plt.xticks(np.arange(-10, 121, 10))
-    plt.axvline(x=0, color='b', linestyle='--')
+    plt.axvline(x=0, color='brown', linestyle='--', linewidth=1)
     plt.grid(False)
     for i in range(len(subtargetnames)):
         cis_data = load_xvg(f"{protein}_cis_{targetname}_{subtargetnames[i]}.xvg", -10)
@@ -42,7 +43,7 @@ for protein in ["qty", "wt"]:
         x = data[:, 0]
         y = data[:, 1]
         #plt.plot(x, y, label=subtargetnames[i], color=colors[i][0], linewidth=0.5)
-        plot_running_avg(x, y, c=colors[i][1], labelname=subtargetnames[i])
-    plt.legend()
+        plot_running_avg(x, y, c=colors[i][1], labelname=labelnames[i])
+    plt.legend(loc='upper center', bbox_to_anchor=(0.5, -0.3), ncol=4)
     plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
     plt.show()

### 2025-05-09 MD/Analysis/plot_gyrate.py
update graphs

@@ -11,30 +11,30 @@ def load_xvg(filename, start = 0):
                 data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(2)])
     return np.array(data)
 
-def plot_running_avg(x, y, c="red", labelname=""):
+def plot_running_avg(x, y, c="red", labelname="1-ns running avg."):
     window_size = 500
     running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
     x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label=labelname, color=c)
+    plt.plot(x_avg, running_avg, label=labelname, color=c, linewidth=0.75)
 
 matplotlib.rcParams['font.family'] = 'Calibri'
 targetname = "gyrate"
 for protein in ["qty", "wt"]:
-    plt.figure(figsize=(8, 5))
+    plt.figure(figsize=(8, 4))
     plt.xlabel("Time (ns)")
     plt.ylabel("Radius (nm)")
     plt.title("")
     plt.xlim(-10, 120)
     plt.xticks(np.arange(-10, 121, 10))
-    plt.axvline(x=0, color='b', linestyle='--')
+    plt.axvline(x=0, color='brown', linestyle='--', linewidth=1)
     plt.grid(False)
     cis_data = load_xvg(f"{protein}_cis_{targetname}.xvg", -10)
     trans_data = load_xvg(f"{protein}_trans_{targetname}.xvg")
     data = np.concatenate((cis_data, trans_data), axis=0)
     x = data[:, 0]
     y = data[:, 1]
-    plt.plot(x, y, color="black", linewidth=0.5)
+    plt.plot(x, y, color="black", linewidth=0.5, label="Radius of gyration")
     plot_running_avg(x, y)
-    #plt.legend()
+    plt.legend()
     plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
     plt.show()

### 2025-05-09 MD/Analysis/plot_ie.py

@@ -54,7 +54,7 @@ for protein in ["qty", "wt"]:
     ax.set_xlim(0, (10 + 120) * 500)
     ax.set_xticks(np.arange(0, (10 + 120) * 500 + 1, 10 * 500))
     ax.set_xticklabels(np.arange(-10, 120 + 1, 10))
-    ax.axvline(x=10*500, color='b', linestyle='--')
+    ax.axvline(x=10*500, color='brown', linestyle='--', linewidth=1 )
     plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
     fig.colorbar(cax)
     plt.savefig(f"{protein}_{targetname}_colorbar.pdf", format="pdf", bbox_inches="tight")

### 2025-05-09 MD/Analysis/plot_rmsf.py

@@ -16,19 +16,19 @@ targetname = "rmsf"
 for protein in ["qty", "wt"]:
     data_cis = load_xvg_rmsf(f"{protein}_cis_{targetname}.xvg")
     data_trans = load_xvg_rmsf(f"{protein}_trans_{targetname}.xvg")
-    fig, ax = plt.subplots(figsize=(8, 5))
+    fig, ax = plt.subplots(figsize=(8, 4))
     bar_width = 1.0
     x = data_cis[:, 0]
     y_cis=data_cis[:, 1]
     y_trans=data_trans[:, 1]
     for i in range(len(x)):
         if y_cis[i] >= y_trans[i]:
-            ax.bar(x[i], y_cis[i], color="blue", width=bar_width, alpha=0.8, align="edge")
-            ax.bar(x[i], y_trans[i], color="yellow", width=bar_width, alpha=0.8, align="edge")
+            ax.bar(x[i], y_cis[i], color="#0000FF", width=bar_width, alpha=0.8, align="edge")
+            ax.bar(x[i], y_trans[i], color="#CCCC00", width=bar_width, alpha=0.8, align="edge")
             
         else:
-            ax.bar(x[i], y_trans[i], color="yellow", width=bar_width, alpha=0.8, align="edge")
-            ax.bar(x[i], y_cis[i], color="blue", width=bar_width, alpha=0.8, align="edge")
+            ax.bar(x[i], y_trans[i], color="#CCCC00", width=bar_width, alpha=0.8, align="edge")
+            ax.bar(x[i], y_cis[i], color="#0000FF", width=bar_width, alpha=0.8, align="edge")
     ax.set_xticks([0.5] + [x[i] + 0.5 for i in range(14, 323, 15)])
     ax.set_xticklabels([1] + [int(x[i]) for i in range(14, 323, 15)])
     ax.set_xlim(0.5, 323.5)

### 2025-05-09 MD/Analysis/plot_hbonds&numwater.py
Make static state figures for MD results

@@ -45,7 +45,7 @@ for protein in ["qty", "wt"]:
     y_hbond = hbond_data[:, 1]
     x_hbond_avg, y_hbond_avg = compute_running_avg(x_hbond, y_hbond)
 
-    fig, ax1 = plt.subplots(figsize=(4, 2.5))
+    fig, ax1 = plt.subplots(figsize=(4.5, 2.25))
     ax2 = ax1.twinx()
 
     ax1.plot(x_hbond_avg, y_hbond_avg, color="blue", label="Number of hydrogen bonds (1ns running avg.)", linewidth=0.75)

### 2025-05-09 MD/Analysis/plot_ie.py

@@ -40,7 +40,7 @@ for protein in ["qty", "wt"]:
     #data_temp.append(np.concatenate((cis_data, trans_data), axis=0))
     data = np.concatenate(data_temp, axis=0)
     
-    fig, ax = plt.subplots(figsize=(4, 5))
+    fig, ax = plt.subplots(figsize=(4.5, 4))
     vmax = np.max(np.abs(data))
     cax = ax.imshow(data, aspect="auto", cmap="RdBu_r", vmin=-vmax, vmax=vmax, origin="lower", interpolation="nearest")
     ax.set_xlabel("Time (ns)")

### 2025-05-09 Paper/Source/manuscript.tex
Complete manuscript text. Add graphs.

@@
 
-This study investigates the QTY design of 9 human and 3 microbial retinylidene proteins ... [TO BE WRITTEN]
+Retinylidene proteins are a large family of retinal-binding light-sensitive proteins, found in many organisms ranging from microbes to human.
+Microbial opsins have been utilized in optogenetics, while animal opsins are essential for vision and other non-visual light-dependent metabolic functions.
+However, all retinylidene proteins are membrane proteins with hydrophobic transmembrane domains, which makes it challenging to study them.
+In this structural and functional bioinformatics study, we used the QTY (Glutamine, Threonine, Tyrosine) code to design water-soluble QTY analogs of retinylidene proteins, including 9 human opsins and 3 microbial opsins.
+We provide the superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water soluble QTY variants, and experimentally-determined structures when available.
+We also provide a comparison of the surface hydrophobicity of the variants.
+Furthermore, we run molecular dynamics (MD) simulations of native and QTY-designed OPN2 and analyze their response to the 11-cis to all-trans isomerization of the retinal chromophore.
+The findings of this study indicate that the QTY code can be used as a robust tool to design water-solubility retinylidene proteins.
+These have potential applications in protein studies, therapeutic treatments, and bioengineering.
 
@@
 The subsequent conformational changes of the protein are well studied using bovine rhodopsin, which changes from dark state to BATHO state, then LUMI, META I, and META II \citep{Okada_2001}.
-Proton transfer plays a major role in this process \citep{Mahalingam_2008}.
-During this process, TM6 is characteristically moved outward, activating the G-protein.
+Proton transfer plays an important role in this process \citep{Mahalingam_2008}.
+As the protein conformation changes, TM6 characteristically moves outward, activating the G-protein.
 
@@
 Certain variants lead to autosomal recessive or autosomal dominant retinitis pigmentosa and congenital stationary night blindness \citep{Fanelli_2021}.
-OPN2 is a representative animal opsin, one of the earliest studied.
-In fact, bovine OPN2 is the first opsin to be sequenced \citep{Nathans_1984} as well as the first GPCR whose crystal structure was resolved experimentally \citep{Palczeski_2000}.
+OPN2 is a representative animal opsin, one of the first studied.
+In fact, bovine OPN2 is the first opsin to be sequenced \citep{Nathans_1984}, as well as the first GPCR whose crystal structure was resolved experimentally \citep{Palczeski_2000}.
 Many studies on the functional mechanisms of animal opsins also focus on OPN2.
-Consequently, we also chose OPN2 to conduct a functional analysis in this study, in order to further explore the effectiveness of the QTY design of retinylidene proteins.
+Consequently, we choose OPN2 to conduct a functional analysis in this study, in order to further explore the effectiveness of the QTY code in redesigning retinylidene proteins.
 
 \textbf{OPN3} (Opsin 3), also known as encephalopsin or panopsin, is activated by blue and ultraviolet A light.
-It is expressed in the brain \citep{Blackshaw_1999}.
+It was discovered in the brain \citep{Blackshaw_1999}.
 It is also expressed in melanocytes and keratinocytes in the skin and regulates functions such as melanogenesis, cell differentiation, and glucose uptake.
-It is also expressed in the liver, pancreas, kidney, lung, heart, and skeletal muscles.
-When it is expressed in neurons, neurotransmitter release is inhibit by light, which renders OPN3 a useful optogenetic tool \citep{Copits_2021}.
+Its expression is also found in the liver, pancreas, kidney, lung, heart, and skeletal muscles.
+When expressed in neurons, the release of neurotransmitters is inhibited by light, making OPN3 a useful inhibitory optogenetic tool \citep{Copits_2021}.
 
 \textbf{OPN4} (Opsin 4), also known as melanopsin, is expressed in ipRGC (intrinsically photosensitive Retinal Ganglion Cells) in the ganglion cell layer in the retina \citep{Provencio_1998}.
-It is essential for non-image-forming responses to light, including for pupillary reflex, optokinetic visual tracking response, and photoentrainment and regulation of circadian rhythm.
-Certain variants of OPN4 lead to seasonal affective disorder and other circadian rhythm disorders.
-\citep{Berson_2002}.
-Image formation via OPN4-containing ipRGCs is also a potential pathway of treatment for various eye diseases such as retinitis pigmentosa and diabetic retinopathy.
+It is essential for non-image-forming responses to light, including the pupillary reflex, optokinetic visual tracking response, and photoentrainment and regulation of circadian rhythm.
+Certain variants of OPN4 lead to seasonal affective disorder and other circadian rhythm disorders \citep{Berson_2002}.
+Rendering OPN4-containing ipRGCs capable of image formation is also a potential pathway for the treatment of various eye diseases such as retinitis pigmentosa and diabetic retinopathy.
 
@@
 It is another protein that preferentially binds to all-trans-retinal \citep{Cook_2017}.
-Although not much information is known about RRH, it can reasonably be inferred that it photoisomerizes all-trans-retinal to 11-cis state, and may play a role in the upkeeping of photoreceptor functions.
+Although not much information is known about RRH, it can reasonably be inferred that it photoisomerizes all-trans-retinal to 11-cis-retinal and may play a role in the upkeep of photoreceptor functions.
 
-\textbf{Bacterial opsins} are transmembrane ion pumps or channels \citep{Findlay_1986, Zhang_2011}.
+\textbf{Microbial opsins} are transmembrane ion pumps or channels \citep{Findlay_1986}.
 They are also 7TM, though this is due to convergent evolution rather than homology \citep{Yee_2013}.
-The isomerization of retinal is usually from all-trans to 13-cis, different from that in animal opsins \citep{Findlay_1986}.
-In addition, bacterial opsins often form oligomers to carry out their functions \citep{Gmelin_2007}.
+The chromophore, retinal, usually isomerizes from all-trans to 13-cis, different from the case of animal opsins \citep{Findlay_1986}.
+In addition, microbial opsins often form oligomers to carry out their functions \citep{Gmelin_2007}.
 
-In this study, we selected 3 bacterial opsins: BACR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P02945/entry}{P02945}), BACH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/B0R2U4/entry}{B0R2U4}), ChR2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q8RUT8/entry}{Q8RUT8}).
+In this study, we selected 3 microbial opsins: BACR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P02945/entry}{P02945}), BACH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/B0R2U4/entry}{B0R2U4}), ChR2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q8RUT8/entry}{Q8RUT8}).
 
-\textbf{BACR} (Bacteriorhodopsin) is a light-driven proton pump and is one of the first bacterial opsins discovered \citep{Oesterhelt_1971}.
+\textbf{BACR} (Bacteriorhodopsin) is a light-driven proton pump.
+It is one of the first microbial opsins discovered \citep{Oesterhelt_1971}.
 \textbf{BACH} (Halorhodopsin) is a light-driven chloride pump activated by yellow light \citep{Schobert_1982}.
@@
 Instead of taking a computational approach, we applied the QTY (Glutamine, Threonine, Tyrosine) code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins.
-There are structural similarities between hydrophobic and polar amino acids: leucine (L) \textit{vs} glutamine (Q); isoleucine (I) / valine (V) \textit{vs} threonine (T); and phenylalanine (F) \textit{vs} tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}.
+There are structural similarities between hydrophobic and polar amino acids: leucine (L) and glutamine (Q); isoleucine (I) / valine (V) and threonine (T); and phenylalanine (F) and tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}.
 This justifies the replacement of hydrophobic amino acids with polar ones.
-We initially applied the QTY code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding activities and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}.
+We initially applied the QTY code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}.
 We have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.
-Besides GPCRs, we have also used the QTY code to design water-soluble glucose transporters \citep{Smorodina_2022}, ABC transporters \citep{Pan_2024}, monoamine neurotransmitter transporters \citep{Karagol_Karagol_Alper_2024}, glutamate transporters \citep{Karagol_Karagol_Smorodina_2024, Karagol_2024}, mitochondrial megacomplex \citep{Chen_2025}, antibodies \citep{Li_Wang_2024}, potassium channels \citep{Smorodina_2024}, receptor kinases \citep{Li_Tang_2024}, transmembrane enzymes \citep{Chen_Pan_2025}, as well as bacterial enzymes with beta barrel structures \citep{Sajeev-Sheeja_2023, Sajeev-Sheeja_2024}.
-The QTY-designed water-soluble CXCR4 chemokine receptor has been successfully in biomimetic sensors \citep{Qing_2023}.
-We have also applied the rQTY (reverse QTY) code to design nanoparticles \citep{Meng_2023}.
+In addition to GPCR, we have also used the QTY code to design water-soluble glucose transporters \citep{Smorodina_2022}, ABC transporters \citep{Pan_2024}, monoamine neurotransmitter transporters \citep{Karagol_Karagol_Alper_2024}, glutamate transporters \citep{Karagol_Karagol_Smorodina_2024, Karagol_2024}, mitochondrial megacomplex \citep{Chen_2025}, antibodies \citep{Li_Wang_2024}, potassium channels \citep{Smorodina_2024}, receptor kinases \citep{Li_Tang_2024}, transmembrane enzymes \citep{Chen_Pan_2025}, as well as bacterial enzymes with beta barrel structures \citep{Sajeev-Sheeja_2023, Sajeev-Sheeja_2024}.
+The QTY-designed water-soluble CXCR4 chemokine receptor has been successfully used in biomimetic sensors \citep{Qing_2023}.
+We have also applied the rQTY (reverse QTY) code to design self-assembled nanoparticles \citep{Meng_2023}.
 
 AlphaFold2 was released by Google DeepMind in July 2021 \citep{Jumper_2021}.
-It greatly facilitated the study of QTY-designed protein variants.
+It has greatly facilitated the study of QTY-designed protein variants.
 Subsequently, AlphaFold3 was released in May 2024, featuring improved architecture and improved efficiency \citep{Abramson_2024}.
-Furthermore, AlphaFold3 enabled the accurate prediction of complexes of multiple proteins, as well as complexes with nucleic acids and certain small molecules.
+Furthermore, AlphaFold3 enabled the accurate prediction of complexes of multiple proteins, as well as complexes with modified residues, nucleic acids, ions, certain ligands.
 QTY studies have made use of these new features \citep{Chen_2025, Johnsson_2025}.
@@
 Its 5.0 version was released in 2015 \citep{Abraham_2015}.
-GROMACS enables an efficient and realistic simulation of biomolecular systems, and has been used to investigate the structural and functional properties of QTY-designed protein variants in various studies \citep{Karagol_2024, Li_Tang_2024, Smorodina_2024, Li_Wang_2024, Johnsson_2025}.
+GROMACS enables an efficient and realistic simulation of biomolecular systems and has been used to investigate the structural and functional properties of QTY-designed protein variants in various studies \citep{Karagol_2024, Li_Tang_2024, Smorodina_2024, Li_Wang_2024, Johnsson_2025}.
 
@@
 The native protein sequences for OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, RRH, BACR, BACH, and ChR2 were obtained from UniProt (\url{https://www.uniprot.org}).
-The sequence for ChR2 was truncated according to the experimentally determined structure in RCSB PDB (PDB ID: \href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
+The sequence for ChR2 was truncated according to the experimentally determined structure in the RCSB PDB (PDB ID: \href{https://www.rcsb.org/structure/8ZAN}{8ZAN}).
 The QTY designs were performed through the Protein Solubilizing Server (\url{https://pss.sjtu.edu.cn/}) \citep{Tao_2022}.
@@
 The retinal molecule was then manually switched to the all-trans state by rotating C13 to C15 and bonded hydrogen and methyl groups by 180 degrees around the C11-C12 bond.
-Energy minimization and equilibration were repeated exactly as before, and then a 200-ns production MD simulation was run.
+Energy minimization and equilibration were repeated exactly as before, and then a 120-ns production MD simulation was run.
 
-Regarding QTY-designed OPN2, the system was constructed directly using GROMACS.
+Regarding QTY-designed OPN2, we found that the helix 9 of the QTY analog was flung up and adhered to the originally transmembrane domain, which disrupted the normal conformation.
+Therefore, this helix was truncated.
+The system was constructed directly using GROMACS.
 The protein was centered in a rectangular box with dimensions equal to those of native OPN2.
@@
 
-[ANALYSIS METHODS OF MD SIMULATION RESULTS, TO BE ADDED.]
+After the simulations, we extracted frames from the trajectory to inspect the structures before and after retinal isomerization.
+We also calculated the RMSD (``gmx rms'' command), number of hydrogen bonds (``gmx hbond'' command) and water molecules (``gmx select'' command) inside the binding pocket, interaction energy (including short-range Coulombic interaction energy and short-range Lennard-Jones energy) (``gmx energy'' command), the RMSF (``gmx rmsf'' command), and radius of gyration (``gmx gyrate'' command).
+The detailed commands are publicly available in the online database for this study.
 
@@
 The QTY substitution resulted in an overall variation of the sequence of 15.48\% to 30.04\% and a variation of transmembrane domain of 35.53\% to 50.24\%.
-Despite changes to the amino acid composition and sequence, the pI only experiences a slight change, between 0.00 and 0.16.
+Despite changes in amino acid composition and sequence, the pI only experiences a slight change, between 0.00 and 0.16.
 This is because the amino acids Q, T, and Y have neutral charges and do not introduce additional charges to the system.
@@
 For OPN2, which has an available X-ray diffraction structure, we also superposed the experimentally determined structure with the AlphaFold3-predicted structures.
-Overall, the root mean square distances (RMSD) are small, from 0.307\AA to 0.611\AA, with only one exception of OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$ (RMSD = 0.999).
+Overall, the root mean square distances (RMSD) are small, from 0.307\AA to 0.611\AA, with only one exception of OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$ (RMSD = 0.999\AA).
 This shows that the water-soluble QTY analogs are quite similar to native proteins in terms of structure.
@@
 After applying the QTY code to respectively replace the hydrophobic amino acids L, I/V, and F with hydrophilic amino acids glutamine (Q), threonine (T), and tyrosine (Y), the hydrophobic surface areas are significantly reduced.
-More importantly, since the electron density maps of the corresponding amino acids are similar, the alpha helices in QTY analogs have a similar surface contour to the helices in the native proteins.
+More importantly, since the electron density maps of the corresponding amino acids are similar, the alpha helices in QTY analogs have a similar contour to those in the native proteins.
 The QTY analogs have successfully retained its structural integrity and stability.
@@
 Although AlphaFold3 allows the structural prediction of complexes that include small-molecule ligands, it only supports a small range of ligands, which does not include retinal.
-We were therefore unable to predict the structure of chromophore-bound states of retinylidene proteins.
+We were therefore unable to predict the structure of chromophore-bound states of retinylidene proteins with AlphaFold3.
 Consequently, we chose another approach, namely molecular dynamics simulation, in order to investigate the behavior of QTY opsin analogs when they are bound to the chromophore.
 
-\subsection*{Simulation of 11-cis to all-trans isomerization of retinal in native OPN2 and its QTY variant}
+\subsection*{Simulation of 11-cis to all-trans isomerization of retinal in native OPN2 and its QTY analog}
 
-Describe, explain, discuss MD simulation results.
-// NOTE: there were no changes to the NPxxY motif or retinal-binding Lys; "The ionic environment of the RSB, defined by the residues of the binding pocket, dictates the spectral and kinetic characteristics of each individual protein." \citep{Fenno_2011}, so QTY variant may have different absorption peak.
+We observe that QTY substitutions do not introduce changes to the essential NPxxY motif or the retinal-binding lysine of human retinylidene proteins.
+Therefore, we propose that QTY analogs of human opsins may have conserved functions and carry out a molecular dynamics (MD) simulation.
+We record and analyze the behavior of native OPN2 and its QTY analog before and after the 11-cis to all-trans isomerization.
 
-MD Results
+The MD simulation provides evidence of conformational change in both native and QTY analogs (Figure~\ref{fig:conformation}).
+The native protein experiences a slower change from its original conformation, while the QTY analog shows more fluctuations and sudden changes.
+Under further inspection, this phenomenon may be due to the entrance of water molecules into the QTY analog.
+In addition, retinal molecule has a greater degree of change in conformation in the native protein than in the QTY analog.
+Nevertheless, the retinal in the QTY analog is still able to cause changes to surrounding residues, sometimes doing so through contact with water molecules.
 
-* different states - binding pocket residues + ligand orientation
+Zooming in on the retinal-binding pocket, we observe that retinal is held within its binding pocket by several forces: the counterions of the retinal Schiff base (RSB) (113E and 181E), the hydrophobic interactions with neighboring residues (for example, 265W, 268Y, and the 187--189 beta strand), and, sometimes, steric collisions (Figure~\ref{fig:binding}).
+Since retinal is a ligand that binds in an internal pocket, we were unable to calculate the Gibbs free energy of its binding.
+Nevertheless, the distribution of interaction energies are found to be roughly the same in both native OPN2 and the water-soluble QTY analog, which is a strong suggestion of functional conservation.
+Finally, we observe very different hydrogen bonding and water molecule patterns inside the binding pocket, which is mainly due to several F to Y substitutions in that region.
+This may cause retinal to interact with adjacent residues in a subtly different way, and may lead to a different absorption peak since the environment of the RSB, i.e., the binding pocket, determines the spectral characteristic of opsins \citep{Fenno_2011}.
 
-* bond length, angle, dihedral, non-bonded interaction lengths graph
-
-* by-helix rmsd
-
-* by-residue IE
-
-* hbond
-
-* overall rmsd, gyrate, rmsf, IE
+Overall, we observe that QTY-designed OPN2 has relatively similar behavior to the native variant despite certain small differences caused by decreased hydrophobicity.
+The function of OPN2$^{\textrm{QTY}}$ awaits to be verified by experiments.
 
@@
 
-Future scopes and potential applications.
+The findings of this study indicate that the QTY code could be used as a robust tool to design water-soluble retinylidene proteins.
+
+This could, in the first place, facilitate the study of these proteins.
+The water-solubility of QTY analogs makes it easier to purify and investigate proteins, especially those such as RGR and RRH, which have not been studied much but may have considerable clinical relevance.
+The water-solubility also reduces the difficulty in recording the different phases of the photocycle, in comparison with native membrane opsins.
+Another application may be the rapid design of new optogenetic tools.
+
+Furthermore, water-soluble QTY opsins may be useful clinically, since they could be delivered and/or expressed in the eye without forming aggregates and precipitating.
+This may be a potential pathway in restoring basic vision for those who have lost it.
+
+Last but not least, water-soluble opsins have the potential to be harvested in mass and may be used to design new biomimetic light-sensing systems, which may have applications in bioengineering.
 
@@
 
-Conclusion
+In this study, we selected 12 retinylidene proteins, including 9 human opsins (OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, and RRH) and 3 microbial opsins (BACR, BACH, and ChR2), that have clinical implications and various applications.
+We applied the QTY code to convert the hydrophobic transmembrane alpha-helices into hydrophilic ones and thus create water-soluble QTY analogs of the proteins.
+Then, we used AlphaFold3 to predict the structures of the native proteins as well as the QTY analogs, superposed them, and found that the structure of the proteins are well conserved despite substantial residue substitutions.
+We also inspected the surface hydrophobicity of the proteins and found a great decrease in hydrophobic patches in the transmembrane surface.
+Next, we chose a representative retinylidene protein, OPN2, and employed molecular dynamics simulations to investigate the behavior of native and QTY analog of OPN2.
+We found that the QTY analog is capable of conformational change and effective protein-ligand interaction.
+These findings reveal that QTY-designed OPN2, and retinylidene proteins in general, may have conserved structure and function.
+We believe that these water-soluble QTY variants may have potentials in research, therapeutic treatments, and bioengineering.
 
@@
 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/function-conformation.jpg}
+	\caption{\textbf{The conformational changes of native OPN2 and its QTY analog before and after 11-cis to all-trans isomerization of the chromophore, retinal.
+} \textbf{a)} and \textbf{b)}: 1ns running averages of the root mean square distances (RMSD) of the protein-retinal complex, transmembrane helix 6 (TM6), the retinal-binding pocket, and retinal.
+\textbf{c)}: superpositions between cis-state OPN2, trans-state OPN2, cis-state OPN2$^{\textrm{QTY}}$, and trans-state OPN2$^{\textrm{QTY}}$.
+Blue: cis-state protein, orange: 11-cis-retinal; yellow: trans-state protein, greenish cyan: all-trans retinal.
+}
+	\label{fig:conformation}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{Figures/function-binding.jpg}
+	\caption{\textbf{Changes in the retinal-binding pocket and protein-ligand interaction in native OPN2 and its QTY analog before and after 11-cis to all-trans isomerization of the chromophore.
+} \textbf{a)} and \textbf{b)}: close-ups of the binding pocket in cis-state.
+Blue: protein residues, orange: 11-cis-retinal; dashed lines: same as a) and b).
+\textbf{c)} and \textbf{d)}: close-ups of the binding pocket in trans-state.
+Yellow: protein residues, greenish cyan: all-trans-retinal; green dashed lines: ion bridge; yellow dashed lines: van der Waals and/or hydrophobic interactions.
+\textbf{e)} and \textbf{f)}: the interaction energies between the protein, the binding pocket, individual residues, and retinal.
+The interaction energy is the sum of the short-range Coulombic interaction energy and short-range Lennard-Jones energy.
+Please note that the interaction energy is a product of MD simulation and is not necessarily a meaningful physical quantity.
+\textbf{g)} and \textbf{h)}: the number of hydrogen bonds formed between residues in the binding pocket, and the number of water molecules within the binding pocket.
+}
+	\label{fig:binding}
+\end{figure}
+
 \end{document}

### 2025-05-10 MD/Analysis/plot_gyrate.py
Clean up files except for MD/QTY and MD/WT.

@@ -1,40 +1,0 @@
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-
-def load_xvg(filename, start = 0):
-    data = []
-    with open(filename, "r") as f:
-        for line in f:
-            if not line.startswith(("#", "@")):
-                split = line.split()
-                data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(2)])
-    return np.array(data)
-
-def plot_running_avg(x, y, c="red", labelname="1-ns running avg."):
-    window_size = 500
-    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
-    x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label=labelname, color=c, linewidth=0.75)
-
-matplotlib.rcParams['font.family'] = 'Calibri'
-targetname = "gyrate"
-for protein in ["qty", "wt"]:
-    plt.figure(figsize=(8, 4))
-    plt.xlabel("Time (ns)")
-    plt.ylabel("Radius (nm)")
-    plt.title("")
-    plt.xlim(-10, 120)
-    plt.xticks(np.arange(-10, 121, 10))
-    plt.axvline(x=0, color='brown', linestyle='--', linewidth=1)
-    plt.grid(False)
-    cis_data = load_xvg(f"{protein}_cis_{targetname}.xvg", -10)
-    trans_data = load_xvg(f"{protein}_trans_{targetname}.xvg")
-    data = np.concatenate((cis_data, trans_data), axis=0)
-    x = data[:, 0]
-    y = data[:, 1]
-    plt.plot(x, y, color="black", linewidth=0.5, label="Radius of gyration")
-    plot_running_avg(x, y)
-    plt.legend()
-    plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
-    plt.show()

### 2025-05-10 MD/Analysis/plot_hbonds&numwater.py

@@ -1,71 +1,0 @@
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-
-def load_xvg_numwater(filename, start = 0):
-    data = []
-    with open(filename, "r") as f:
-        for line in f:
-            if not line.startswith(("#", "@")) and len(line.split()) > 0:
-                split = line.split()
-                data.append([float(split[i]) + start if i == 0 else int(float(split[i]) / 3) for i in range(len(split))])
-    return np.array(data)
-
-def load_xvg(filename, start = 0):
-    data = []
-    with open(filename, "r") as f:
-        for line in f:
-            if not line.startswith(("#", "@")):
-                split = line.split()
-                data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(len(split))])
-    return np.array(data)
-
-def compute_running_avg(x, y):
-    window_size = 500
-    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
-    x_avg = x[len(x) - len(running_avg) : ]
-    return x_avg, running_avg
-
-matplotlib.rcParams["font.family"] = "Calibri"
-
-for protein in ["qty", "wt"]:
-    target_water = "numwater"
-    cis_water = load_xvg_numwater(f"{protein}_cis_{target_water}.xvg", -10)
-    trans_water = load_xvg_numwater(f"{protein}_trans_{target_water}.xvg")
-    water_data = np.concatenate((cis_water, trans_water), axis=0)
-    x_water = water_data[:, 0]
-    y_water = water_data[:, 1]
-    x_water_avg, y_water_avg = compute_running_avg(x_water, y_water)
-
-    target_hbond = "hbonds"
-    cis_hbond = load_xvg(f"{protein}_cis_{target_hbond}.xvg", -10)
-    trans_hbond = load_xvg(f"{protein}_trans_{target_hbond}.xvg")
-    hbond_data = np.concatenate((cis_hbond, trans_hbond), axis=0)
-    x_hbond = hbond_data[:, 0]
-    y_hbond = hbond_data[:, 1]
-    x_hbond_avg, y_hbond_avg = compute_running_avg(x_hbond, y_hbond)
-
-    fig, ax1 = plt.subplots(figsize=(4.5, 2.25))
-    ax2 = ax1.twinx()
-
[…]

### 2025-05-10 MD/Analysis/plot_hbonds.py

@@ -1,40 +1,0 @@
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-
-def load_xvg(filename, start = 0):
-    data = []
-    with open(filename, "r") as f:
-        for line in f:
-            if not line.startswith(("#", "@")):
-                split = line.split()
-                data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(len(split))])
-    return np.array(data)
-
-def plot_running_avg(x, y):
-    window_size = 500
-    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
-    x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label="1-ns Running Avg", color="red")
-
-matplotlib.rcParams['font.family'] = 'Calibri'
-targetname = "hbonds"
-for protein in ["qty", "wt"]:
-    cis_data = load_xvg(f"{protein}_cis_{targetname}.xvg", -10)
-    trans_data = load_xvg(f"{protein}_trans_{targetname}.xvg")
-    data = np.concatenate((cis_data, trans_data), axis=0)
-    x = data[:, 0]
-    y = data[:, 1]
-    plt.figure(figsize=(8, 5))
-    plt.plot(x, y, label="", color="black", linewidth=0.5)
-    plot_running_avg(x, y)
-    plt.xlabel("Time (ns)")
-    plt.ylabel("Number of hydrogen bonds within binding pocket")
-    plt.title("")
-    plt.xlim(-10, 120)
-    plt.xticks(np.arange(-10, 121, 10))
-    plt.axvline(x=0, color='b', linestyle='--')
-    #plt.legend()
-    plt.grid(False)
-    plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
-    plt.show()

### 2025-05-10 MD/Analysis/plot_ie.py

@@ -1,75 +1,0 @@
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-
-def load_xvg_ie(filename, byres = False):
-    data = [[] for _ in range(15)] if byres else [[]]
-    with open(filename, "r") as f:
-        for line in f:
-            if not line.startswith(("#", "@")) and len(line.split()) > 0:
-                split = line.split()
-                if byres:
-                    for i in range(15):
-                        data[i].append(float(split[2 * i + 1]) + float(split[2 * i + 2]))
-                else:
-                    data[0].append(float(split[1]) + float(split[2]))
-    return np.array(data)
-
-matplotlib.rcParams['font.family'] = 'Calibri'
-data = []
-targetname = "ie"
-reslabels = {
-    "qty": ["265W", "113E", "181E", "268Y", "207M", "186S", "191Y", "187C", "188G", "189I", "117A", "292A", "212Y", "295A", "208Y"], 
-    "wt" : ["265W", "113E", "181E", "268Y", "207M", "186S", "191Y", "187C", "188G", "189I", "117A", "292A", "212F", "295A", "208F"]
-}
-matplotlib.rcParams['font.family'] = 'Calibri'
-targetname = "ie"
-resids = [265, 113, 181, 268, 207, 186, 191, 187, 188, 189, 117, 292, 212, 295, 208]
-resnames = [int(resid) for resid in resids]
-groups = ["prot", "pocket"]
-for protein in ["qty", "wt"]:
-    data_temp = []
-    for group in groups:
-        cis_data = load_xvg_ie(f"{protein}_cis_{targetname}_{group}.xvg", byres=False)
-        data_temp.append(cis_data)
-        #trans_data = load_xvg_ie(f"{protein}_trans_{targetname}_{group}.xvg"， byres=False)
-        #data_temp.append(np.concatenate((cis_data, trans_data), axis=0))
-    cis_data = load_xvg_ie(f"{protein}_cis_{targetname}_byres.xvg", byres=True)
-    data_temp.append(cis_data)
-    #trans_data = load_xvg_ie(f"{protein}_trans_{targetname}_byres.xvg", byres=True)
-    #data_temp.append(np.concatenate((cis_data, trans_data), axis=0))
[…]

### 2025-05-10 MD/Analysis/plot_numwater.py

@@ -1,40 +1,0 @@
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-
-def load_xvg(filename, start = 0):
-    data = []
-    with open(filename, "r") as f:
-        for line in f:
-            if not line.startswith(("#", "@")) and len(line.split()) > 0:
-                split = line.split()
-                data.append([float(split[i]) + start if i == 0 else int(float(split[i]) / 3) for i in range(len(split))])
-    return np.array(data)
-
-def plot_running_avg(x, y):
-    window_size = 500
-    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
-    x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label="1-ns Running Avg", color="red")
-
-matplotlib.rcParams['font.family'] = 'Calibri'
-targetname = "numwater"
-for protein in ["qty", "wt"]:
-    cis_data = load_xvg(f"{protein}_cis_{targetname}.xvg", -10)
-    trans_data = load_xvg(f"{protein}_trans_{targetname}.xvg")
-    data = np.concatenate((cis_data, trans_data), axis=0)
-    x = data[:, 0]
-    y = data[:, 1]
-    plt.figure(figsize=(8, 5))
-    plt.plot(x, y, label="", color="black", linewidth=0.5)
-    plot_running_avg(x, y)
-    plt.xlabel("Time (ns)")
-    plt.ylabel("Number of water molecules within binding pocket")
-    plt.title("")
-    plt.xlim(-10, 120)
-    plt.xticks(np.arange(-10, 121, 10))
-    plt.axvline(x=0, color='b', linestyle='--')
-    #plt.legend()
-    plt.grid(False)
-    plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
-    plt.show()

### 2025-05-10 MD/Analysis/plot_rmsd.py

@@ -1,49 +1,0 @@
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-
-def load_xvg(filename, start = 0):
-    data = []
-    with open(filename, "r") as f:
-        for line in f:
-            if not line.startswith(("#", "@")):
-                split = line.split()
-                data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(len(split))])
-    return np.array(data)
-
-def plot_running_avg(x, y, c="red", labelname=""):
-    window_size = 500
-    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
-    x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label=labelname, color=c, linewidth=0.75)
-
-matplotlib.rcParams['font.family'] = 'Calibri'
-targetname = "rmsd"
-subtargetnames = ["solu", "tm6", "pocket", "ret"]
-labelnames = ["Protein and retinal", "TM6", "Binding pocket", "Retinal"]
-colors = [
-    ["#000000", "#000000"],
-    ["#000077", "#0000FF"],
-    ["#007700", "#00FF00"],
-    ["#770000", "#FF0000"]
-]
-for protein in ["qty", "wt"]:
-    plt.figure(figsize=(4, 2.5))
-    plt.xlabel("Time (ns)")
-    plt.ylabel("RMSD (nm)")
-    plt.title("")
-    plt.xlim(-10, 120)
-    plt.xticks(np.arange(-10, 121, 10))
-    plt.axvline(x=0, color='brown', linestyle='--', linewidth=1)
-    plt.grid(False)
-    for i in range(len(subtargetnames)):
-        cis_data = load_xvg(f"{protein}_cis_{targetname}_{subtargetnames[i]}.xvg", -10)
-        trans_data = load_xvg(f"{protein}_trans_{targetname}_{subtargetnames[i]}.xvg")
-        data = np.concatenate((cis_data, trans_data), axis=0)
-        x = data[:, 0]
-        y = data[:, 1]
-        #plt.plot(x, y, label=subtargetnames[i], color=colors[i][0], linewidth=0.5)
-        plot_running_avg(x, y, c=colors[i][1], labelname=labelnames[i])
-    plt.legend(loc='upper center', bbox_to_anchor=(0.5, -0.3), ncol=4)
-    plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
-    plt.show()

### 2025-05-10 MD/Analysis/plot_rmsd_byres.py

@@ -1,45 +1,0 @@
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-
-def load_xvg(filename, start = 0):
-    data = []
-    with open(filename, "r") as f:
-        for line in f:
-            if not line.startswith(("#", "@")):
-                split = line.split()
-                data.append([float(split[i]) + start if i == 0 else float(split[i]) for i in range(len(split))])
-    return np.array(data)
-
-def plot_running_avg(x, y, c="red", labelname="", window=1):
-    window_size = window * 500
-    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
-    x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label=labelname, color=c)
-
-matplotlib.rcParams['font.family'] = 'Calibri'
-targetname = "rmsd"
-subtargetids = [296, 265, 113, 181, 268, 207, 186, 191, 187, 188, 189, 117, 292, 212, 295, 208]
-subtargetnames = [int(subtargetid) for subtargetid in subtargetids]
-cmap = plt.cm.get_cmap("tab20", 16)
-colors = [cmap(i) for i in range(16)]
-for protein in ["qty", "wt"]:
-    plt.figure(figsize=(8, 5))
-    plt.xlabel("Time (ns)")
-    plt.ylabel("RMSD (nm)")
-    plt.title("")
-    plt.xlim(-10, 120)
-    plt.xticks(np.arange(-10, 121, 10))
-    plt.axvline(x=0, color='b', linestyle='--')
-    plt.grid(False)
-    for i in range(len(subtargetnames)):
-        cis_data = load_xvg(f"{protein}_cis_{targetname}_{subtargetnames[i]}.xvg", -10)
-        trans_data = load_xvg(f"{protein}_trans_{targetname}_{subtargetnames[i]}.xvg")
-        data = np.concatenate((cis_data, trans_data), axis=0)
-        x = data[:, 0]
-        y = data[:, 1]
-        #plt.plot(x, y, label=subtargetnames[i], color=colors[i][0], linewidth=0.5)
-        plot_running_avg(x, y, c=colors[i], labelname=subtargetnames[i], window=2)
-    plt.legend()
-    plt.savefig(f"{protein}_{targetname}_byres.pdf", format="pdf", bbox_inches="tight")
-    plt.show()

### 2025-05-10 MD/Analysis/plot_rmsf.py

@@ -1,40 +1,0 @@
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-
-def load_xvg_rmsf(filename):
-    data = []
-    with open(filename, "r") as f:
-        for line in f:
-            if not line.startswith(("#", "@")) and len(line.split()) > 0 \
-                and int(line.split()[0]) < 323:
-                data.append([int(line.split()[i]) if i == 0 else float(line.split()[i]) for i in range(2)])
-    return np.array(data)
-
-matplotlib.rcParams["font.family"] = "Calibri"
-targetname = "rmsf"
-for protein in ["qty", "wt"]:
-    data_cis = load_xvg_rmsf(f"{protein}_cis_{targetname}.xvg")
-    data_trans = load_xvg_rmsf(f"{protein}_trans_{targetname}.xvg")
-    fig, ax = plt.subplots(figsize=(8, 4))
-    bar_width = 1.0
-    x = data_cis[:, 0]
-    y_cis=data_cis[:, 1]
-    y_trans=data_trans[:, 1]
-    for i in range(len(x)):
-        if y_cis[i] >= y_trans[i]:
-            ax.bar(x[i], y_cis[i], color="#0000FF", width=bar_width, alpha=0.8, align="edge")
-            ax.bar(x[i], y_trans[i], color="#CCCC00", width=bar_width, alpha=0.8, align="edge")
-            
-        else:
-            ax.bar(x[i], y_trans[i], color="#CCCC00", width=bar_width, alpha=0.8, align="edge")
-            ax.bar(x[i], y_cis[i], color="#0000FF", width=bar_width, alpha=0.8, align="edge")
-    ax.set_xticks([0.5] + [x[i] + 0.5 for i in range(14, 323, 15)])
-    ax.set_xticklabels([1] + [int(x[i]) for i in range(14, 323, 15)])
-    ax.set_xlim(0.5, 323.5)
-    ax.set_xlabel("Residue Number")
-    ax.set_ylabel("RMS Fluctuation (nm)")
-    ax.set_ylim(0, 0.75)
-    #ax.legend()
-    plt.savefig(f"{protein}_{targetname}.pdf", format="pdf", bbox_inches="tight")
-    plt.show()

### 2025-05-10 MD/QTY-trans-only/Backup/Delete_atom.py

@@ -1,76 +1,0 @@
-import re
-
-def delete_atom_and_update_indices(file_path, write_path, atom_index):
-    with open(file_path, "r") as file:
-        lines = file.readlines()
-
-    atom_index = int(atom_index)
-    atom_section = 0
-    current_section = ""
-    sections_to_update = ["[ pairs ]", "[ bonds ]", "[ angles ]", "[ dihedrals ]", "[ cmap ]"]
-    section_to_format = {
-        "[ pairs ]": "{:>5}{:>6}{:>6}",
-        "[ bonds ]": "{:>5}{:>6}{:>6}",
-        "[ angles ]": "{:>5}{:>6}{:>6}{:>6}",
-        "[ dihedrals ]": "{:>5}{:>6}{:>6}{:>6}{:>6}",
-        "[ cmap ]": "{:>5}{:>6}{:>6}{:>6}{:>6}{:>6}"
-    }
-    updated_lines = []
-    atom_indices_to_delete = set()
-
-    for line in lines:
-        if line.strip().startswith("[ atoms ]"):
-            atom_section = 1
-        elif line.strip().startswith("["):
-            atom_section = -1
-
-        if atom_section == 0:
-            updated_lines.append(line)
-            continue
-        elif atom_section == 1:
-            updated_lines.append(line)
-            atom_section = 2
-        elif atom_section == 2:
-            if line.strip() and not line.strip().startswith(";"):
-                parts = line.split()
-                if int(parts[0]) == atom_index:
-                    atom_indices_to_delete.add(atom_index)
-                    continue
-                elif int(parts[0]) > atom_index:
-                    parts[0] = str(int(parts[0]) - 1)
-                formatted_line = "{:>7}{:>11}{:>7}{:>7}{:>7}{:>7}{:>11}{:>11}".format(*parts)
-                updated_lines.append(formatted_line + "\n")
-            else:
-                updated_lines.append(line)
-        elif atom_section == -1:
-            updated_lines.append(line)
-            if any(line.strip().startswith(section) for section in sections_to_update):
-                atom_section = -2
-                current_section = line.strip()
-            else:
-                atom_section = -3
-        elif atom_section == -2:
-            if line.strip() and not line.strip().startswith(";")  and not line.strip().startswith("#"):
-                parts = line.split()
-                if any(int(index) in atom_indices_to_delete for index in parts[:-1]):
-                    continue
[…]

### 2025-05-10 MD/QTY-try-trans-to-cis-2/rotate_coordinates.py

@@ -1,34 +1,0 @@
-from math import *
-
-def rotate_180(point, axis, ref_point):
-    point = [point[i] - ref_point[i] for i in range(3)]
-    dot_product = sum([point[i]*axis[i] for i in range(3)])
-    norm_axis_sq = sum([axis[i]**2 for i in range(3)])
-    proj = [dot_product/norm_axis_sq*axis[i] for i in range(3)]
-    orth = [point[i] - proj[i] for i in range(3)]
-    new_point = [proj[i] - orth[i] for i in range(3)]
-    new_point = [new_point[i] + ref_point[i] for i in range(3)]
-    return new_point
-
-with open("coordinates_to_rotate.txt", "r") as file:
-    lines = file.readlines()
-
-ref_point_0 = [float(lines[0].strip().split()[i]) for i in [2, 3, 4]]
-ref_point_1 = [float(lines[1].strip().split()[i]) for i in [2, 3, 4]]
-axis = [ref_point_1[i] - ref_point_0[i] for i in [0, 1, 2]]
-
-points_to_rotate = []
-for i in range (3, len(lines)):
-    points_to_rotate.append(lines[i].strip().split())
-
-points_rotated = []
-for point in points_to_rotate:
-    point_id = [point[0], point[1]]
-    rotated_pos = rotate_180([float(point[i]) for i in [2, 3, 4]], axis, ref_point_1)
-    rotated_pos = [str(round(rotated_pos[i], 5)) for i in range(3)]
-    rotated_vel = rotate_180([float(point[i]) for i in [5, 6, 7]], axis, [0, 0, 0])
-    rotated_vel = [str(round(rotated_vel[i], 5)) for i in range(3)]
-    points_rotated.append(point_id + rotated_pos + rotated_vel)
-
-with open("coordinates_rotated.txt", "w") as file:
-    lines = file.writelines([" ".join(point) + "\n" for point in points_rotated])

### 2025-05-10 MD/QTY-wrong-dihedral/Delete_atom_gro.py

@@ -1,30 +1,0 @@
-import re
-
-def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms):
-    with open(file_path, "r") as file:
-        lines = file.readlines()
-    updated_lines = []
-    num_deleted = 0
-
-    for line in lines:
-        line_splitted = line.split()
-        if len(line_splitted) != 6:
-            updated_lines.append(line)
-            continue
-        atom_index = int(line_splitted[2])
-        if atom_index in target_delete_atoms:
-            num_deleted += 1
-            continue
-        new_line_splitted = line_splitted[:2] + [str(atom_index - num_deleted)] + line_splitted[3:]
-        formatted_line = "{:>8}{:>7}{:>5}{:>8}{:>8}{:>8}\n".format(*new_line_splitted)
-        updated_lines.append(formatted_line)
-
-    with open(write_path, "w") as file:
-        file.writelines(updated_lines)
-
-file_path = "complex.gro"
-write_path = "complex_new.gro"
-target_delete_atoms = [4547, 4548, 5342, 5343]
-delete_atom_and_update_indices(file_path, write_path, target_delete_atoms)
-
-# Remember to manually edit the total atom count!

### 2025-05-10 MD/Retinal Parameters/Delete_atom_top.py

@@ -1,76 +1,0 @@
-import re
-
-def delete_atom_and_update_indices(file_path, write_path, atom_index):
-    with open(file_path, "r") as file:
-        lines = file.readlines()
-
-    atom_index = int(atom_index)
-    atom_section = 0
-    current_section = ""
-    sections_to_update = ["[ pairs ]", "[ bonds ]", "[ angles ]", "[ dihedrals ]", "[ cmap ]"]
-    section_to_format = {
-        "[ pairs ]": "{:>5}{:>6}{:>6}",
-        "[ bonds ]": "{:>5}{:>6}{:>6}",
-        "[ angles ]": "{:>5}{:>6}{:>6}{:>6}",
-        "[ dihedrals ]": "{:>5}{:>6}{:>6}{:>6}{:>6}",
-        "[ cmap ]": "{:>5}{:>6}{:>6}{:>6}{:>6}{:>6}"
-    }
-    updated_lines = []
-    atom_indices_to_delete = set()
-
-    for line in lines:
-        if line.strip().startswith("[ atoms ]"):
-            atom_section = 1
-        elif line.strip().startswith("["):
-            atom_section = -1
-
-        if atom_section == 0:
-            updated_lines.append(line)
-            continue
-        elif atom_section == 1:
-            updated_lines.append(line)
-            atom_section = 2
-        elif atom_section == 2:
-            if line.strip() and not line.strip().startswith(";"):
-                parts = line.split()
-                if int(parts[0]) == atom_index:
-                    atom_indices_to_delete.add(atom_index)
-                    continue
-                elif int(parts[0]) > atom_index:
-                    parts[0] = str(int(parts[0]) - 1)
-                formatted_line = "{:>7}{:>11}{:>7}{:>7}{:>7}{:>7}{:>11}{:>11}".format(*parts)
-                updated_lines.append(formatted_line + "\n")
-            else:
-                updated_lines.append(line)
-        elif atom_section == -1:
-            updated_lines.append(line)
-            if any(line.strip().startswith(section) for section in sections_to_update):
-                atom_section = -2
-                current_section = line.strip()
-            else:
-                atom_section = -3
-        elif atom_section == -2:
-            if line.strip() and not line.strip().startswith(";")  and not line.strip().startswith("#"):
-                parts = line.split()
-                if any(int(index) in atom_indices_to_delete for index in parts[:-1]):
-                    continue
[…]

### 2025-05-10 MD/WT-wrong-ff/Delete_atom_top.py

@@ -1,76 +1,0 @@
-import re
-
-def delete_atom_and_update_indices(file_path, write_path, atom_index):
-    with open(file_path, "r") as file:
-        lines = file.readlines()
-
-    atom_index = int(atom_index)
-    atom_section = 0
-    current_section = ""
-    sections_to_update = ["[ pairs ]", "[ bonds ]", "[ angles ]", "[ dihedrals ]", "[ cmap ]"]
-    section_to_format = {
-        "[ pairs ]": "{:>5}{:>6}{:>6}",
-        "[ bonds ]": "{:>5}{:>6}{:>6}",
-        "[ angles ]": "{:>5}{:>6}{:>6}{:>6}",
-        "[ dihedrals ]": "{:>5}{:>6}{:>6}{:>6}{:>6}",
-        "[ cmap ]": "{:>5}{:>6}{:>6}{:>6}{:>6}{:>6}"
-    }
-    updated_lines = []
-    atom_indices_to_delete = set()
-
-    for line in lines:
-        if line.strip().startswith("[ atoms ]"):
-            atom_section = 1
-        elif line.strip().startswith("["):
-            atom_section = -1
-
-        if atom_section == 0:
-            updated_lines.append(line)
-            continue
-        elif atom_section == 1:
-            updated_lines.append(line)
-            atom_section = 2
-        elif atom_section == 2:
-            if line.strip() and not line.strip().startswith(";"):
-                parts = line.split()
-                if int(parts[0]) == atom_index:
-                    atom_indices_to_delete.add(atom_index)
-                    continue
-                elif int(parts[0]) > atom_index:
-                    parts[0] = str(int(parts[0]) - 1)
-                formatted_line = "{:>7}{:>11}{:>7}{:>7}{:>7}{:>7}{:>11}{:>11}".format(*parts)
-                updated_lines.append(formatted_line + "\n")
-            else:
-                updated_lines.append(line)
-        elif atom_section == -1:
-            updated_lines.append(line)
-            if any(line.strip().startswith(section) for section in sections_to_update):
-                atom_section = -2
-                current_section = line.strip()
-            else:
-                atom_section = -3
-        elif atom_section == -2:
-            if line.strip() and not line.strip().startswith(";")  and not line.strip().startswith("#"):
-                parts = line.split()
-                if any(int(index) in atom_indices_to_delete for index in parts[:-1]):
-                    continue
[…]

### 2025-05-10 MD/WT-wrong-ff/gro_formatter.py

@@ -1,18 +1,0 @@
-with open("step5_input_shifted.txt", "r") as file:
-    lines = file.readlines()
-    
-widths = [5, 4, 6, 5, 8, 8, 8]
-new_lines = []
-for line in lines:
-    parts = line.split()
-    new_parts = []
-    for i in range(len(widths)):
-        if i == 1:
-            new_parts.append(parts[i].ljust(widths[i], " "))
-        else:
-            new_parts.append(parts[i].rjust(widths[i], " "))
-    new_line = "".join(new_parts)
-    new_lines.append(new_line + "\n")
-
-with open("step5_input_formatted.txt", "w") as file:
-    file.writelines(new_lines)

### 2025-05-10 MD/WT-wrong-ff/set_dihedral.py

@@ -1,61 +1,0 @@
-from math import *
-
-def rotate(point, axis, ref_point, angle):
-    rel_point = [point[i] - ref_point[i] for i in range(3)]
-    rel_new_point = [0, 0, 0]
-    angle_rad = angle *pi / 180
-    axis_normalized = [axis[i] / sqrt(sum([axis[j]**2 for j in range(3)])) for i in range(3)]
-    dot = sum([rel_point[i] * axis_normalized[i] for i in range(3)])
-    cross = [rel_point[(i+1)%3]*axis_normalized[(i+2)%3] - rel_point[(i+2)%3]*axis_normalized[(i+1)%3] for i in range(3)]
-    parallel = [axis_normalized[i] * dot for i in range(3)]
-    perpendicular = [rel_point[i] - parallel[i] for i in range(3)]
-    rotated_perpendicular = [perpendicular[i] * cos(angle_rad) + cross[i] * sin(angle_rad) for i in range(3)]
-    rel_new_point = [parallel[i] + rotated_perpendicular[i] for i in range(3)]
-    new_point = [rel_new_point[i] + ref_point[i] for i in range(3)]
-    return new_point
-
-def measure_dihedral(a, b, c, d):
-    ab = [a[i] - b[i] for i in range(3)]
-    bc = [b[i] - c[i] for i in range(3)]
-    cd = [c[i] - d[i] for i in range(3)]
-    ab_cross_bc = [ab[1]*bc[2] - ab[2]*bc[1], ab[2]*bc[0] - ab[0]*bc[2], ab[0]*bc[1] - ab[1]*bc[0]]
-    bc_cross_cd = [bc[1]*cd[2] - bc[2]*cd[1], bc[2]*cd[0] - bc[0]*cd[2], bc[0]*cd[1] - bc[1]*cd[0]]
-    ab_cross_bc_length = sqrt(sum([x**2 for x in ab_cross_bc]))
-    bc_cross_cd_length = sqrt(sum([x**2 for x in bc_cross_cd]))
-    cos_angle = sum([ab_cross_bc[i]*bc_cross_cd[i] for i in range(3)]) / (ab_cross_bc_length * bc_cross_cd_length)
-    dihedral = acos(cos_angle) * 180 / pi
-    return dihedral
-
-with open("coordinates_to_rotate.txt", "r") as file:
-    lines = file.readlines()
-
-# axis is b-c
-# pivot is c
-# dihedral is a-b-c-d
-# delete the first column of resi/resn in .gro file
[…]

### 2025-05-10 MD/plot_xvg_change_to_use.py

@@ -1,34 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-def load_xvg(filename):
-    data = []
-    with open(filename, "r") as f:
-        for line in f:
-            if not line.startswith(("#", "@")):
-                data.append([float(x) for x in line.split()])
-    return np.array(data)
-
-def plot_running_avg(x, y):
-    window_size = 1000
-    running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
-    x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label="X-ps Running Avg", color="red")
-
-filename = "QTY-cut/rmsd_cis_md_again"
-data = load_xvg(f"{filename}.xvg")
-x = [time - 10 for time in data[:, 0]]
-y = data[:, 1]
-plt.figure(figsize=(8, 5))
-plt.plot(x, y, label="", color="black")
-plot_running_avg(x, y)
-plt.xlabel("time (ns)")
-plt.ylabel("RMSD (nm)")
-plt.title("")
-#plt.ylim(0, 1.2)
-plt.axvline(x=0, color='b', linestyle='--')
-#plt.xlim(-10, 0)
-#plt.legend()
-plt.grid(False)
-plt.savefig(f"{filename}.pdf", format="pdf", bbox_inches="tight")
-plt.show()

### 2025-05-10 MD simulation/QTY-cut/Delete_atom_gro.py
Ready for publishing.

@@ -1,58 +1,0 @@
-import re
-
-def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms, target_delete_residues):
-    with open(file_path, "r") as file:
-        lines = file.readlines()
-    updated_lines = []
-    num_deleted = 0
-    num_res_deleted = 0
-    res_deleted = []
-
-    for line in lines:
-        line_splitted = line.split()
-        if len(line_splitted) != 6:
-            updated_lines.append(line)
-            continue
-        atom_index = int(line_splitted[2])
-        line_0 = line_splitted[0]
-        res_index = int(line_0[:-3])
-        res_index -= num_res_deleted
-        res_name = line_0[-3:]
-        if atom_index > 62450:
-            pass
-        if atom_index in target_delete_atoms:
-            num_deleted += 1
-            if res_index in target_delete_residues and res_index not in res_deleted:
-                num_res_deleted += 1
-                res_deleted.append(res_index)
-            continue
-        new_line_splitted = [str(res_index), res_name, line_splitted[1], str(atom_index - num_deleted)] + line_splitted[3:]
-        formatted_line = "{:>5}{:>3}{:>7}{:>5}{:>8}{:>8}{:>8}\n".format(*new_line_splitted)
-        updated_lines.append(formatted_line)
-
-    with open(write_path, "w") as file:
-        file.writelines(updated_lines)
-
-file_path = "solv_ions_again.gro"
-write_path = "solv_ions_again_new.gro"
-target_delete_atoms = [
-    62459, 62460, 62461, 
-    62501, 62502, 62503, 
-    78107, 78108, 78109, 
-    78110, 78111, 78112, 
-    78116, 78117, 78118, 
-    78146, 78147, 78148, 
-    78167, 78168, 78169
-]
-target_delete_residues = [
-    19472,
-    19486,
-    24688,
-    24689,
-    24691,
-    24701,
-    24708
-]
-delete_atom_and_update_indices(file_path, write_path, target_delete_atoms, target_delete_residues)
-
-# Remember to manually edit the total atom count!

### 2025-05-10 MD simulation/QTY-cut/Delete_atom_gro_large.py

@@ -1,87 +1,0 @@
-import re
-
-def delete_atom_and_update_indices(file_path, write_path, target_delete_atoms, target_delete_residues):
-    with open(file_path, "r") as file:
-        lines = file.readlines()
-    updated_lines = []
-    num_deleted = 0
-    num_res_deleted = 0
-    res_deleted = []
-    reached100000 = False
-
-    for line in lines:
-        line_splitted = line.split()
-        if len(line_splitted) == 5:
-            line_splitted = line_splitted[:1] + [line_splitted[1][:-5], line_splitted[1][-5:]] + line_splitted[2:]
-        elif len(line_splitted) != 6:
-            updated_lines.append(line)
-            continue
-        atom_index = int(line_splitted[2])
-        line_0 = line_splitted[0]
-        res_index = int(line_0[:-3])
-        res_index -= num_res_deleted
-        res_name = line_0[-3:]
-        if reached100000:
-           atom_index += 100000 
-        if atom_index == 99999:
-            reached100000 = True
-        if atom_index in target_delete_atoms and num_deleted < len(target_delete_atoms):
-            num_deleted += 1
-            if res_index in target_delete_residues and res_index not in res_deleted:
-                num_res_deleted += 1
-                res_deleted.append(res_index)
-            continue
-        new_line_splitted = [str(res_index), res_name, line_splitted[1], str((atom_index - num_deleted) % 100000)] + line_splitted[3:]
-        formatted_line = ""
-        formatted_line = "{:>5}{:>3}{:>7}{:>5}{:>8}{:>8}{:>8}\n".format(*new_line_splitted)
-        updated_lines.append(formatted_line)
-
-    with open(write_path, "w") as file:
-        file.writelines(updated_lines)
-
-file_path = "trans_em_again.gro"
-write_path = "trans_em_again_delwater.gro"
-target_delete_atoms = [
-    5066,   5067,   5068, 
-    7994,   7995,   7996, 
-    8051,   8052,   8053, 
-    39665,  39666,  39667, 
-    62339,  62340,  62341, 
-    62549,  62550,  62551, 
-    67952,  67953,  67954, 
-    78410,  78411,  78412, 
-    86198,  86199,  86200, 
-    93791,  93792,  93793, 
-    94406,  94407,  94408, 
-    96140,  96141,  96142, 
-    104750, 104751, 104752, 
[…]

### 2025-05-10 MD simulation/QTY-cut/Delete_atom_top.py

@@ -1,76 +1,0 @@
-import re
-
-def delete_atom_and_update_indices(file_path, write_path, atom_index):
-    with open(file_path, "r") as file:
-        lines = file.readlines()
-
-    atom_index = int(atom_index)
-    atom_section = 0
-    current_section = ""
-    sections_to_update = ["[ pairs ]", "[ bonds ]", "[ angles ]", "[ dihedrals ]", "[ cmap ]"]
-    section_to_format = {
-        "[ pairs ]": "{:>5}{:>6}{:>6}",
-        "[ bonds ]": "{:>5}{:>6}{:>6}",
-        "[ angles ]": "{:>5}{:>6}{:>6}{:>6}",
-        "[ dihedrals ]": "{:>5}{:>6}{:>6}{:>6}{:>6}",
-        "[ cmap ]": "{:>5}{:>6}{:>6}{:>6}{:>6}{:>6}"
-    }
-    updated_lines = []
-    atom_indices_to_delete = set()
-
-    for line in lines:
-        if line.strip().startswith("[ atoms ]"):
-            atom_section = 1
-        elif line.strip().startswith("["):
-            atom_section = -1
-
-        if atom_section == 0:
-            updated_lines.append(line)
-            continue
-        elif atom_section == 1:
-            updated_lines.append(line)
-            atom_section = 2
-        elif atom_section == 2:
-            if line.strip() and not line.strip().startswith(";"):
-                parts = line.split()
-                if int(parts[0]) == atom_index:
-                    atom_indices_to_delete.add(atom_index)
-                    continue
-                elif int(parts[0]) > atom_index:
-                    parts[0] = str(int(parts[0]) - 1)
-                formatted_line = "{:>7}{:>11}{:>7}{:>7}{:>7}{:>7}{:>11}{:>11}".format(*parts)
-                updated_lines.append(formatted_line + "\n")
-            else:
-                updated_lines.append(line)
-        elif atom_section == -1:
-            updated_lines.append(line)
-            if any(line.strip().startswith(section) for section in sections_to_update):
-                atom_section = -2
-                current_section = line.strip()
-            else:
-                atom_section = -3
-        elif atom_section == -2:
-            if line.strip() and not line.strip().startswith(";")  and not line.strip().startswith("#"):
-                parts = line.split()
-                if any(int(index) in atom_indices_to_delete for index in parts[:-1]):
-                    continue
[…]

### 2025-05-10 MD simulation/QTY-cut/set_dihedral.py

@@ -1,61 +1,0 @@
-from math import *
-
-def rotate(point, axis, ref_point, angle):
-    rel_point = [point[i] - ref_point[i] for i in range(3)]
-    rel_new_point = [0, 0, 0]
-    angle_rad = angle *pi / 180
-    axis_normalized = [axis[i] / sqrt(sum([axis[j]**2 for j in range(3)])) for i in range(3)]
-    dot = sum([rel_point[i] * axis_normalized[i] for i in range(3)])
-    cross = [rel_point[(i+1)%3]*axis_normalized[(i+2)%3] - rel_point[(i+2)%3]*axis_normalized[(i+1)%3] for i in range(3)]
-    parallel = [axis_normalized[i] * dot for i in range(3)]
-    perpendicular = [rel_point[i] - parallel[i] for i in range(3)]
-    rotated_perpendicular = [perpendicular[i] * cos(angle_rad) + cross[i] * sin(angle_rad) for i in range(3)]
-    rel_new_point = [parallel[i] + rotated_perpendicular[i] for i in range(3)]
-    new_point = [rel_new_point[i] + ref_point[i] for i in range(3)]
-    return new_point
-
-def measure_dihedral(a, b, c, d):
-    ab = [a[i] - b[i] for i in range(3)]
-    bc = [b[i] - c[i] for i in range(3)]
-    cd = [c[i] - d[i] for i in range(3)]
-    ab_cross_bc = [ab[1]*bc[2] - ab[2]*bc[1], ab[2]*bc[0] - ab[0]*bc[2], ab[0]*bc[1] - ab[1]*bc[0]]
-    bc_cross_cd = [bc[1]*cd[2] - bc[2]*cd[1], bc[2]*cd[0] - bc[0]*cd[2], bc[0]*cd[1] - bc[1]*cd[0]]
-    ab_cross_bc_length = sqrt(sum([x**2 for x in ab_cross_bc]))
-    bc_cross_cd_length = sqrt(sum([x**2 for x in bc_cross_cd]))
-    cos_angle = sum([ab_cross_bc[i]*bc_cross_cd[i] for i in range(3)]) / (ab_cross_bc_length * bc_cross_cd_length)
-    dihedral = acos(cos_angle) * 180 / pi
-    return dihedral
-
-with open("coordinates_to_rotate.txt", "r") as file:
-    lines = file.readlines()
-
-# axis is b-c
-# pivot is c
-# dihedral is a-b-c-d
-# delete the first column of resi/resn in .gro file
[…]

### 2025-05-10 MD simulation/WT/set_dihedral.py

@@ -1,61 +1,0 @@
-from math import *
-
-def rotate(point, axis, ref_point, angle):
-    rel_point = [point[i] - ref_point[i] for i in range(3)]
-    rel_new_point = [0, 0, 0]
-    angle_rad = angle *pi / 180
-    axis_normalized = [axis[i] / sqrt(sum([axis[j]**2 for j in range(3)])) for i in range(3)]
-    dot = sum([rel_point[i] * axis_normalized[i] for i in range(3)])
-    cross = [rel_point[(i+1)%3]*axis_normalized[(i+2)%3] - rel_point[(i+2)%3]*axis_normalized[(i+1)%3] for i in range(3)]
-    parallel = [axis_normalized[i] * dot for i in range(3)]
-    perpendicular = [rel_point[i] - parallel[i] for i in range(3)]
-    rotated_perpendicular = [perpendicular[i] * cos(angle_rad) + cross[i] * sin(angle_rad) for i in range(3)]
-    rel_new_point = [parallel[i] + rotated_perpendicular[i] for i in range(3)]
-    new_point = [rel_new_point[i] + ref_point[i] for i in range(3)]
-    return new_point
-
-def measure_dihedral(a, b, c, d):
-    ab = [a[i] - b[i] for i in range(3)]
-    bc = [b[i] - c[i] for i in range(3)]
-    cd = [c[i] - d[i] for i in range(3)]
-    ab_cross_bc = [ab[1]*bc[2] - ab[2]*bc[1], ab[2]*bc[0] - ab[0]*bc[2], ab[0]*bc[1] - ab[1]*bc[0]]
-    bc_cross_cd = [bc[1]*cd[2] - bc[2]*cd[1], bc[2]*cd[0] - bc[0]*cd[2], bc[0]*cd[1] - bc[1]*cd[0]]
-    ab_cross_bc_length = sqrt(sum([x**2 for x in ab_cross_bc]))
-    bc_cross_cd_length = sqrt(sum([x**2 for x in bc_cross_cd]))
-    cos_angle = sum([ab_cross_bc[i]*bc_cross_cd[i] for i in range(3)]) / (ab_cross_bc_length * bc_cross_cd_length)
-    dihedral = acos(cos_angle) * 180 / pi
-    return dihedral
-
-with open("coordinates_to_rotate_new.txt", "r") as file:
-    lines = file.readlines()
-
-# axis is b-c
-# pivot is c
-# dihedral is a-b-c-d
-# delete the first column of resi/resn in .gro file
[…]

### 2025-05-10 Paper/Source/manuscript.tex
Finalize first draft (except figure)

@@
 Data for retinal were obtained from NAMD Wiki (\url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalTop} for topology and \url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalPar} for parameters) and manually integrated into the protein file.
-Initial structures, configuration files, and command-line codes for the simulations are publicly available at...
-[ONLINE DATABASE TO BE PREPARED].
+Initial structures, configuration files, and command-line codes for the simulations are publicly available on Zenodo (\url{https://doi.org/10.5281/zenodo.15377505}).
 
@@
 
-Describe and discuss Figure~\ref{fig:hydrophobicity} (surface hydrophobicity).
-
 As transmembrane proteins, retinylidene proteins require detergents to be separated from the lipid bilayer.
@@
 
-The hydrophobic portions of the protein surface are represented in yellow (Figure 5).
+The hydrophobic portions of the protein surface are represented in yellow (Figure~\ref{fig:hydrophobicity}).
 In the native proteins, there are large hydrophobic patches in the transmembrane domains, which are embedded within the lipid bilayer.
@@
 
-\section*{Supplementary Material}
-
-The supplementary material can be found at... [TO BE ADDED]
-
 \section*{Data Availability Statement}
 
-The data for... can be found at... [ONLINE DATABASE TO BE PREPARED]
+The data for the AlphaFold3-predicted structures and MD simulation setting files and commands can be found on Zenodo (\url{https://doi.org/10.5281/zenodo.15377505}).
 
@@
 There is no financial support for this digital bioinformatics study. We only used free tools that are publicly available.
-
-\section*{Acknowledgments}
-
-Thanks to... for... [TO BE ADDED]
 
@@
 } \textbf{a)} and \textbf{b)}: 1ns running averages of the root mean square distances (RMSD) of the protein-retinal complex, transmembrane helix 6 (TM6), the retinal-binding pocket, and retinal.
+By convention, the isomerization is set at time 0ns, which is indicated by a brown, vertical dashed line.
 \textbf{c)}: superpositions between cis-state OPN2, trans-state OPN2, cis-state OPN2$^{\textrm{QTY}}$, and trans-state OPN2$^{\textrm{QTY}}$.
@@
 	\includegraphics[width=\linewidth]{Figures/function-binding.jpg}
+\end{figure}
+
+\begin{figure}[htbp]
 	\caption{\textbf{Changes in the retinal-binding pocket and protein-ligand interaction in native OPN2 and its QTY analog before and after 11-cis to all-trans isomerization of the chromophore.
@@
 \textbf{g)} and \textbf{h)}: the number of hydrogen bonds formed between residues in the binding pocket, and the number of water molecules within the binding pocket.
+By convention, the isomerization is set at time 0ns, which is indicated by a brown, vertical dashed line.
 }

### 2025-05-10 Paper/Source/supp.tex
Write results and discussion
Finalize first draft (except figure)

@@
 \begin{figure}[H]
-    \label{tb:sequence}
     \caption{\textbf{The enlarge protein sequence alignments of 12 retinylidene proteins with their water-soluble QTY analogs from Figure 1.} The symbols $|$ and $*$ indicate that amino acids are identical and different respectively.
@@
     The alignments are: 
-    \textbf{a)} OPN1MW vs. OPN1MW$^{\textrm{QTY}}$, 
-    \textbf{b)} OPN1LW vs. OPN1LW$^{\textrm{QTY}}$, 
-    \textbf{c)} OPN1SW vs. OPN1SW$^{\textrm{QTY}}$, 
-    \textbf{d)} OPN2 vs. OPN2$^{\textrm{QTY}}$, 
-    \textbf{e)} OPN3 vs. OPN3$^{\textrm{QTY}}$, 
-    \textbf{f)} OPN4 vs. OPN4$^{\textrm{QTY}}$, 
-    \textbf{g)} OPN5 vs. OPN5$^{\textrm{QTY}}$, 
-    \textbf{h)} RGR vs. RGR$^{\textrm{QTY}}$, 
-    \textbf{i)} RRH vs. RRH$^{\textrm{QTY}}$, 
-    \textbf{j)} BACR vs. BACR$^{\textrm{QTY}}$, 
-    \textbf{k)} BACH vs. BACH$^{\textrm{QTY}}$, 
-    \textbf{l)} ChR2 vs. ChR2$^{\textrm{QTY}}$. }
-    \textbf{a)} OPN1MW vs. OPN1MW$^{\textrm{QTY}}$ \\
+    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
+    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
+    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
+    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$, 
+    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$, 
+    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$, 
+    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$, 
+    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$, 
+    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$, 
+    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$, 
+    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$, 
+    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$. }
+    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/opn1mw.jpg}
@@
 \begin{figure}[H]
-    \textbf{b)} OPN1LW vs. OPN1LW$^{\textrm{QTY}}$ \\
+    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/opn1lw.jpg}
@@
 \begin{figure}[H]
-    \textbf{c)} OPN1SW vs. OPN1SW$^{\textrm{QTY}}$ \\
+    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/opn1sw.jpg}
@@
 \begin{figure}[H]
-    \textbf{d)} OPN2 vs. OPN2$^{\textrm{QTY}}$ \\
+    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/opn2.jpg}
@@
 \begin{figure}[H]
-    \textbf{e)} OPN3 vs. OPN3$^{\textrm{QTY}}$ \\
+    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/opn3.jpg}
@@
 \begin{figure}[H]
-    \textbf{f)} OPN4 vs. OPN4$^{\textrm{QTY}}$ \\
+    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/opn4.jpg}
@@
 \begin{figure}[H]
-    \textbf{g)} OPN5 vs. OPN5$^{\textrm{QTY}}$ \\
+    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/opn5.jpg}
@@
 \begin{figure}[H]
-    \textbf{h)} RGR vs. RGR$^{\textrm{QTY}}$ \\
+    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/rgr.jpg}
@@
 \begin{figure}[H]
-    \textbf{i)} RRH vs. RRH$^{\textrm{QTY}}$ \\
+    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/rrh.jpg}
@@
 \begin{figure}[H]
-    \textbf{j)} BACR vs. BACR$^{\textrm{QTY}}$ \\
+    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/bacr.jpg}
@@
 \begin{figure}[H]
-    \textbf{k)} BACH vs. BACH$^{\textrm{QTY}}$ \\
+    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/bach.jpg}
@@
 \begin{figure}[H]
-    \textbf{l)} ChR2 vs. ChR2$^{\textrm{QTY}}$ \\
+    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$ \\
     \includegraphics[width=\linewidth]{SuppFigures/chr2.jpg}
@@
 \begin{figure}[H]
-    \label{tb:af3}
     \caption{\textbf{AlphaFold3 prediction accuracy: plDDT, PAE, ipTM, and pTM scores.} \\
@@
 
+\begin{figure}[H]
+    \caption{\textbf{The radius of gyration of native and QTY-designed OPN2.
+} By convention, the isomerization is set at time 0ns, which is indicated by a brown, vertical dashed line.
+The radius of gyration and its 1-ns running average are shown, respectively, as black and red lines.
+}
+    \textbf{a)} Native OPN2 \\ \\
+    \includegraphics[width=\linewidth]{SuppFigures/wt gyrate.jpg}
+    \textbf{b)} QTY-designed OPN2 \\ \\
+    \includegraphics[width=\linewidth]{SuppFigures/qty gyrate.jpg}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{\textbf{The root mean square (RMS) fluctuation of native and QTY-designed OPN2.
+} Blue bars represent proteins with 11-cis-retinal and yellow bars represent proteins with all-trans-retinal.
+The two states are plotted on the same set of axis, with the shorter bars placed on top of the taller bars.
+}
+    \textbf{a)} Native OPN2 \\ \\
+    \includegraphics[width=\linewidth]{SuppFigures/wt rmsf.jpg}
+    \textbf{b)} QTY-designed OPN2 \\ \\
+    \includegraphics[width=\linewidth]{SuppFigures/qty rmsf.jpg}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{\textbf{The root mean square distance (RMSD) of each residue in the retinal-binding pocket of native and QTY-designed OPN2.
+} By convention, the isomerization is set at time 0ns, which is indicated by a brown, vertical dashed line.
+Only the 1-ns running average of RMSD are shown for clarity.
+}
+    \textbf{a)} Native OPN2 \\ \\
+    \includegraphics[width=\linewidth]{SuppFigures/wt rmsd byres.jpg}
+    \textbf{b)} QTY-designed OPN2 \\ \\
+    \includegraphics[width=\linewidth]{SuppFigures/qty rmsd byres.jpg}
+
+    \vspace{0.5cm}
+    \includegraphics[width=\linewidth]{SuppFigures/legend rmsd byres.jpg}
+\end{figure}
+
 \end{document}

### 2025-05-10 MD/Analysis/plot_rmsd_byres.py

@@ -15,22 +15,26 @@ def plot_running_avg(x, y, c="red", labelname="", window=1):
     window_size = window * 500
     running_avg = np.convolve(y, np.ones(window_size) / window_size, mode="valid")
     x_avg = x[len(x) - len(running_avg) : ]
-    plt.plot(x_avg, running_avg, label=labelname, color=c)
+    plt.plot(x_avg, running_avg, label=labelname, color=c, linewidth=0.75)
 
 matplotlib.rcParams['font.family'] = 'Calibri'
 targetname = "rmsd"
 subtargetids = [296, 265, 113, 181, 268, 207, 186, 191, 187, 188, 189, 117, 292, 212, 295, 208]
+reslabels = {
+    "qty": ["296K", "265W", "113E", "181E", "268Y", "207M", "186S", "191Y", "187C", "188G", "189I", "117A", "292A", "212Y", "295A", "208Y"], 
+    "wt" : ["296K", "265W", "113E", "181E", "268Y", "207M", "186S", "191Y", "187C", "188G", "189I", "117A", "292A", "212F", "295A", "208F"]
+}
 subtargetnames = [int(subtargetid) for subtargetid in subtargetids]
 cmap = plt.cm.get_cmap("tab20", 16)
 colors = [cmap(i) for i in range(16)]
 for protein in ["qty", "wt"]:
-    plt.figure(figsize=(8, 5))
+    plt.figure(figsize=(8, 4))
     plt.xlabel("Time (ns)")
     plt.ylabel("RMSD (nm)")
     plt.title("")
     plt.xlim(-10, 120)
     plt.xticks(np.arange(-10, 121, 10))
-    plt.axvline(x=0, color='b', linestyle='--')
+    plt.axvline(x=0, color='brown', linestyle='--', linewidth=1)
     plt.grid(False)
     for i in range(len(subtargetnames)):
         cis_data = load_xvg(f"{protein}_cis_{targetname}_{subtargetnames[i]}.xvg", -10)
@@ -39,7 +43,7 @@ for protein in ["qty", "wt"]:
         x = data[:, 0]
         y = data[:, 1]
         #plt.plot(x, y, label=subtargetnames[i], color=colors[i][0], linewidth=0.5)
-        plot_running_avg(x, y, c=colors[i], labelname=subtargetnames[i], window=2)
-    plt.legend()
[…]

### 2025-05-11 Paper/Source/manuscript.tex
finalize first draft

@@
-\documentclass[fleqn, 10pt, lineno]{manuscript}
+\documentclass[fleqn, 10pt]{manuscript}
 %%\usepackage{setspace}
@@
 \author[1]{Siqi Pan}
-\author[2]{Shuguang Zhang}
 \affil[1]{Shanghai World Foreign Language Academy, 400 Baihua Street, Shanghai 200233, China}
-\affil[2]{Lab of Molecular Architecture, Media Lab, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, MA 02139, USA}
 
-\corrauthor[2]{Shuguang Zhang}{Shuguang@MIT.EDU}
+\corrauthor[1]{Siqi Pan}{siqipan2008@outlook.com}
 
@@
 
-Retinylidene proteins are a large family of retinal-binding light-sensitive proteins, found in many organisms ranging from microbes to human.
-Microbial opsins have been utilized in optogenetics, while animal opsins are essential for vision and other non-visual light-dependent metabolic functions.
-However, all retinylidene proteins are membrane proteins with hydrophobic transmembrane domains, which makes it challenging to study them.
-In this structural and functional bioinformatics study, we used the QTY (Glutamine, Threonine, Tyrosine) code to design water-soluble QTY analogs of retinylidene proteins, including 9 human opsins and 3 microbial opsins.
-We provide the superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water soluble QTY variants, and experimentally-determined structures when available.
-We also provide a comparison of the surface hydrophobicity of the variants.
-Furthermore, we run molecular dynamics (MD) simulations of native and QTY-designed OPN2 and analyze their response to the 11-cis to all-trans isomerization of the retinal chromophore.
+Retinylidene proteins are retinal-binding light-sensitive proteins found in organisms ranging from microbes to human.
+Microbial opsins have been utilized in optogenetics, while animal opsins are essential for vision and light-dependent metabolic functions.
+However, retinylidene proteins have hydrophobic transmembrane (TM) domains, which makes them challenging to study.
+In this structural and functional bioinformatics study, we used the QTY (Glutamine, Threonine, Tyrosine) code to design water-soluble QTY analogs of retinylidene proteins, including 9 human and 3 microbial opsins.
+We provide superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY analogs, and experimentally-determined structures when available.
+We also provide a comparison of surface hydrophobicity of the variants.
+Despite significant changes to the protein sequence (35.53\% to 50.24\% in the TM domain), protein characteristics and structures are well-preserved.
+Furthermore, we run molecular dynamics (MD) simulations of native and QTY-designed OPN2 (rhodopsin) and analyze their response to the isomerization of 11-cis-retinal to all-trans-retinal.
+The results show that the QTY analog has similar functional behavior to the native protein.
 The findings of this study indicate that the QTY code can be used as a robust tool to design water-solubility retinylidene proteins.
@@
 This justifies the replacement of hydrophobic amino acids with polar ones.
-We initially applied the QTY code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}.
-We have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.
-In addition to GPCR, we have also used the QTY code to design water-soluble glucose transporters \citep{Smorodina_2022}, ABC transporters \citep{Pan_2024}, monoamine neurotransmitter transporters \citep{Karagol_Karagol_Alper_2024}, glutamate transporters \citep{Karagol_Karagol_Smorodina_2024, Karagol_2024}, mitochondrial megacomplex \citep{Chen_2025}, antibodies \citep{Li_Wang_2024}, potassium channels \citep{Smorodina_2024}, receptor kinases \citep{Li_Tang_2024}, transmembrane enzymes \citep{Chen_Pan_2025}, as well as bacterial enzymes with beta barrel structures \citep{Sajeev-Sheeja_2023, Sajeev-Sheeja_2024}.
+Zhang et al.
+initially applied the QTY code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}.
+They have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.
+In addition to GPCR, they have also used the QTY code to design water-soluble glucose transporters \citep{Smorodina_2022}, ABC transporters \citep{Pan_2024}, monoamine neurotransmitter transporters \citep{Karagol_Karagol_Alper_2024}, glutamate transporters \citep{Karagol_Karagol_Smorodina_2024, Karagol_2024}, mitochondrial megacomplex \citep{Chen_2025}, antibodies \citep{Li_Wang_2024}, potassium channels \citep{Smorodina_2024}, receptor kinases \citep{Li_Tang_2024}, transmembrane enzymes \citep{Chen_Pan_2025}, as well as bacterial enzymes with beta barrel structures \citep{Sajeev-Sheeja_2023, Sajeev-Sheeja_2024}.
 The QTY-designed water-soluble CXCR4 chemokine receptor has been successfully used in biomimetic sensors \citep{Qing_2023}.
-We have also applied the rQTY (reverse QTY) code to design self-assembled nanoparticles \citep{Meng_2023}.
+They have also applied the rQTY (reverse QTY) code to design self-assembled nanoparticles \citep{Meng_2023}.
 
@@
 The retinal molecule was then manually switched to the all-trans state by rotating C13 to C15 and bonded hydrogen and methyl groups by 180 degrees around the C11-C12 bond.
+This mimics the effect of the absorption of a photon by 11-cis-retinal.
 Energy minimization and equilibration were repeated exactly as before, and then a 120-ns production MD simulation was run.
@@
 For OPN2, which has an available X-ray diffraction structure, we also superposed the experimentally determined structure with the AlphaFold3-predicted structures.
-Overall, the root mean square distances (RMSD) are small, from 0.307\AA to 0.611\AA, with only one exception of OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$ (RMSD = 0.999\AA).
+Overall, the root mean square distances (RMSD) are small, from 0.307{\AA} to 0.611\AA, with only one exception of OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$ (RMSD = 0.999\AA).
 This shows that the water-soluble QTY analogs are quite similar to native proteins in terms of structure.
@@
 
-We observe that QTY substitutions do not introduce changes to the essential NPxxY motif or the retinal-binding lysine of human retinylidene proteins.
+QTY substitutions do not introduce changes to the essential NPxxY motif or the retinal-binding lysine of human retinylidene proteins.
 Therefore, we propose that QTY analogs of human opsins may have conserved functions and carry out a molecular dynamics (MD) simulation.
@@
 
-Zooming in on the retinal-binding pocket, we observe that retinal is held within its binding pocket by several forces: the counterions of the retinal Schiff base (RSB) (113E and 181E), the hydrophobic interactions with neighboring residues (for example, 265W, 268Y, and the 187--189 beta strand), and, sometimes, steric collisions (Figure~\ref{fig:binding}).
+Zooming in on the retinal-binding pocket, we observe that retinal is held within its binding pocket by several forces in both the native and QTY analog: the counterions of the retinal Schiff base (RSB) (113E and 181E), the hydrophobic interactions with neighboring residues (for example, 265W, 268Y, and the 187--189 beta strand), and, sometimes, steric collisions (Figure~\ref{fig:binding}).
 Since retinal is a ligand that binds in an internal pocket, we were unable to calculate the Gibbs free energy of its binding.
-Nevertheless, the distribution of interaction energies are found to be roughly the same in both native OPN2 and the water-soluble QTY analog, which is a strong suggestion of functional conservation.
+Nevertheless, the distribution of interaction energies are found to be similar in native OPN2 and the water-soluble QTY analog, except for small differences: native OPN2 experiences a change in interaction energy at about $t=50$ns due to the entrance of water near 113E; the QTY analog has more negative interaction energy at residues 208 and 212 due to phenylalanine (F) to tyrosine (Y) substitutions.
+Besides from these, the similarity is a strong suggestion of functional conservation.
 Finally, we observe very different hydrogen bonding and water molecule patterns inside the binding pocket, which is mainly due to several F to Y substitutions in that region.
@@
 
+\section*{Supplementary Information}
+
+The Supplementary Information is available at...
+
 \section*{Data Availability Statement}
@@
 
-Conceptualization: S.P., S.Z.; Formal analysis: S.P.; Investigation: Methodology: S.P.; Validation: S.P.; Data curation: S.P.; Writing—original draft preparation: S.P., S.Z.; Review and editing: S.P., S.Z.
+Conceptualization: S.P.; Formal analysis: S.P.; Investigation: Methodology: S.P.; Validation: S.P.; Data curation: S.P.; Writing—original draft preparation: S.P.; Review and editing: S.P.
+
+\section*{Acknowledgements}
+
+S.P.
+thanks Prof.
+Shuguang Zhang of the Lab of Molecular Architecture, Media Lab, Massachusetts Institute of Technology for inspiring the topic of this study as well as providing valuable advice on research methods and manuscript preparation.
 
@@
 	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
-        \vspace{-0.5cm}
 	\caption{\textbf{The protein sequence alignments of 12 retinylidene proteins and their QTY analogs.
 } Blue: human opsins; purple: microbial opsins.
-The symbols $|$ and $*$ indicate that amino acids are identical and different respectively.
-Amino acids L, V, I and F in TM (transmembrane) alpha helices are replaced with Q, T, Y and Y respectively.
-The alpha helices (blue) are shown above the protein sequences.
+The symbols $|$ and $*$ indicate that amino acids are identical or different, respectively.
+Amino acids L, I/V, and F in TM (transmembrane) alpha helices (shown in blue above the sequences) are replaced with Q, T, and Y respectively.
+The variation in the TM domain ranges from 35.53\% to 50.24\% while the overall variation rate ranges from 15.48\% to 30.04\%.
 The characteristics of the proteins are shown above the sequences.
-    The alignments are: 
+Despite large variation rates, the pI only experiences a slight change between 0.00 and 0.16 and the MW increases slightly by a value between 0.04kDa and 0.60kDa.
+The enlarged individual sequence alignments are available in Supplementary Information.
+    The alignments are 
     \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
@@
 } For clarity, unstructured N- and C- terminal ends are deleted.
-    For \textbf{a)} to \textbf{i)}, green: AlphaFold3-predicted native structure; cyan: AlphaFold3-predicted QTY analog structure; magenta: experimentally determined structure. The superpositions are 
+    For \textbf{a)} to \textbf{i)}, despite significant changes in the protein sequence, the structures superpose very well.
+The root mean square distance (RMSD) values are quite small, from 0.307{\AA} to 0.611\AA, with only one exception (OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$, RMSD = 0.999\AA).
+Green: AlphaFold3-predicted native structure; cyan: AlphaFold3-predicted QTY analog structure; magenta: experimentally determined structure.
+The superpositions are
     \textbf{a)} OPN1MW$^{\textrm{AF3}}$ \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
@@
     \textbf{i)} RRH$^{\textrm{AF3}}$ \textit{vs} RRH$^{\textrm{QTY}}$. 
-    For \textbf{j)} and \textbf{k)}, green: OPN1MW; red: OPN1LW; blue: OPN1SW; purple: OPN2; cyan: OPN3; gray: OPN4; olive: OPN5; orange: RGR; pink: RRH. The superpositions are
+    For \textbf{j)} and \textbf{k)}, there is a large degree of similarity between the RMSD between a pair of native proteins and that between the corresponding pair of QTY analogs.
+Green: OPN1MW; red: OPN1LW; blue: OPN1SW; purple: OPN2; cyan: OPN3; gray: OPN4; olive: OPN5; orange: RGR; pink: RRH.
+The superpositions are
     \textbf{j)} OPN1MW$^{\textrm{AF3}}$ \textit{vs} OPN1LW$^{\textrm{AF3}}$ \textit{vs} OPN1SW$^{\textrm{AF3}}$ \textit{vs} OPN2$^{\textrm{AF3}}$ \textit{vs} OPN3$^{\textrm{AF3}}$ \textit{vs} OPN4$^{\textrm{AF3}}$ \textit{vs} OPN5$^{\textrm{AF3}}$ \textit{vs} RGR$^{\textrm{AF3}}$ \textit{vs} RRH$^{\textrm{AF3}}$,
@@
 	\caption{\textbf{Superposition of AlphaFold3-predicted native microbial retinylidene proteins, their QTY analogs, and experimentally determined structures.
-} For clarity, unstructured N- and C- terminal ends are deleted.
-    Green: AlphaFold3-predicted native structure; cyan: AlphaFold3-predicted QTY analog structure; magenta: experimentally determined structure. The superpositions are 
+} Despite significant changes in the protein sequence, the structures superpose very well.
+The root mean square distance (RMSD) values are quite small, with the highest being 0.685\AA.
+For clarity, unstructured N- and C- terminal ends are deleted.
+    Green: AlphaFold3-predicted native structure; cyan: AlphaFold3-predicted QTY analog structure; magenta: experimentally determined structure. 
+    The superpositions are 
     \textbf{a)} BACR$^{\textrm{AF3}}$ \textit{vs} BACR$^{\textrm{QTY}}$ \textit{vs} BACR$^{\textrm{EXP}}$ monomer, 
@@
 	\caption{\textbf{Hydrophobic surface of 12 retinylidene proteins and their water-soluble QTY analogs.
-} The native proteins have many hydrophobic (yellow) patches due to the presence of hydrophobic amino acids, including L, I, V, and F.
-After QTY substitution, hydrophilic Q, T, and Y have respectively replaced hydrophobic L, I/V, and F, and the hydrophobic patches in the surface of transmembrane helices have become more hydrophilic (cyan).
+} Hydrophobic patches are shown in yellow while hydrophilic patches are shown in cyan.
+The native proteins have many hydrophobic patches due to the presence of hydrophobic amino acids, including L, I, V, and F.
+After QTY substitution, hydrophilic Q, T, and Y have respectively replaced hydrophobic L, I/V, and F, and the hydrophobic patches in the surface of transmembrane helices have become more hydrophilic.
+In addition, the surface shape of the native and QTY analogs are very similar.
 For clarity, unstructured N- and C- terminal ends are deleted.
+    The comparisons are 
     \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
@@
 \textbf{c)}: superpositions between cis-state OPN2, trans-state OPN2, cis-state OPN2$^{\textrm{QTY}}$, and trans-state OPN2$^{\textrm{QTY}}$.
+Both OPN2 and OPN2$^{\textrm{QTY}}$ exhibit conformational changes, with RMSDs greater than 2\AA.
 Blue: cis-state protein, orange: 11-cis-retinal; yellow: trans-state protein, greenish cyan: all-trans retinal.
@@
 } \textbf{a)} and \textbf{b)}: close-ups of the binding pocket in cis-state.
-Blue: protein residues, orange: 11-cis-retinal; dashed lines: same as a) and b).
+Protein-ligand interactions with lengths shorter or equal to 3.5\AA are shown in the figure.
+Blue: protein residues, orange: 11-cis-retinal; green dashed lines: ion bridge; yellow dashed lines: van der Waals and/or hydrophobic interactions.
 \textbf{c)} and \textbf{d)}: close-ups of the binding pocket in trans-state.
+Protein-ligand interactions with lengths shorter or equal to 3.5\AA are shown in the figure.
 Yellow: protein residues, greenish cyan: all-trans-retinal; green dashed lines: ion bridge; yellow dashed lines: van der Waals and/or hydrophobic interactions.
-\textbf{e)} and \textbf{f)}: the interaction energies between the protein, the binding pocket, individual residues, and retinal.
-The interaction energy is the sum of the short-range Coulombic interaction energy and short-range Lennard-Jones energy.
-Please note that the interaction energy is a product of MD simulation and is not necessarily a meaningful physical quantity.
+\textbf{e)} and \textbf{f)}: the interaction energies (IE) between the protein, the binding pocket, individual residues, and retinal.
+IE is the sum of the short-range Coulombic interaction energy and short-range Lennard-Jones energy.
+Please note that IE is a product of MD simulation and is not necessarily a ``real'' physical quantity.
+For clarity, IE is rescaled using the signed pseudo logarithm ($y = \textrm{sign}(x)\cdot\ln(|x|+1)$).
+By convention, the isomerization is set at time 0ns, which is indicated by a brown, vertical dashed line.
+The large changes in IE in OPN2 around $t=50$ns are due to the entrance of water molecules into the binding pocket, near 113E.
+The QTY analog has more negative IE at residues 208 and 212 due to F to Y substitutions.
+Besides from these, the similarity between the IE of OPN2 and OPN2$^{\textrm{QTY}}$ is a strong suggestion of functional conservation.
 \textbf{g)} and \textbf{h)}: the number of hydrogen bonds formed between residues in the binding pocket, and the number of water molecules within the binding pocket.

### 2025-05-11 Paper/Source/supp.tex
finalize first draft

@@
 
-\subsection*{Siqi Pan and Shuguang Zhang}
+\subsection*{Siqi Pan}
 
 \begin{figure}[H]
-    \caption{\textbf{The enlarge protein sequence alignments of 12 retinylidene proteins with their water-soluble QTY analogs from Figure 1.} The symbols $|$ and $*$ indicate that amino acids are identical and different respectively.
-Amino acids L, V, I and F in TM (transmembrane) alpha helices are replaced with Q, T, Y and Y respectively.
-The alpha helices (blue) are shown above the protein sequences.
-\\
-    The alignments are: 
+    \caption{\textbf{The enlarged protein sequence alignments of 12 retinylidene proteins and their QTY analogs from Figure 1.
+} The symbols $|$ and $*$ indicate that amino acids are identical or different, respectively.
+Amino acids L, I/V, and F in TM (transmembrane) alpha helices (shown in blue above the sequences) are replaced with Q, T, and Y respectively.
+The variation in the TM domain ranges from 35.53\% to 50.24\% while the overall variation rate ranges from 15.48\% to 30.04\%.
+    The alignments are 
     \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
@@
 \begin{figure}[H]
-    \textbf{j)} BACR$^{\textrm{QTY}}$ \\
+    \textbf{j)} BACR$^{\textrm{QTY}}$ monomer \\
     \includegraphics[width=\linewidth]{SuppFigures/af3 bacr qty mono.jpg}
@@
 \begin{figure}[H]
-    \textbf{k)} BACH$^{\textrm{QTY}}$ \\
+    \textbf{k)} BACH$^{\textrm{QTY}}$ monomer \\
     \includegraphics[width=\linewidth]{SuppFigures/af3 bach qty mono.jpg}
@@
 \begin{figure}[H]
-    \textbf{l)} ChR2$^{\textrm{QTY}}$ \\
+    \textbf{l)} ChR2$^{\textrm{QTY}}$ monomer \\
     \includegraphics[width=\linewidth]{SuppFigures/af3 chr2 qty mono.jpg}
@@
 \begin{figure}[H]
-    \textbf{m)} BACR$^{\textrm{QTY}}$ \\
+    \textbf{m)} BACR$^{\textrm{QTY}}$ trimer \\
     \includegraphics[width=\linewidth]{SuppFigures/af3 bacr qty tri.jpg}
@@
 \begin{figure}[H]
-    \textbf{n)} BACH$^{\textrm{QTY}}$ \\
+    \textbf{n)} BACH$^{\textrm{QTY}}$ trimer \\
     \includegraphics[width=\linewidth]{SuppFigures/af3 bach qty tri.jpg}
@@
 \begin{figure}[H]
-    \textbf{o)} ChR2$^{\textrm{QTY}}$ \\
+    \textbf{o)} ChR2$^{\textrm{QTY}}$ dimer \\
     \includegraphics[width=\linewidth]{SuppFigures/af3 chr2 qty di.jpg}

### 2025-05-11 MD/Analysis/plot_ie.py
Finalize IE graph

@@ -27,22 +27,23 @@ targetname = "ie"
 resids = [265, 113, 181, 268, 207, 186, 191, 187, 188, 189, 117, 292, 212, 295, 208]
 resnames = [int(resid) for resid in resids]
 groups = ["prot", "pocket"]
+data = {"qty": 0, "wt": 0}
 for protein in ["qty", "wt"]:
     data_temp = []
     for group in groups:
         cis_data = load_xvg_ie(f"{protein}_cis_{targetname}_{group}.xvg", byres=False)
-        data_temp.append(cis_data)
-        #trans_data = load_xvg_ie(f"{protein}_trans_{targetname}_{group}.xvg"， byres=False)
-        #data_temp.append(np.concatenate((cis_data, trans_data), axis=0))
+        trans_data = load_xvg_ie(f"{protein}_trans_{targetname}_{group}.xvg", byres=False)
+        data_temp.append(np.concatenate((cis_data, trans_data), axis=1))
     cis_data = load_xvg_ie(f"{protein}_cis_{targetname}_byres.xvg", byres=True)
-    data_temp.append(cis_data)
-    #trans_data = load_xvg_ie(f"{protein}_trans_{targetname}_byres.xvg", byres=True)
-    #data_temp.append(np.concatenate((cis_data, trans_data), axis=0))
-    data = np.concatenate(data_temp, axis=0)
-    
+    trans_data = load_xvg_ie(f"{protein}_trans_{targetname}_byres.xvg", byres=True)
+    data_temp.append(np.concatenate((cis_data, trans_data), axis=1))
+    data[protein] = np.concatenate(data_temp, axis=0)
+    data[protein] = np.sign(data[protein]) * np.log1p(np.abs(data[protein]))
+
+vmax = max(np.max(np.abs(data["qty"])), np.max(np.abs(data["wt"])))
+for protein in ["qty", "wt"]:
     fig, ax = plt.subplots(figsize=(4.5, 4))
-    vmax = np.max(np.abs(data))
-    cax = ax.imshow(data, aspect="auto", cmap="RdBu_r", vmin=-vmax, vmax=vmax, origin="lower", interpolation="nearest")
+    cax = ax.imshow(data[protein], aspect="auto", cmap="RdBu_r", vmin=-vmax, vmax=vmax, origin="lower", interpolation="nearest")
     ax.set_xlabel("Time (ns)")
     ax.set_ylabel("")
     ax.set_yticks(range(17))

### 2025-05-15 Paper/Manuscript/manuscript.tex
Reorganize paper latex files for QRB Discovery Submission.
Submit to QRB D.

--- 2025-05-11 Paper/Source/manuscript.tex
@@
 
-\keywords{hydrophobic to hydrophilic conversion; membrane proteins; protein design; QTY code; water-soluble retinylidene proteins; water-soluble opsins; activation of QTY variants of rhodopsin}
+\keywords{bioinformatics; computational studies on functional properties of biological molecule; GPCRs; membrane protein structure; protein dynamics simulation}
 \begin{abstract}
@@
 
-There is no financial support for this digital bioinformatics study. We only used free tools that are publicly available.
+There is no financial support for this digital bioinformatics study. I only used free tools that are publicly available.
 
@@
 
-Massachusetts Institute of Technology (MIT) filed several patent applications for the QTY code for GPCRs excluding the human opsins.
-OH2Laboratories licensed the technology from MIT to work on water-soluble GPCR variants.
-S.Z.
-is an inventor of the QTY code and has a minor equity in OH2Laboratories.
-S.Z.
-is a Scientific Advisor and has minor shares for a startup RealNose to develop a sensing device based on olfactory receptors.
-S.Z.
-founded a startup 511 Therapeutics to generate therapeutic monoclonal antibodies against solute carrier transporters to treat pancreatic cancer.
-S.Z.
-has majority equity in 511 Therapeutics.
-All other authors have no competing interests.
+Massachusetts Institute of Technology (MIT) filed several patent applications for the QTY code for GPCRs, which do not include the human opsins. There are no competing interests.
 

### 2025-05-16 Paper/Manuscript/manuscript.tex
Submit to QRB.

@@
 However, retinylidene proteins have hydrophobic transmembrane (TM) domains, which makes them challenging to study.
-In this structural and functional bioinformatics study, we used the QTY (Glutamine, Threonine, Tyrosine) code to design water-soluble QTY analogs of retinylidene proteins, including 9 human and 3 microbial opsins.
-We provide superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY analogs, and experimentally-determined structures when available.
-We also provide a comparison of surface hydrophobicity of the variants.
+In this structural and functional bioinformatics study, I used the QTY (Glutamine, Threonine, Tyrosine) code to design water-soluble QTY analogs of retinylidene proteins, including 9 human and 3 microbial opsins.
+I provide superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY analogs, and experimentally-determined structures when available.
+I also provide a comparison of surface hydrophobicity of the variants.
 Despite significant changes to the protein sequence (35.53\% to 50.24\% in the TM domain), protein characteristics and structures are well-preserved.
-Furthermore, we run molecular dynamics (MD) simulations of native and QTY-designed OPN2 (rhodopsin) and analyze their response to the isomerization of 11-cis-retinal to all-trans-retinal.
+Furthermore, I run molecular dynamics (MD) simulations of native and QTY-designed OPN2 (rhodopsin) and analyze their response to the isomerization of 11-cis-retinal to all-trans-retinal.
 The results show that the QTY analog has similar functional behavior to the native protein.
@@
 Retinylidene proteins are photochemically reactive proteins that are bound to or can bind to retinal (vitamin A aldehyde) as their chromophore \citep{Spudich_2000}.
-We will use the term ``opsin'' interchangeably with ``retinylidene protein'', despite the fact that ``opsin'' sometimes refers specifically to the chromophore-free apoprotein.
+I will use the term ``opsin'' interchangeably with ``retinylidene protein'', despite the fact that ``opsin'' sometimes refers specifically to the chromophore-free apoprotein.
 Retinylidene proteins are divided into two groups, animal opsins and microbial opsins, which are evolutionarily distinct but share common characteristics such as having 7 transmembrane (TM) domains and a retinal-binding lysine residue \citep{Yee_2013, Spudich_2000}.
-In this study, we will consider 9 animal opsins and 3 microbial opsins.
+In this study, I will consider 9 animal opsins and 3 microbial opsins.
 
@@
 
-In this study, we selected 9 opsins expressed in the human nervous system: OPN1MW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04001}), OPN1SW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P08100/entry}{P04001}), OPN3 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}).
+In this study, I selected 9 opsins expressed in the human nervous system: OPN1MW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04001}), OPN1SW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P08100/entry}{P04001}), OPN3 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}).
 They belong to several evolutionarily distinct families of animal opsins \citep{Terakita_2005}.
@@
 Many studies on the functional mechanisms of animal opsins also focus on OPN2.
-Consequently, we choose OPN2 to conduct a functional analysis in this study, in order to further explore the effectiveness of the QTY code in redesigning retinylidene proteins.
+Consequently, I choose OPN2 to conduct a functional analysis in this study, in order to further explore the effectiveness of the QTY code in redesigning retinylidene proteins.
 
@@
 
-In this study, we selected 3 microbial opsins: BACR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P02945/entry}{P02945}), BACH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/B0R2U4/entry}{B0R2U4}), ChR2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q8RUT8/entry}{Q8RUT8}).
+In this study, I selected 3 microbial opsins: BACR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P02945/entry}{P02945}), BACH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/B0R2U4/entry}{B0R2U4}), ChR2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q8RUT8/entry}{Q8RUT8}).
 
@@
 
-We have asked whether retinylidene proteins could be redesigned to be more soluble.
+I have asked whether retinylidene proteins could be redesigned to be more soluble.
 Retinylidene proteins are all integral membrane proteins with seven transmembrane alpha helices embedded in a lipid bilayer.
@@
 
-Instead of taking a computational approach, we applied the QTY (Glutamine, Threonine, Tyrosine) code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins.
+Instead of taking a computational approach, I applied the QTY (Glutamine, Threonine, Tyrosine) code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins.
 There are structural similarities between hydrophobic and polar amino acids: leucine (L) and glutamine (Q); isoleucine (I) / valine (V) and threonine (T); and phenylalanine (F) and tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}.
@@
 initially applied the QTY code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}.
-They have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.
+Zhang's team have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.
 In addition to GPCR, they have also used the QTY code to design water-soluble glucose transporters \citep{Smorodina_2022}, ABC transporters \citep{Pan_2024}, monoamine neurotransmitter transporters \citep{Karagol_Karagol_Alper_2024}, glutamate transporters \citep{Karagol_Karagol_Smorodina_2024, Karagol_2024}, mitochondrial megacomplex \citep{Chen_2025}, antibodies \citep{Li_Wang_2024}, potassium channels \citep{Smorodina_2024}, receptor kinases \citep{Li_Tang_2024}, transmembrane enzymes \citep{Chen_Pan_2025}, as well as bacterial enzymes with beta barrel structures \citep{Sajeev-Sheeja_2023, Sajeev-Sheeja_2024}.
@@
 
-In this paper, we apply the QTY code to redesign 9 human opsins and 3 microbial opsins.
-We provide the superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY variants, and experimentally-determined structures when available.
-We also provide a comparison of the surface hydrophobicity of the variants.
-Furthermore, we run MD simulations of native and QTY-designed OPN2 and analyze their response to the 11-cis to all-trans isomerization of the retinal chromophore.
+In this paper, I apply the QTY code to redesign 9 human opsins and 3 microbial opsins.
+I provide the superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY variants, and experimentally-determined structures when available.
+I also provide a comparison of the surface hydrophobicity of the variants.
+Furthermore, I run MD simulations of native and QTY-designed OPN2 and analyze their response to the 11-cis to all-trans isomerization of the retinal chromophore.
 
@@
 
-We predicted the structures of native proteins and their QTY variants using the AlphaFold3 website (\url{https://alphafoldserver.com}) \citep{Abramson_2024}.
+I predicted the structures of native proteins and their QTY variants using the AlphaFold3 website (\url{https://alphafoldserver.com}) \citep{Abramson_2024}.
 For microbial opsins, the dimers and trimers had identical subunits, i.e., they were homodimers and homotrimers.
@@
 Superpositions were performed via the command ``super'' in PyMOL (\url{https://pymol.org}).
-We remove unstructured loops at the N and C terminals for the sake of clarity.
+I remove unstructured loops at the N and C terminals for the sake of clarity.
 
@@
 
-We used PyMOL (\url{https://pymol.org}) to superpose the native predicted protein structures, their QTY variants, and the experimentally determined structures for the proteins where these existed.
-We then used UCSF ChimeraX (\url{https://www.cgl.ucsf.edu/chimerax/}) to render each protein model with hydrophobicity patches.
+I used PyMOL (\url{https://pymol.org}) to superpose the native predicted protein structures, their QTY variants, and the experimentally determined structures for the proteins where these existed.
+I then used UCSF ChimeraX (\url{https://www.cgl.ucsf.edu/chimerax/}) to render each protein model with hydrophobicity patches.
 
@@
 
-Regarding QTY-designed OPN2, we found that the helix 9 of the QTY analog was flung up and adhered to the originally transmembrane domain, which disrupted the normal conformation.
+Regarding QTY-designed OPN2, I found that the helix 9 of the QTY analog was flung up and adhered to the originally transmembrane domain, which disrupted the normal conformation.
 Therefore, this helix was truncated.
@@
 
-After the simulations, we extracted frames from the trajectory to inspect the structures before and after retinal isomerization.
-We also calculated the RMSD (``gmx rms'' command), number of hydrogen bonds (``gmx hbond'' command) and water molecules (``gmx select'' command) inside the binding pocket, interaction energy (including short-range Coulombic interaction energy and short-range Lennard-Jones energy) (``gmx energy'' command), the RMSF (``gmx rmsf'' command), and radius of gyration (``gmx gyrate'' command).
+After the simulations, I extracted frames from the trajectory to inspect the structures before and after retinal isomerization.
+I also calculated the RMSD (``gmx rms'' command), number of hydrogen bonds (``gmx hbond'' command) and water molecules (``gmx select'' command) inside the binding pocket, interaction energy (including short-range Coulombic interaction energy and short-range Lennard-Jones energy) (``gmx energy'' command), the RMSF (``gmx rmsf'' command), and radius of gyration (``gmx gyrate'' command).
 The detailed commands are publicly available in the online database for this study.
@@
 Traditionally, detergent must be used to purify them.
-We consider a different approach, i.e., via systematic soluble protein design.
+Zhang et al.
+considered a different approach, i.e., via systematic soluble protein design.
 There exists structural similarities, as can be observed on high-resolution electron density maps, between certain hydrophobic and hydrophilic amino acids: leucine (L) and glutamine (Q), isoleucine (I) or valine (V) and threonine (T), and phenylalanine (F) with tyrosine (Y).
-This fact enables systematic replacement of L with Q, I/V with T, and F with Y in all transmembrane segments of the membrane protein, which we named the QTY code.
+This fact enables systematic replacement of L with Q, I/V with T, and F with Y in all transmembrane segments of the membrane protein, which Zhang et al.
+named the QTY code.
 QTY analogs are less hydrophobic than native membrane proteins.
@@
 Thus, it is justified to predict the ligand-free forms of the proteins.
-We used AlphaFold3 to predict the structure of the 9 native human opsins and their water-soluble QTY analogs.
+I used AlphaFold3 to predict the structure of the 9 native human opsins and their water-soluble QTY analogs.
 The structures superpose very well (Figure~\ref{fig:humansup} \textbf{a)} to \textbf{i)}).
-For OPN2, which has an available X-ray diffraction structure, we also superposed the experimentally determined structure with the AlphaFold3-predicted structures.
+For OPN2, which has an available X-ray diffraction structure, I also superposed the experimentally determined structure with the AlphaFold3-predicted structures.
 Overall, the root mean square distances (RMSD) are small, from 0.307{\AA} to 0.611\AA, with only one exception of OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$ (RMSD = 0.999\AA).
@@
 However, they belong to different subfamilies and have structural differences from each other.
-In order to investigate the extent to which the water-soluble QTY analogs preserve these differences, we also conducted pairwise superpositions within all 9 native human opsins and within all 9 QTY analogs of human opsins (Figure~\ref{fig:humansup} \textbf{j)} and \textbf{k)}).
+In order to investigate the extent to which the water-soluble QTY analogs preserve these differences, I also conducted pairwise superpositions within all 9 native human opsins and within all 9 QTY analogs of human opsins (Figure~\ref{fig:humansup} \textbf{j)} and \textbf{k)}).
 As observed in the tables, there is a large degree of similarity between the RMSD between a pair of native proteins and that between the corresponding pair of QTY analogs.
-Therefore, we conclude that the structural differences are relatively well-preserved before and after the QTY substitution.
+Therefore, I conclude that the structural differences are relatively well-preserved before and after the QTY substitution.
 However, whether the functional differences are preserved remains a problem to study.
@@
 
-We used AlphaFold3 to predict the structure of monomers of the 3 native microbial opsins, their water-soluble QTY analogs.
-Since microbial opsins often have to form oligomers to be functional, we also predicted the structure of native and QTY variants of BACR trimers, BACH trimers, and ChR2 dimers.
+I used AlphaFold3 to predict the structure of monomers of the 3 native microbial opsins, their water-soluble QTY analogs.
+Since microbial opsins often have to form oligomers to be functional, I also predicted the structure of native and QTY variants of BACR trimers, BACH trimers, and ChR2 dimers.
 These predicted structures are also superposed with experimentally determined structures (X-ray diffraction or electron microscopy).
@@
 
-We investigate the surface hydrophobicity of water-soluble QTY-analogs in comparison with the native proteins.
+I investigate the surface hydrophobicity of water-soluble QTY-analogs in comparison with the native proteins.
 After applying the QTY code to respectively replace the hydrophobic amino acids L, I/V, and F with hydrophilic amino acids glutamine (Q), threonine (T), and tyrosine (Y), the hydrophobic surface areas are significantly reduced.
@@
 Although AlphaFold3 allows the structural prediction of complexes that include small-molecule ligands, it only supports a small range of ligands, which does not include retinal.
-We were therefore unable to predict the structure of chromophore-bound states of retinylidene proteins with AlphaFold3.
-Consequently, we chose another approach, namely molecular dynamics simulation, in order to investigate the behavior of QTY opsin analogs when they are bound to the chromophore.
+I were therefore unable to predict the structure of chromophore-bound states of retinylidene proteins with AlphaFold3.
+Consequently, I chose another approach, namely molecular dynamics simulation, in order to investigate the behavior of QTY opsin analogs when they are bound to the chromophore.
 
@@
 QTY substitutions do not introduce changes to the essential NPxxY motif or the retinal-binding lysine of human retinylidene proteins.
-Therefore, we propose that QTY analogs of human opsins may have conserved functions and carry out a molecular dynamics (MD) simulation.
-We record and analyze the behavior of native OPN2 and its QTY analog before and after the 11-cis to all-trans isomerization.
+Therefore, I propose that QTY analogs of human opsins may have conserved functions and carry out a molecular dynamics (MD) simulation.
+I record and analyze the behavior of native OPN2 and its QTY analog before and after the 11-cis to all-trans isomerization.
 
@@
 
-Zooming in on the retinal-binding pocket, we observe that retinal is held within its binding pocket by several forces in both the native and QTY analog: the counterions of the retinal Schiff base (RSB) (113E and 181E), the hydrophobic interactions with neighboring residues (for example, 265W, 268Y, and the 187--189 beta strand), and, sometimes, steric collisions (Figure~\ref{fig:binding}).
-Since retinal is a ligand that binds in an internal pocket, we were unable to calculate the Gibbs free energy of its binding.
+Zooming in on the retinal-binding pocket, I observe that retinal is held within its binding pocket by several forces in both the native and QTY analog: the counterions of the retinal Schiff base (RSB) (113E and 181E), the hydrophobic interactions with neighboring residues (for example, 265W, 268Y, and the 187--189 beta strand), and, sometimes, steric collisions (Figure~\ref{fig:binding}).
+Since retinal is a ligand that binds in an internal pocket, I were unable to calculate the Gibbs free energy of its binding.
 Nevertheless, the distribution of interaction energies are found to be similar in native OPN2 and the water-soluble QTY analog, except for small differences: native OPN2 experiences a change in interaction energy at about $t=50$ns due to the entrance of water near 113E; the QTY analog has more negative interaction energy at residues 208 and 212 due to phenylalanine (F) to tyrosine (Y) substitutions.
 Besides from these, the similarity is a strong suggestion of functional conservation.
-Finally, we observe very different hydrogen bonding and water molecule patterns inside the binding pocket, which is mainly due to several F to Y substitutions in that region.
+Finally, I observe very different hydrogen bonding and water molecule patterns inside the binding pocket, which is mainly due to several F to Y substitutions in that region.
 This may cause retinal to interact with adjacent residues in a subtly different way, and may lead to a different absorption peak since the environment of the RSB, i.e., the binding pocket, determines the spectral characteristic of opsins \citep{Fenno_2011}.
 
-Overall, we observe that QTY-designed OPN2 has relatively similar behavior to the native variant despite certain small differences caused by decreased hydrophobicity.
+Overall, I observe that QTY-designed OPN2 has relatively similar behavior to the native variant despite certain small differences caused by decreased hydrophobicity.
 The function of OPN2$^{\textrm{QTY}}$ awaits to be verified by experiments.
@@
 
-In this study, we selected 12 retinylidene proteins, including 9 human opsins (OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, and RRH) and 3 microbial opsins (BACR, BACH, and ChR2), that have clinical implications and various applications.
-We applied the QTY code to convert the hydrophobic transmembrane alpha-helices into hydrophilic ones and thus create water-soluble QTY analogs of the proteins.
-Then, we used AlphaFold3 to predict the structures of the native proteins as well as the QTY analogs, superposed them, and found that the structure of the proteins are well conserved despite substantial residue substitutions.
-We also inspected the surface hydrophobicity of the proteins and found a great decrease in hydrophobic patches in the transmembrane surface.
-Next, we chose a representative retinylidene protein, OPN2, and employed molecular dynamics simulations to investigate the behavior of native and QTY analog of OPN2.
-We found that the QTY analog is capable of conformational change and effective protein-ligand interaction.
+In this study, I selected 12 retinylidene proteins, including 9 human opsins (OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, and RRH) and 3 microbial opsins (BACR, BACH, and ChR2), that have clinical implications and various applications.
+I applied the QTY code to convert the hydrophobic transmembrane alpha-helices into hydrophilic ones and thus create water-soluble QTY analogs of the proteins.
+Then, I used AlphaFold3 to predict the structures of the native proteins as well as the QTY analogs, superposed them, and found that the structure of the proteins are well conserved despite substantial residue substitutions.
+I also inspected the surface hydrophobicity of the proteins and found a great decrease in hydrophobic patches in the transmembrane surface.
+Next, I chose a representative retinylidene protein, OPN2, and employed molecular dynamics simulations to investigate the behavior of native and QTY analog of OPN2.
+I found that the QTY analog is capable of conformational change and effective protein-ligand interaction.
 These findings reveal that QTY-designed OPN2, and retinylidene proteins in general, may have conserved structure and function.
-We believe that these water-soluble QTY variants may have potentials in research, therapeutic treatments, and bioengineering.
+I believe that these water-soluble QTY variants may have potentials in research, therapeutic treatments, and bioengineering.
 

### 2025-06-09 Paper/Manuscript-revised/manuscript.tex
Revise manuscript

--- 2025-05-16 Paper/Manuscript/manuscript.tex
@@
 However, retinylidene proteins have hydrophobic transmembrane (TM) domains, which makes them challenging to study.
-In this structural and functional bioinformatics study, I used the QTY (Glutamine, Threonine, Tyrosine) code to design water-soluble QTY analogs of retinylidene proteins, including 9 human and 3 microbial opsins.
+In this structural and functional bioinformatics study, I use the QTY (Glutamine, Threonine, Tyrosine) code to design water-soluble QTY analogs of retinylidene proteins, including 9 human and 3 microbial opsins.
 I provide superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY analogs, and experimentally-determined structures when available.
@@
 Retinylidene proteins are photochemically reactive proteins that are bound to or can bind to retinal (vitamin A aldehyde) as their chromophore \citep{Spudich_2000}.
-I will use the term ``opsin'' interchangeably with ``retinylidene protein'', despite the fact that ``opsin'' sometimes refers specifically to the chromophore-free apoprotein.
+For convenience, I will use the term ``opsin'' interchangeably with ``retinylidene protein'', despite the fact that ``opsin'' sometimes refers specifically to the chromophore-free apoprotein.
 Retinylidene proteins are divided into two groups, animal opsins and microbial opsins, which are evolutionarily distinct but share common characteristics such as having 7 transmembrane (TM) domains and a retinal-binding lysine residue \citep{Yee_2013, Spudich_2000}.
@@
 Proton transfer plays an important role in this process \citep{Mahalingam_2008}.
-As the protein conformation changes, TM6 characteristically moves outward, activating the G-protein.
+Afterward, the protein bleaches and returns to the dark state, completing what is called the photocycle.
+As the protein conformation changes to META, TM6 moves characteristically outward, activating the G-protein.
+In photoreceptor cells, the G-protein, transducin, activates a phosphodiesterase, which hydrolyzes cGMP into GMP, decreasing the activity of cGMP-gated cation channels and hyperpolarizing the cell \citep{Chabre_1989}.
 
-In this study, I selected 9 opsins expressed in the human nervous system: OPN1MW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04001}), OPN1SW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P08100/entry}{P04001}), OPN3 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}).
+In this study, I select 9 opsins expressed in the human nervous system: OPN1MW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04001}), OPN1SW (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P08100/entry}{P04001}), OPN3 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}).
 They belong to several evolutionarily distinct families of animal opsins \citep{Terakita_2005}.
@@
 Many studies on the functional mechanisms of animal opsins also focus on OPN2.
-Consequently, I choose OPN2 to conduct a functional analysis in this study, in order to further explore the effectiveness of the QTY code in redesigning retinylidene proteins.
+Consequently, I choose OPN2 to conduct a functional analysis in this study in order to further explore the effectiveness of the QTY code in redesigning retinylidene proteins.
 
@@
 
-In this study, I selected 3 microbial opsins: BACR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P02945/entry}{P02945}), BACH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/B0R2U4/entry}{B0R2U4}), ChR2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q8RUT8/entry}{Q8RUT8}).
+In this study, I select 3 microbial opsins: BACR (UniProt ID: \href{https://www.uniprot.org/uniprotkb/P02945/entry}{P02945}), BACH (UniProt ID: \href{https://www.uniprot.org/uniprotkb/B0R2U4/entry}{B0R2U4}), ChR2 (UniProt ID: \href{https://www.uniprot.org/uniprotkb/Q8RUT8/entry}{Q8RUT8}).
 
@@
 
-Instead of taking a computational approach, I applied the QTY (Glutamine, Threonine, Tyrosine) code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins.
+Instead of taking a computational approach, I apply the QTY (Glutamine, Threonine, Tyrosine) code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins.
 There are structural similarities between hydrophobic and polar amino acids: leucine (L) and glutamine (Q); isoleucine (I) / valine (V) and threonine (T); and phenylalanine (F) and tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}.
@@
 initially applied the QTY code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}.
-Zhang's team have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.
-In addition to GPCR, they have also used the QTY code to design water-soluble glucose transporters \citep{Smorodina_2022}, ABC transporters \citep{Pan_2024}, monoamine neurotransmitter transporters \citep{Karagol_Karagol_Alper_2024}, glutamate transporters \citep{Karagol_Karagol_Smorodina_2024, Karagol_2024}, mitochondrial megacomplex \citep{Chen_2025}, antibodies \citep{Li_Wang_2024}, potassium channels \citep{Smorodina_2024}, receptor kinases \citep{Li_Tang_2024}, transmembrane enzymes \citep{Chen_Pan_2025}, as well as bacterial enzymes with beta barrel structures \citep{Sajeev-Sheeja_2023, Sajeev-Sheeja_2024}.
-The QTY-designed water-soluble CXCR4 chemokine receptor has been successfully used in biomimetic sensors \citep{Qing_2023}.
-They have also applied the rQTY (reverse QTY) code to design self-assembled nanoparticles \citep{Meng_2023}.
+Zhang's team also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.
+In addition to GPCR, they used the QTY code to design water-soluble glucose transporters \citep{Smorodina_2022}, ABC transporters \citep{Pan_2024}, monoamine neurotransmitter transporters \citep{Karagol_Karagol_Alper_2024}, glutamate transporters \citep{Karagol_Karagol_Smorodina_2024, Karagol_2024}, mitochondrial megacomplex \citep{Chen_2025}, antibodies \citep{Li_Wang_2024}, potassium channels \citep{Smorodina_2024}, receptor kinases \citep{Li_Tang_2024}, transmembrane enzymes \citep{Chen_Pan_2025}, as well as bacterial enzymes with beta barrel structures \citep{Sajeev-Sheeja_2023, Sajeev-Sheeja_2024}.
+The QTY-designed water-soluble CXCR4 chemokine receptor was successfully used in biomimetic sensors \citep{Qing_2023}.
 
@@
 Subsequently, AlphaFold3 was released in May 2024, featuring improved architecture and improved efficiency \citep{Abramson_2024}.
-Furthermore, AlphaFold3 enabled the accurate prediction of complexes of multiple proteins, as well as complexes with modified residues, nucleic acids, ions, certain ligands.
+Furthermore, AlphaFold3 enabled the accurate prediction of complexes of multiple proteins, as well as complexes with modified residues, nucleic acids, ions, and certain ligands.
 QTY studies have made use of these new features \citep{Chen_2025, Johnsson_2025}.
@@
 I predicted the structures of native proteins and their QTY variants using the AlphaFold3 website (\url{https://alphafoldserver.com}) \citep{Abramson_2024}.
-For microbial opsins, the dimers and trimers had identical subunits, i.e., they were homodimers and homotrimers.
+For microbial opsins, the dimers and trimers have identical subunits, i.e., are homodimers and homotrimers.
 In AlphaFold3, this was achieved by altering the number of protein copies.
@@
 Superpositions were performed via the command ``super'' in PyMOL (\url{https://pymol.org}).
-I remove unstructured loops at the N and C terminals for the sake of clarity.
+I removed unstructured loops at the N and C terminals for the sake of clarity.
 
@@
 
-Regarding native OPN2, the membrane protein system was constructed using the web-based membrane builder CHARMM-GUI and was downloaded in GROMACS format \citep{Jo_2008, Wu_2014, Lee_2016}.
+Regarding native OPN2, the protein-membrane system was constructed using the web-based membrane builder CHARMM-GUI and downloaded in GROMACS format \citep{Jo_2008, Wu_2014, Lee_2016}.
 The protein was centered in a rectangular box.
-The generated membrane models consisted of 40\% POPC, 40\% POPE, 10\% POPS, and 10\% cholesterol, which simulate a rod photoreceptor disk membrane \citep{Albert_2005}.
+The generated membrane models consisted of 40\% POPC, 40\% POPE, 10\% POPS, and 10\% cholesterol, which simulated a rod photoreceptor disk membrane where native OPN2 is usually expressed \citep{Albert_2005}.
 The system was solvated in TIP3P water with 150 mM NaCl.
+NaCl was used instead of KCl to simulate the environment of rod photoreceptor outer segments \citep{Govardovskii_1971}.
 11-cis-retinal was manually added to the protein files.
@@
 Following equilibration, a 10-ns production MD simulation was run.
-The retinal molecule was then manually switched to the all-trans state by rotating C13 to C15 and bonded hydrogen and methyl groups by 180 degrees around the C11-C12 bond.
-This mimics the effect of the absorption of a photon by 11-cis-retinal.
+The retinal molecule was then manually switched to the all-trans state by rotating C13 to C15 and associated hydrogen and methyl groups by 180 degrees around the C11-C12 bond.
+This mimicked the effect of the absorption of a photon by 11-cis-retinal.
 Energy minimization and equilibration were repeated exactly as before, and then a 120-ns production MD simulation was run.
 
-Regarding QTY-designed OPN2, I found that the helix 9 of the QTY analog was flung up and adhered to the originally transmembrane domain, which disrupted the normal conformation.
+Regarding QTY-designed OPN2, I found that the helix 9 of the QTY analog flung up and adhered to the surface that was originally the transmembrane domain, which disrupted the normal conformation.
 Therefore, this helix was truncated.
@@
 The equilibration involved a sequence of simulations: one 250-ps NVT equilibration, followed by one 125-ps and one 1500-ps NPT equilibrations, totaling an equilibration duration that matches that of the natural OPN2.
-All other configurations and parameters are identical to those of the original OPN2.
+All other configurations and parameters were identical to those of the original OPN2.
 
@@
 considered a different approach, i.e., via systematic soluble protein design.
-There exists structural similarities, as can be observed on high-resolution electron density maps, between certain hydrophobic and hydrophilic amino acids: leucine (L) and glutamine (Q), isoleucine (I) or valine (V) and threonine (T), and phenylalanine (F) with tyrosine (Y).
+There exist structural similarities, as can be observed on high-resolution electron density maps, between certain hydrophobic and hydrophilic amino acids: leucine (L) and glutamine (Q), isoleucine (I) or valine (V) and threonine (T), and phenylalanine (F) with tyrosine (Y).
 This fact enables systematic replacement of L with Q, I/V with T, and F with Y in all transmembrane segments of the membrane protein, which Zhang et al.
@@
 QTY analogs are less hydrophobic than native membrane proteins.
-Although their amino acid sequences have been significantly changed, they still exhibit relatively preserved structure, isoelectric points (pI), and molecular weights (MW) compared to the native membrane proteins (Table~\ref{tb:characteristics}).
+Although their amino acid sequences are significantly changed, they still exhibit relatively preserved structure, isoelectric points (pI), and molecular weights (MW) compared to the native membrane proteins (Table~\ref{tb:characteristics}).
 
@@
 
-The protein sequences of 9 human opsins and 3 microbial opsins are aligned with their QTY analogs (Figure~\ref{fig:sequences}).
+The protein sequences of 9 human opsins and 3 microbial opsins were aligned with their QTY analogs (Figure~\ref{fig:sequences}).
 The QTY substitution resulted in an overall variation of the sequence of 15.48\% to 30.04\% and a variation of transmembrane domain of 35.53\% to 50.24\%.
-Despite changes in amino acid composition and sequence, the pI only experiences a slight change, between 0.00 and 0.16.
+Despite changes in amino acid composition and sequence, the pI only experienced a slight change, between 0.00 and 0.16.
 This is because the amino acids Q, T, and Y have neutral charges and do not introduce additional charges to the system.
-The MW increases slightly by a value between 0.04kDa and 0.60kDa.
+The MW increased slightly by a value between 0.04kDa and 0.60kDa.
 This is because the hydrophilic amino acids usually have nitrogen or oxygen atoms in place of carbon atoms in hydrophobic acids and thus may have higher mass: L (131.17Da) \textit{vs} Q (146.14Da); I (131.17Da) and V (117.15Da) \textit{vs} T (119.12Da); F (165.19Da) \textit{vs} Y (181.19Da).
@@
 I used AlphaFold3 to predict the structure of the 9 native human opsins and their water-soluble QTY analogs.
-The structures superpose very well (Figure~\ref{fig:humansup} \textbf{a)} to \textbf{i)}).
+The structures superposed very well (Figure~\ref{fig:humansup} \textbf{a)} to \textbf{i)}).
 For OPN2, which has an available X-ray diffraction structure, I also superposed the experimentally determined structure with the AlphaFold3-predicted structures.
-Overall, the root mean square distances (RMSD) are small, from 0.307{\AA} to 0.611\AA, with only one exception of OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$ (RMSD = 0.999\AA).
+Overall, the root mean square distances (RMSD) were small, from 0.307{\AA} to 0.611\AA, with only one exception of OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$ (RMSD = 0.999\AA).
 This shows that the water-soluble QTY analogs are quite similar to native proteins in terms of structure.
@@
 In order to investigate the extent to which the water-soluble QTY analogs preserve these differences, I also conducted pairwise superpositions within all 9 native human opsins and within all 9 QTY analogs of human opsins (Figure~\ref{fig:humansup} \textbf{j)} and \textbf{k)}).
-As observed in the tables, there is a large degree of similarity between the RMSD between a pair of native proteins and that between the corresponding pair of QTY analogs.
+As observed in the tables, there was a large degree of similarity between the RMSD between a pair of native proteins and that between the corresponding pair of QTY analogs.
 Therefore, I conclude that the structural differences are relatively well-preserved before and after the QTY substitution.
@@
 Since microbial opsins often have to form oligomers to be functional, I also predicted the structure of native and QTY variants of BACR trimers, BACH trimers, and ChR2 dimers.
-These predicted structures are also superposed with experimentally determined structures (X-ray diffraction or electron microscopy).
-The structures superpose very well (Figure~\ref{fig:microbialsup}).
-Overall, the root mean square differences (RMSD) are small, with the highest value being 0.685\AA.
+These predicted structures were also superposed with experimentally determined structures (X-ray diffraction or electron microscopy).
+The structures superposed very well (Figure~\ref{fig:microbialsup}).
+Overall, the root mean square differences (RMSD) were small, with the highest value being 0.685\AA.
 This shows that the water-soluble QTY analogs are likely capable of forming oligomers with structures similar to those of native proteins.
@@
 In the native proteins, there are large hydrophobic patches in the transmembrane domains, which are embedded within the lipid bilayer.
-The nonpolar and hydrophobic amino acids including leucine (L), isoleucine (I), valine (V), phenylalanine (F), alanine (A), methionine (M), and tryptophan (W) interact with the hydrophobic hydrocarbon chains and expel water.
+The nonpolar and hydrophobic amino acids, including leucine (L), isoleucine (I), valine (V), phenylalanine (F), alanine (A), methionine (M), and tryptophan (W), interact with the hydrophobic hydrocarbon chains and expel water.
 
-I investigate the surface hydrophobicity of water-soluble QTY-analogs in comparison with the native proteins.
-After applying the QTY code to respectively replace the hydrophobic amino acids L, I/V, and F with hydrophilic amino acids glutamine (Q), threonine (T), and tyrosine (Y), the hydrophobic surface areas are significantly reduced.
-More importantly, since the electron density maps of the corresponding amino acids are similar, the alpha helices in QTY analogs have a similar contour to those in the native proteins.
-The QTY analogs have successfully retained its structural integrity and stability.
+I investigated the surface hydrophobicity of water-soluble QTY-analogs in comparison with the native proteins.
+After applying the QTY code to respectively replace the hydrophobic amino acids L, I/V, and F with hydrophilic amino acids glutamine (Q), threonine (T), and tyrosine (Y), the hydrophobic surface areas were significantly reduced.
+More importantly, since the electron density maps of the corresponding amino acids are similar, the alpha helices in QTY analogs had a similar contour to those in the native proteins.
+The QTY analogs successfully retained its structural integrity and stability.
 
@@
 
-AlphaFold3 is easily accessible online (\url{https://alphafoldserver.com}), allowing users to make 30 predictions a day.
-The structures of the QTY analogs were predicted using the AlphaFold3 server, which was run free of charge and the results were produced within a few minutes.
+AlphaFold3 is easily accessible online (\url{https://alphafoldserver.com}), allowing users to make 30 predictions a day at present.
+The structures of the QTY analogs were predicted using the AlphaFold3 server, which was free of charge, and the results were produced within a few minutes.
 
-DeepMind also collaborates with the EBI to make over 214 million predicted protein structures available through the AlphaFold Protein Structure Database (\url{https://alphafold.ebi.ac.uk}).
+DeepMind also collaborated with the EBI to make over 214 million predicted protein structures available through the AlphaFold Protein Structure Database (\url{https://alphafold.ebi.ac.uk}).
 This number is continuously expanding, with the quality of predictions further improving with the advent of AlphaFold 3.
@@
 Although AlphaFold3 allows the structural prediction of complexes that include small-molecule ligands, it only supports a small range of ligands, which does not include retinal.
-I were therefore unable to predict the structure of chromophore-bound states of retinylidene proteins with AlphaFold3.
+I was therefore unable to predict the structure of chromophore-bound states of retinylidene proteins with AlphaFold3.
 Consequently, I chose another approach, namely molecular dynamics simulation, in order to investigate the behavior of QTY opsin analogs when they are bound to the chromophore.
@@
 QTY substitutions do not introduce changes to the essential NPxxY motif or the retinal-binding lysine of human retinylidene proteins.
-Therefore, I propose that QTY analogs of human opsins may have conserved functions and carry out a molecular dynamics (MD) simulation.
-I record and analyze the behavior of native OPN2 and its QTY analog before and after the 11-cis to all-trans isomerization.
+Therefore, I proposed that QTY analogs of human opsins may have conserved functions and carried out a molecular dynamics (MD) simulation.
+I recorded and analyzed the behavior of native OPN2 and its QTY analog before and after the 11-cis to all-trans isomerization.
+Please note that my aim is not to simulate the whole photocycle of OPN2, which takes longer than 1ms \citep{Fanelli_2021}, but rather to find proof that the QTY analog conserves the function of being activated by isomerization of retinal.
 
-The MD simulation provides evidence of conformational change in both native and QTY analogs (Figure~\ref{fig:conformation}).
-The native protein experiences a slower change from its original conformation, while the QTY analog shows more fluctuations and sudden changes.
-Under further inspection, this phenomenon may be due to the entrance of water molecules into the QTY analog.
-In addition, retinal molecule has a greater degree of change in conformation in the native protein than in the QTY analog.
-Nevertheless, the retinal in the QTY analog is still able to cause changes to surrounding residues, sometimes doing so through contact with water molecules.
+The MD simulation provided evidence of conformational change in both native and QTY analogs (Figure~\ref{fig:conformation}).
+The native protein experienced a slower change from its original conformation, while the QTY analog showed more fluctuations and sudden changes.
+Under further inspection, this phenomenon might be due to the entrance of water molecules into the QTY analog.
+In addition, retinal molecule had a greater degree of change in conformation in the native protein than in the QTY analog.
+Nevertheless, the retinal in the QTY analog was still able to cause changes to surrounding residues, sometimes doing so via intervening water molecules.
+It may be noted that the RMSD was still fluctuating, which means that the protein had not yet stabailized.
+This was expected, since the OPN2 was still in the process of transition from BATH to LUMI state, and this provided evidence for the activation of the protein in response to isomerization of retinal.
 
-Zooming in on the retinal-binding pocket, I observe that retinal is held within its binding pocket by several forces in both the native and QTY analog: the counterions of the retinal Schiff base (RSB) (113E and 181E), the hydrophobic interactions with neighboring residues (for example, 265W, 268Y, and the 187--189 beta strand), and, sometimes, steric collisions (Figure~\ref{fig:binding}).
-Since retinal is a ligand that binds in an internal pocket, I were unable to calculate the Gibbs free energy of its binding.
-Nevertheless, the distribution of interaction energies are found to be similar in native OPN2 and the water-soluble QTY analog, except for small differences: native OPN2 experiences a change in interaction energy at about $t=50$ns due to the entrance of water near 113E; the QTY analog has more negative interaction energy at residues 208 and 212 due to phenylalanine (F) to tyrosine (Y) substitutions.
-Besides from these, the similarity is a strong suggestion of functional conservation.
-Finally, I observe very different hydrogen bonding and water molecule patterns inside the binding pocket, which is mainly due to several F to Y substitutions in that region.
-This may cause retinal to interact with adjacent residues in a subtly different way, and may lead to a different absorption peak since the environment of the RSB, i.e., the binding pocket, determines the spectral characteristic of opsins \citep{Fenno_2011}.
+Zooming in on the retinal-binding pocket, I observed that retinal is held within its binding pocket by several forces in both the native and QTY analog: the counterions of the retinal Schiff base (RSB) (113E and 181E), the hydrophobic interactions with neighboring residues (for example, 265W, 268Y, and the 187--189 beta strand), and, sometimes, steric collisions (Figure~\ref{fig:binding}).
+Since retinal is a ligand that binds in an internal pocket, I was unable to calculate the Gibbs free energy of its binding.
+Nevertheless, the distributions of interaction energies were found to be similar in native OPN2 and the water-soluble QTY analog, except for small differences: native OPN2 experienced a change in interaction energy at about $t=50$ns due to the entrance of water near 113E; the QTY analog had more negative interaction energy at residues 208 and 212 due to phenylalanine (F) to tyrosine (Y) substitutions.
+Apart from these, the similarity was a strong suggestion of functional conservation.
+Finally, I observed very different hydrogen bonding and water molecule patterns inside the binding pocket, which was mainly due to several F to Y substitutions in that region.
+This might cause retinal to interact with adjacent residues in a subtly different way, and might lead to a different absorption peak since the environment of the RSB, i.e., the binding pocket, determines the spectral characteristic of opsins \citep{Fenno_2011}.
 
-Overall, I observe that QTY-designed OPN2 has relatively similar behavior to the native variant despite certain small differences caused by decreased hydrophobicity.
+Overall, I observed that QTY-designed OPN2 had relatively similar behavior to the native variant despite certain small differences caused by decreased hydrophobicity.
 The function of OPN2$^{\textrm{QTY}}$ awaits to be verified by experiments.
@@
 
-Furthermore, water-soluble QTY opsins may be useful clinically, since they could be delivered and/or expressed in the eye without forming aggregates and precipitating.
-This may be a potential pathway in restoring basic vision for those who have lost it.
+Furthermore, water-soluble QTY opsins could be useful clinically, since they could be delivered and/or expressed in the eye without forming aggregates and precipitating.
+It is not unreasonable to hypothesize that QTY opsins can still pass through the photocycle and interact with downstream signaling proteins.
+In light of this, QTY opsins may facilitate the optogenetic therapy of ophthalmological diseases \citep{Sakai_2022}, providing a potential pathway in restoring basic vision for those who have lost it.
 
@@
 
-In this study, I selected 12 retinylidene proteins, including 9 human opsins (OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, and RRH) and 3 microbial opsins (BACR, BACH, and ChR2), that have clinical implications and various applications.
+In this study, I selected 12 retinylidene proteins, including 9 human opsins (OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, and RRH) and 3 microbial opsins (BACR, BACH, and ChR2), that had clinical implications and various potential applications.
 I applied the QTY code to convert the hydrophobic transmembrane alpha-helices into hydrophilic ones and thus create water-soluble QTY analogs of the proteins.
-Then, I used AlphaFold3 to predict the structures of the native proteins as well as the QTY analogs, superposed them, and found that the structure of the proteins are well conserved despite substantial residue substitutions.
+Then, I used AlphaFold3 to predict the structures of the native proteins as well as the QTY analogs, superposed them, and found that the structure of the proteins were well conserved despite substantial residue substitutions.
 I also inspected the surface hydrophobicity of the proteins and found a great decrease in hydrophobic patches in the transmembrane surface.
 Next, I chose a representative retinylidene protein, OPN2, and employed molecular dynamics simulations to investigate the behavior of native and QTY analog of OPN2.
-I found that the QTY analog is capable of conformational change and effective protein-ligand interaction.
-These findings reveal that QTY-designed OPN2, and retinylidene proteins in general, may have conserved structure and function.
+I found that the QTY analog was capable of conformational change and effective protein-ligand interaction.
+These findings revealed that QTY-designed OPN2, and retinylidene proteins in general, might have conserved structure and function.
 I believe that these water-soluble QTY variants may have potentials in research, therapeutic treatments, and bioengineering.
